\reftab{2-7}: PDF-specific display options 
Option Value Default Description 
a4pa per boolean true Paper size is set to 210 mm X 297 mm. 
3: 
boolean 
Iegalpa per 
bookmarks boolean false Write a set of Acrobat bookmarks, in a 
manner similar to the table of contents, 
requiring two passes of ET X 
bookmarksnumbered boolean false If Acrobat bookmarks are requested, 
include the section numbers. 
0 
Set the PDF View for each link.
. 1 V . 
pdfstartpage name Set the page number on which the’ PDF file 
.. K ogisyapeoneayygg . L _ K 
pdfstartview name Fit Set the initial page view. 
.pdfh‘ighfigl§t " /I T Determine how link buttons behave when 
e o _ selected / I is for‘111jve1'se (tlacoglefar It}; the 
iiii _ 111 . , 
and /P 
7 (outline), 
citebordercolor RGB color 0 1 0 The color of the box around citations. 
fiiebordercolor j H RGB, color 0 .5 .5 The color of the box around links to files. 
linkbordercolor RGB color 1 0 0 D The color of the box around simple links. 
menuboréercoior ; . s 7“ color *1 “ 00 . L The color of ythegboxam Acrobat-menu 
bordercolor RGB color 1 1 0 The color of the box around links to pages. 
uribordercolor o a RGB color 0 1 I The color of the box around links to URLs. 
pdfpagescrop n n n n Set the default PDF crop box for pages. 
This should be a set of four numbers, like a 
PostScript BoundingBox. 
0,70 1' D styleyof aroundlinks. Defaultsto" a D 
D T D ’ boxewiith lines of lpt thickness, but the D T‘ T 4 
, coloxlinks option resets it toproduce no 
a border. ii ‘ 
pdftoolbar boolean false Determine whether the viewer’s toolbar is 
visible when the document is opened. 
pdfmenubar boolean fizlse o Detennine Whether the viewers menu bar L 
o if D H o T is visible. if 
pdfwindowui boolean false Determine whether the user interface 
elements in the document’s window are 
visible. 
, bqolean L o a false ; Determine whether the shouldfl _ y 
i “ it - s * r T resize the window displaying the dowment 
to fit the size of the first displayed pagelof“ 
pdfcenterwindow boolean false Determine whether the viewer should 
position the window displaying the 
document in the center of the computer’s 
monitor. 
pdfvagéfayoute D name ‘ SiagiePzzge me. layouts tl1‘e-‘tl1e l V. y . 
T document isiopiened. The possibilities are 
V V . T listed in \reftab{2-11} on page 66. 
pdfnewwindow boolean false Determine whether links that open another 
PDF file should start a new window or 
replace the contents of the current window 
with the new file.“ 
pdffitwihdowr “Under Windows, the new window is placed in exactly the same place on the screen as the existing window. To make them 
both visible at the same time, you have to use the VVindow->Tile . . . menu item; then adjust the windows by hand with the 
mouse, or use Ctrl-Tab. 

 
