\reftab{2-10}: Forms options 

Option Value Default Description 
accesskey key (As per HTML) 
backgroundcolor RGB color 1 I 1 Color of field box. 
bordersep V H : content an bor er. 
borderwidth number 1 Width of box border (in points) 
charsize dimen Iopt Font Slze of field text. 
 
color RGB color 0 0 0 Color of text in box. 
combo boolean false VVhether choice list is combo style. 
default Default value for field 
disabled boolean false Whether field is disabled. 
form at _]avaScript code to format the entry. 
height dimen Height of field box. 
hidden boolean false VVhether field is hidden. 
keystroke _]avaScn'pt code to control the keystrokes on entry. 
maxien number 0 Number of characters allowed in text field (0 means 
unlimited). 
menulength number 4 Number of elements shown in list. 
muitiiine boolean false VVhether text box is multiline. 
name name Name of field (defaults to the label contents). 
onbiur _lavaScript code. 
oncha nge _]avaScript code. 
onciick _]avaScript code. 
ondblclick _]avaScn'pt code. 
onfocus Javascript code. 
onkeydown Javascript code. 
onkeypress _]avaScript code. 
onkeyup Javascript code. 
onmousedown _lavaScript code. 
on mousemove Javascript code. 
onmouseout _]avaScript code. 
onmouseover _]avaScript code. 
onmouseu p _lavaScript code. 
onselect _lavaScript code. 
password boolean false VVhether text field is password style. 
popdown boolean fizlse VVhether choice list is pop-down style. 
radio boolean false VVhether choice list is radio style. 
readoniy boolean false VVhether field is read only. 
tabkey (as per HTML) 
validate _lavaScript code to validate the entry. 
value Initial value for field-not the same as the default. 
width dimen Width of field box.
