% vim: keymap=russian-jcukenwin
%%beginhead 
 
%%file 31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.pic.3.cmt
%%parent 31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine
 
%%url 
 
%%author_id 
%%date 
 
%%tags 
%%title 
 
%%endhead 

\iusr{Slav Jouravlev}
SCUM

\iusr{Piero Passarelli}

Awful characters.... without dignity!

\iusr{Juan Calvo Suárez}

White collar Imputable real terrorists

\iusr{Федько Коваленко}

Russian political figure Vladimir Zhirinovsky in Russian parlament votes for
burning Paris and o bomb Germany 

\url{https://www.facebook.com/video.php?v=1384527028526819}

\#ukraineneedsjavelines

Federalisation of the Ukraine? Forcing Ukraine to agree with Crimea annexion by
Russia? That is how US and EU plan to "help" the Ukraine?

History repeats today. Appeasement policy did not work to stop Hitler and now
does not work and cannot stop Putin! Like Hitler started from annexion of
Аustria (anshlus) and occupying part of Czechoslovak Republic (Sudetes) and
attacking Poland - the same thing Putin does today. War against Gergia,
annexing Crimea (part of the Ukraine) and starting war against the Ukraine...

To Iran, India, Pakіstan, and others: Please do not repeat the mistake of the
Ukraine, do not join the Treaty on the Non-Proliferation of Nuclear Weapons
because there are no "Security Assurances" for you!!!!

It was a big mistake for the Ukraine to join Treaty on the Non-Proliferation of
Nuclear Weapons in exchange for "Security Assurances" - now Russia annexed part
of the Ukraine and started war against the Ukraine, russian solders have
invaded to Ukraine, but other countries forgot about their obligations on
"Security Assurances" and do almost nothing to save the Ukraine from Russia -
they are just "deeply concerned" or try to play "appeasement" again, as that
happened before....

\url{https://en.wikipedia.org/wiki/Budapest_Memorandum_on_Security_Assurances}

According to the memorandum, Russia, the U.S., and the UK confirmed, in
recognition of Ukraine becoming party to the Treaty on the Non-Proliferation of
Nuclear Weapons and in effect abandoning its nuclear arsenal to Russia, that
they would:

* Respect Ukrainian independence and sovereignty within its existing borders.

* Refrain from the threat or use of force against Ukraine.

* Refrain from using economic pressure on Ukraine in order to influence its politics.

* Seek immediate United Nations Security Council action to provide assistance to Ukraine, "if Ukraine should become a victim of an act of aggression or an object of a threat of aggression in which nuclear weapons are used".

* Refrain from the use of nuclear arms against Ukraine.

* Consult with one another if questions arise regarding these commitments.

For those who claim "Ukraine is a different state after revolution". Do you
also confirm that such a new state has no obligations on credits and has no
debt any more? Do you confirm that new Ukraine has no obligations on Treaty on
the Non-Proliferation of Nuclear Weapons ans can create new Nuclear Weapons
now?

PHOTO

\iusr{Александр Арбузов}
"Джон Мак Кейн John McCain" мне жаль становится что наши вьетнамские друзья его не убили...

\iusr{Daniel Lins}

May Peace attend you always

||13SACTGATROUAACTSTWG 3688TAMWHBCTGCTG

PARAIBA

STONE ||3688

\iusr{Gala Konnova}
McCain non è essere umano. Garantisco!

\iusr{Екатерина Стрельченко}

Yatsenyuk - Prime War, Czech Prime Minister rightly said, it is because of him
and Turchinova such a mess in the country, fascist and kill innocent people.
Yatsenyuk - you're a murderer and a bastard!


\iusr{Imre Géczi}
Tömeg gyilkosok találkozója !

\href{https://www.facebook.com/notes/349016649860342}{
PROCLAMATION FOR BOYCOTTING IN THE NAME OF PEACE, AGAINST WARMONGERING COUNTRIES !!, facebook%
}

\iusr{Александра Карнышкова}

all the stories about corruption - this is the reason to destroy the state,
including Russian no faith in democracy and never will .... the United States
is not a god ... and you still get tired of Ukraine .... now only the
beginning)


\iusr{Hubert Deschouwer}

bad apel John MCCAIN!
war man !!!!!

\iusr{J.V. Ayson}
John McCain, talking with notorious Maidan leaders.

\iusr{Rudolfo Rojas}

Senator McCain is a legitimate war hero and has a great amount of integrity. He
continues to support those who present tyranny and discord to their people. I
would suggest before you throw 'Stones' you stand in his foot steps. He
suffered greatly for our country and did his patriotic duty for Americans.

\iusr{Albu Dumitru Marian}
The Zionazis have met

\iusr{Maxim Kilewoy}
fascism

\iusr{Paul H.Carr}
He is a relic of the US destructive past and most of the world wish men like him would simply go away.

\iusr{Alex Matveev}
What a disgusting picture....

\iusr{Aleks Leonov}
The real ovner of ucrain

\iusr{Алексей Прокофьев}

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10574527_913266472026147_7983954473864174616_n.jpg?_nc_cat=110&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=rXGn8g8xrX4AX_ZF82z&_nc_ht=scontent-frx5-1.xx&oh=fe478f46751152bc43ad6ddd3cb8bf05&oe=61CADDFC
  @width 0.4
\fi

\begin{itemize} % {
\iusr{Alex Manikhin}

\ifcmt
  ig https://scontent-frt3-1.xx.fbcdn.net/v/t1.18169-9/10897076_10205979966640100_3391437138516221357_n.jpg?_nc_cat=104&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=zkpFSrJm-hgAX-OrmIu&_nc_ht=scontent-frt3-1.xx&oh=3d0c00e78d06bdfa4849099b7b1b4483&oe=61CAFDC7
  @width 0.4
\fi

\iusr{Bob Sincl}

Actually Ukraine army participated in the US' dirty iraq war with 123,284
killed civilians. Also Check out the US' history of supported coup d'etats and
wars.

\iusr{Jorge Albella}
better i would say: Three nations destroyed.

\iusr{Владислав Перчинков}
Cant wait to see Russia fuck your Nazi ass up  @igg{fbicon.face.grinning.big.eyes} 

\end{itemize} % }

\iusr{Marc Raymond Wilkins}

Forget McCain. He has no power. He is a clown. Viva la liberty of Ukraine.

\begin{itemize} % {
\iusr{Христина Грищук}
Viva los Heroes of Ukraine!

\iusr{Marc Raymond Wilkins}

Thalles, please define "genociders". Once you are done with this task, you will
see that you are wrong with your perception that the Ukrainian government are
committing a genocide.


\iusr{Rudolfo Rojas}
Slava Ukraina
\end{itemize} % }

\iusr{Olga Stellmach}
Psychos seems to be the right adviser to Ukraine's pretend Government

\iusr{Jozef Konš}
3 warmongers....

\iusr{Dimitri Mikhayloff}

"And this gesture, my dear friend, is called 'embracing democratic values': it
shows how young men who want to advance politically in today's West ought to
learn to hug each other physically. It's real easy, Yats. Come here, I'll show
you."
