% vim: keymap=russian-jcukenwin
%%beginhead 
 
%%file 31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine
%%parent 31_12_2014
 
%%url https://www.facebook.com/permalink.php?story_fbid=902035439820756&id=386829811341324
 
%%author_id stoun_oliver.kinorezhisser.usa
%%date 
 
%%tags donbass,ukraina,vojna
%%title 'Nightingale' in Ukraine
 
%%endhead 
 
\subsection{'Nightingale' in Ukraine}
\label{sec:31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine}
 
\Purl{https://www.facebook.com/permalink.php?story_fbid=902035439820756&id=386829811341324}
\ifcmt
 author_begin
   author_id stoun_oliver.kinorezhisser.usa
 author_end
\fi

'Nightingale' in Ukraine

For those of you angry with my analysis of Ukraine yesterday, please try to
understand the bigger picture I’m offering. I have no brief for Viktor
Yanukovych, he may well be the most corrupt president Ukraine’s ever had.
Ukraine has a dramatic history of corruption.  That is not my point. How
Yanukovych was removed is - and although many (perhaps a majority) of
Ukrainian people wanted him out, there is ample evidence of pro-Western, third
party interference, beginning with Victoria Nuland, John McCain, USAID,
National Endowment for Democracy (who apparently organize very well on Facebook
and Twitter), etc. Why for instance are so many policemen dead and wounded, and
yet no one has investigated this in the new government?

The other point to consider in the big picture is US involvement with Ukraine
going back to 1949, when the CIA and strongly anti-Soviet Defense Secretary
James Forrestal created a guerrilla army codenamed ‘Nightingale,’ made up of
ultra-nationalist Ukrainians. The Nazis originally set up the prototype of this
militia up in 1941 to wreak havoc in famine-racked regions where Soviet control
was loose, carrying out the murder of 1000s of Jews, Soviets, and Poles who
opposed a separate Ukrainian state. 

Beginning in 1949, for 5 years the CIA parachuted Ukrainian infiltrators into
the region. To the Soviets it was as if the US were infiltrating guerrillas
into Canada or Mexico. 

The big picture is the US has never given up on using Ukraine as a launching
pad to the underbelly of the Soviet Union, now a reduced Russia. This Cold War
2.0 policy continues in a most deadly fashion, and whether they know it or not,
the Ukrainian civilian population in the middle has suffered greatly from this
ideological crusade.

\begin{multicols}{2}
\ii{31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.pic.1}
\ii{31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.pic.1.cmt}

\ii{31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.pic.2}
\ii{31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.pic.2.cmt}

\ii{31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.pic.3}
\ii{31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.pic.3.cmt}

\ii{31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.pic.4}
\ii{31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.pic.4.cmt}
\end{multicols}
