% vim: keymap=russian-jcukenwin
%%beginhead 
 
%%file 16_03_2023.fb.karpenko_sergij.mariupol.1.segodnya_rovno_god_k.eng
%%parent 16_03_2023.fb.karpenko_sergij.mariupol.1.segodnya_rovno_god_k
 
%%url 
 
%%author_id 
%%date 
 
%%tags 
%%title 
 
%%endhead 

Today is exactly one year since my family left Mariupol. sorry for the roughness
Chronicle
Day 0
just an ordinary day. Yesterday the bald spoke with the recognition of the republic of dambass... Well, he spoke and spoke, he has been scratching this balalaika for eight years... he clearly doesn't have enough strength to invade and capture, why would he climb?!?
By evening, sources in the local police wrote that the invasion will be tomorrow. Decided that it will be more visible in the morning
Day 1
At 4:00, the explosions of rockets began around the city. The Internet said the bald head is speaking. Turned on the broadcast: special military operation... blah blah blah... turned off the .... I was thinking of going to work, my wife talked me. I went scouting: queues for ATMs, for water, cigarettes... long queues ... by the evening, there was a persistent sensation that it was necessary to fall from the left bank, the grads went in packages, without stopping, through the suburbs, and around the city precisely tried to work with barrel art from the east and northeast. If I had only leaned on the experience of eight years, I would have stayed home, but my intuition kept saying "it's time to go!" "
We decided to go to our parents, this is the very west of the city, there are fewer options that come to mind... took the cats and mother-in-law... Took stuff for a couple of days
Day 2
рите Get your water in
не It's in the tap, isn't it?
⁃ Dial...
Ку Where to?
тон 2 tons will not be redundant in the drip irrigation container
Lets go get our groove on ... Gas stations are all already closed, even if I want to leave the city now, I'll be 300km in the best case scenario, and they still need to be passed, and it eats you up on a bare foot too...
Okay in the store: a sack of potatoes, oils 5l, flour, water... oh you can still pay by card here, you have to... [and why didn't I smoke cigarettes then a ram?!? ] the people are nervous smari, if it weren't for the military around, it would have already been a mess...
Day 5
So many things left at home... Well, we were going for a couple of days... they say the city is already surrounded... we lie down, the lights went out in the evening. Along with him, there is a connection, any.
Honey, would you like a trick?
I take potatoes, a bandage, a saucer, sunflower oil. Voila, the Kaganets is ready) for the near future, this is our light source in the evening...
Day 6 in the city, looters are all over the place to hide the car. My neighbor's garage is empty... hid it
Day 7
The water is turned off. And I have been saying !
Day 8
Water in the tanks froze. -12 at night is not it for you... stepped out on the porch in the evening, facing south. BJP won in my town The roar should be on the right in the west, where the sun has set, and it to the left, where the city is. The city is on fire, it's household gas flashing all over the city
Day 9
they turned off the gas ........
Day 10
I need to pick up my grandma from downtown, it's already too crowded. Picked up. Poor thing doesn't know where she is or why, get me home please..
Found a kerosene, the newest Soviet-depovo kerosene... In the neighbor's garden, for some reason, a half a gallon of kerosene has been failing for several years... filled up... Burns like hell...
Cooking over the campfire is the fun... exactly one day until firewood is all raw and it's an all day process... pancakes instead of bread, hot drinks instead of everything... pour boiling water in thermos!.. is there any coal left? Cover yourself, put a cauldron with technical water, it will at least heat the room in which we sleep, a summer room without insulation with eternal condensate on the walls...
Day 13
today is March eighth, there is moonshine, a bottle of champagne, a column and music on the phone. Let's celebrate, sing and dance...
Day 14
Orcs bombed the maternity hospital, third... a shell came to us too. Five meters from my parent's house. The second floor extended by skill. Children spent the night there, fortunately, they were not there at that time. The glass was taken out, now everyone is spending the night in summer houses... also wrecked one of our cars
Day 15
The neighbor has film, they tightened the windows in the house
Day 16
We drain gasoline with a scoop from a broken car, now we have no stock...
Day 17
Must go fetch some water... four "young ones" two eggplants in their hands and went to the spring... I really want to smoke...
We got there, gathered water, met men, had a smoke)
Learned the news: one shop in the city operates, there are long-kilometer queues, fights in the northwestern part of the city, separatists enter on tanks burn them, they fall with arta according to the development, looters trade slowly or change: a block of cigarettes-liter of gasoline, one hundred bucks-20000 UAH, a pack of cigarettes - 500 UAH ... dog
There are a lot of broken houses and cars along the road from that shelling...
In short, they returned home, took the car and filled 300 liters in all the containers. This is a little for a crowd of 10
Day 19
They say there's a net upstairs near the school... is off .... I climbed the roofs for a long time, skins in smoke, I need to... caught the net, talked to a relative from the tenth time, it was enough to say that we are alive to explain...
Day 20
And let's go half the net... oh, what is this? At the top of a pile of cars towards Melekino with white bandages and the inscriptions "children", an endless swirl to the horizon. What is this? Is it possible to drive out? Corridor? Zaporozhye? Off to consult with my family... Before that, I checked the tap on the water barrel every day... always not a drop, and on this day it spread, which is not a sign like stay, there is still food, water too... nah, gotta hit the nail on the head.. maybe tomorrow ? Not today .. gathered in an hour and a half, on the clock about 2 o'clock in the afternoon, with God... 10 people for two cars and two cats for one carrier... Leaked gasoline came in handy
By the curfew we managed to get to Berdyansk, along the way there are a bunch of roadblocks with various non-Ukrainian faces in homeless green uniforms with white headbands. The "aswabadites" of their mothers... It was safe everywhere that there were children and old people in the cars, that day there were so many cars that they even had no time to observe superficially.
We arrived almost to Tokmak, sat on the letter X, there the Asvabadites wrapped us up, said to stay the night in the cars near the landing, do not get burned... volunteers came from the village, let's place the children to us. We are scared, where will we put the kids?!? Off to school we go, there's hot food.
Ate, even some swear words gave us a bed on the floor, gave birth to women and children, they didn't sleep well themselves, it's bloody cold...
Day 21
7:00 am here we go ..... Tokmak, Vasilyevka... roadblocks stretch and stretch everywhere... We arrived at Zaporozhye at one o'clock in the afternoon. Handsome bridge at the entrance from the south blown up... need to take a detour. There they launch cars at a rate of 50 and they are afraid of shelling... We entered something around 4 p.m. ... and then the web started to break through... hundreds of messages from friends with support and questions throughout March... even now I have tears in my eyes... we came, some settled, washed, read the news of the day: a bombed drama theater with people, ships began to work along the coast, where we lived just yesterday... that's how they jumped out at the last moment...
Already later, reports of atrocities in the Kiev region began to come, about the scale of the genocide in Mariupol, and it became clear what was not obvious on day 0: they do not have the strength to seize the territory. If grabbing is the goal. And here's to the genocide...
