% vim: keymap=russian-jcukenwin
%%beginhead 
 
%%file 29_04_2022.fb.danilova_inna.harkov.1.smi_molchit.eng
%%parent 29_04_2022.fb.danilova_inna.harkov.1.smi_molchit
 
%%url 
 
%%author_id 
%%date 
 
%%tags 
%%title 
 
%%endhead 

WHY IS THE MEDIA SILENT !? 

Kharkov holds on to its last strength, thanks to its spirit and desire to live!

Thanks to our mayor Igor Terekhov and the heads of district administrations who
try to save the lives of the people and the heart of the city by providing
people with warmth, light, water, food and shelter.

But for some reason the media stopped talking about Kharkov, which has been
bombed since the first day of the war. There was not a single day that the
bombs did not explode and there was silence. Every day houses, parks, streets,
buildings crash and people die.

Kharkiv residents are left without a roof over their heads and the means for
their existence. Where do they go? How to live by them? What should I feed my
children?

There is no work to do. And if it was, it would be impossible to get under the
bullets on it. Transport is not moving. There are few medicines in the
pharmacy. The choices are poor. And what it is, is incredibly expensive. People
got no money.

Kharkov is dying. Why aren't they talking about this?

We are all worried about Odessa and Kiev, but in Kharkov every day is the same.
The bombing and destruction of the city of Kharkov do not stop, but on the
contrary, it only increases every day. 30-40 rockets and bombs fly into the
city EVERY DAY!

The end and the edge is not visible to this.

If this continues, there will be nothing left of the city. It will be a burnt
earth, with burnt and empty buildings.

Kharkov needs to be talked about. This is not just a hero city, this is the
soul of our country, this is the first capital of Ukraine.

Lord, save the city of Kharkov @igg{fbicon.hands.pray} 🏻
