% vim: keymap=russian-jcukenwin
%%beginhead 
 
%%file topics.ukraina.rossia.cit
%%parent topics.ukraina.rossia
 
%%url 
 
%%author_id 
%%date 
 
%%tags 
%%title 
 
%%endhead 

%%%cit
%%%cit_head
%%%cit_pic
%%%cit_text
Ukraine is the motherland of all Russia. From Kaliningrad to Kamchatka
Ukrainian surnames populate every city and village. Kiev is the mother of all
Russian cities and the Kievan RUS are the mother of all Russian people.
Ukrainians are Russians, the ones promoting the idea that they are a separate
people are from the west of modern Ukraine which was Poland and Lithuania
formerly. There was no famine in 1913, there was famine in 1931-32 and millions
died all across Russia from this famine. There were many reasons for the high
death toll, partly because Stalin had murdered all the best farm managers as
Kulaki, my German Mennonite ancestors among them, and to a lesser degree the
indifference of bureaucrats in Moscow and Kiev. Millions also died on the
Indian sub-continent fromthe same famine. Ukrainian history is Russian history,
the eastward march of Muscovy was a continuation of the north eastward march of
Kievan Rus! I would not be so impressed with Harvard professors, graduate
students at Harvard are no better at geography than the set decorators that
work at CNN! Lastly, Ukraine is a Russian word, it means borderland, borderland
of the Kievan Rus, who dwell in the modern great nation of Russia that all the
ancestors of the true Ukrainian people pioneered and created!!!
%%%cit_comment
\iusr{Vincenzo Lachimera}
%%%cit_title
\citTitle{'Nightingale' in Ukraine}, Oliver Stone, facebook, 31.12.2014
%%%endcit
