% vim: keymap=russian-jcukenwin
%%beginhead 
 
%%file songs.deti.serdcu_dorogoe
%%parent songs.deti
 
%%url 
 
%%author 
%%author_id 
%%author_url 
 
%%tags 
%%title 
 
%%endhead 

\url{http://pesenok.ru/5/deti-poyut/tekst-pesni-Serdtsu-dorogoe}

Просыпается Земля, радостно сегодня встречаем лето
Рано утром выйду я, наберу цветов и березы веток
Перезвон колоколов в небеса летит, возвещая праздник.
В праздник Троицы Святой наполняется воздух добротой.
Припев:
Я скажу тебе здравствуй: солнце золотое, небо голубое
Слава Богу за то, что все вокруг живое, сердцу дорогое

2 . Изумрудная трава, босиком закружим в ней хороводы
И венки из васильков снимем с головы и отправим в воду
Сколько радости вокруг, веточки березы повсюду в храме
Ангельскою чистотой наполняет сердца нам Дух Святой.

3. Я сегодня не грущу, солнышко сияет и много света. Я с молитвой обращусь,
Троица Святая храни планету. Я ликую и пою, мир и счастье людям, Господь меж
нами. Ангельскою чистотой наполняет сердца нам Дух Святой.

→ http://pesenok.ru/5/deti-poyut/tekst-pesni-Serdtsu-dorogoe 

 Earth wakes up, today we meet joyfully
Early in the morning I will leave, I will type flowers and birches of branches
The chime of the bells to heaven flies, announcing the holiday.
On the feast of the Holy Trinity, the air is filled with kindness.
Chorus:
I'll tell you hello: the sun is golden, the sky is blue
Praise God that everything around is alive, dear to the heart

2. Emerald grass, barefoot round it roundelay
And we will remove the wreaths of cornflowers from the head and send them into the water
How much joy around, birch twigs everywhere in the temple
The Holy Spirit fills the heart with an angelic purity.

3. I'm not sad today, the sun is shining and a lot of light. I pray with prayer, Holy Trinity preserve the planet. I rejoice and sing, peace and happiness to people, the Lord is between us. The Holy Spirit fills the heart with an angelic purity.
→ http://pesenok.ru/5/deti-poyut/tekst-pesni-Serdtsu-dorogoe 
