% vim: keymap=russian-jcukenwin
%%beginhead 
 
%%file 29_04_2022.fb.fb_group.story_kiev_ua.1.hronika_harkov.eng
%%parent 29_04_2022.fb.fb_group.story_kiev_ua.1.hronika_harkov
 
%%url 
 
%%author_id 
%%date 
 
%%tags 
%%title 
 
%%endhead 

CHRONICLES OF UNDECLARED WAR
Day sixty four. The first capital city.
Kharkiv is another wound that does not let go of its pain for a minute.
Kharkiv, we had almost two years with you. During which it was different, but these two years - for a lifetime.
For when the day comes,
The war will end ,
Lost myself there,
Saw it all the way to the bottom.
Kharkiv, once you became a real revelation for me. When I first came to you, I was expecting to see an industrial monster, and unexpectedly met a park city.
And from my soul
Puts the weapons down,
Is she really the one
So want warm tears?
Kharkiv, it wasn't love at first sight. Sumy, Darwin, Pushkin... step by step I discovered you. Freedom Square, State Prom, Karazin University... you revealed yourself to me every day, every night. In all of its glory. Mesmerized and inspired.
Give me a hug, give me a hug.
And don't let it go like that anymore.
Hug me hug me hug me hug
Your spring will come let it.
Kharkiv, yes, your spring is coming. And then - another and more. And no enemy will put you on your knees, no one will conquer.
Kharkiv, yes, we will still have it. Because this is for life.
PS:
Svyatoslav Vakarchuk shot the clip "Hugs" specially for the Venice Bienale 2022.
The shooting took place on April 14 in Kharkiv, in the yard of the Palace of Labor, which was destroyed by Russian bombings. The building, built in 1916, represented two World Wars, but suffered significant damage during the Russian invasion of Ukraine in 2022.
Among the participants of the string quartet that helped Vakarchuk in recording the song - Kharkiv musician, cellist Denis Karachentsev, who is known for his musical performances among Kharkiv ruins.
PPS:
Kharkiv.
Photo: Stepanov Farid, 2017.
