% vim: keymap=russian-jcukenwin
%%beginhead 
 
%%file 31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.pic.6.cmt
%%parent 31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine
 
%%url 
 
%%author_id 
%%date 
 
%%tags 
%%title 
 
%%endhead 

\iusr{William F. Smith}

Mr. Stone, please base your film on facts, not conjecture or speculation.
Careful research will show you that your reported entering premise, that the
USG was in any way involved in the ouster of Yanukovych, is completely off
base. Ukraine and the Ukrainians deserve the facts; not Russian propaganda.

\iusr{Валя Яценко}

Варвары! Чего они хотят, разрушая свою Родину..

\iusr{Paul Niland}

And the second most corrupt dictator in modern history is defeated. This was
the end. Yanukovych had fled. Ukraine was at peace. Then Russia invaded to
discredit the fact that the revolution was just about corruption, and the
reasons for that are extremely obvious.


\iusr{Robert De Cherry}
Who is shooting who?

\iusr{Anton Hlushko}
Настасья, они - это КТО? И какую страну - Украину, Россию или СССР?

\begin{itemize} % {
\iusr{Anton Hlushko}
Ну Вам виднее в Екатеринбурге, конечно, особенно фашистов и хунту, это уж точно!
\end{itemize} % }

\iusr{Olga Stellmach}
Europe's values!

\begin{itemize} % {
\iusr{Alex Manikhin}
Russia - the peacemaker!

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10885480_10205979975760328_5169933621630991326_n.jpg?_nc_cat=111&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=NML_vch4SBEAX9mbpkA&_nc_ht=scontent-frx5-1.xx&oh=0a0fccc5ef858565e5d6166bf7e3ba54&oe=61CB9B65
  @width 0.4
\fi

\iusr{Olga Stellmach}
Just it!

\end{itemize} % }
