%%beginhead 
 
%%file 01_11_2022.fb.ryzhenko_sergij.ua.likar.dnepr.1.operats__dovsh__za_
%%parent 01_11_2022
 
%%url https://www.facebook.com/rsa010963/posts/pfbid02ghLjQ2n2QizQCuKZTHuAPKzsR7WyjS3NAsjSsmiVEYAWNiEdVE5k44yaFWoda5X8l
 
%%author_id ryzhenko_sergij.ua.likar.dnepr
%%date 01_11_2022
 
%%tags 
%%title Операції довші за життя…
 
%%endhead 

\subsection{Операції довші за життя...}
\label{sec:01_11_2022.fb.ryzhenko_sergij.ua.likar.dnepr.1.operats__dovsh__za_}

\Purl{https://www.facebook.com/rsa010963/posts/pfbid02ghLjQ2n2QizQCuKZTHuAPKzsR7WyjS3NAsjSsmiVEYAWNiEdVE5k44yaFWoda5X8l}
\ifcmt
 author_begin
   author_id ryzhenko_sergij.ua.likar.dnepr
 author_end
\fi

Операції довші за життя...

25 жовтня на заправці в Дніпрі пролунав вибух.

Настя з Олексієм, їм по 28 років, отримали важкі поранення.

Машину прорізали десятки уламків.

Олексій, втрачаючи багато крові, робив все можливе, щоб допомогти дружині
вибратись.

До останньої миті підтримував її, закриваючі рани руками.

Бригада екстреної медичної допомоги (керівник Радий Шевченко) миттєво доставила
поранені тіла в реанімацію Мечникова, надаючи саму важливу екстрену допомогу,
рятуючи від кровотечі.

Настю оперували двічі.

Торакальний хірург Андрей Снисарь близько серця дістав два відламка.

Потім тривалі складні операції на хребці.

Весь час в реанімації були поруч, дотягуючись один до одного руками.

Вставати поки не можуть, функція нижніх кінцівок, нажаль, дуже постраждала.

Восьмирічний син підходить по черзі до мами і до тата, не розуміючі важкість їх
стану, сприймаючи все як дитячу гру.

Попереду довгий шлях до одужання.

Яким він буде покаже час...

Operations are longer than life...

On October 25, an explosion was heard at a gas station in Dnieper.

Nastya and Alexei, they are 28 years old, were seriously injured.

The car was cut through by dozens of debris.

Alexei, losing a lot of blood, did everything possible to help his wife get
out.

Until the last moment he supported her, closing the wounds with his hands.

The emergency medical team (headed by Radii Shevchenko) instantly delivered the
wounded to Mechnikov's intensive care unit, providing the most important
emergency assistance, saving them from bleeding.

Nastya was operated twice.

Thoracic surgeon Andrii Snysar drew out two fragments near her heart.

Then were long and complex operations on the vertebra. 

All time in intensive care they were nearby, reaching each other with their
hands.

They cannot stand up yet, the function of the lower extremities, unfortunately,
has suffered greatly.

The eight-year-old son approaches his mother and father in turn, not
understanding the severity of their condition, perceiving everything as a game.

They have a long road to recovery.

Time will show how it will be...
