% vim: keymap=russian-jcukenwin
%%beginhead 
 
%%file 03_04_2023.fb.korovanenkova_natalia.mariupol.1.31_03_2022_blok_post.eng
%%parent 03_04_2023.fb.korovanenkova_natalia.mariupol.1.31_03_2022_blok_post
 
%%url 
 
%%author_id 
%%date 
 
%%tags 
%%title 
 
%%endhead 

#Маріуполь_2022 #як_це_було
31.03.2022
Block post .
It's been over an hour. We are still standing at the exit from the parade, there is not a single bus, we are waiting..
Fear and cold, two feelings merged together, the only desire, to fall on the ground and never get up again.
Cars passing by, leaving from
cities are dirty, broken and scared.
"Washed" and cool people enter the city, a jeep comes by, a woman well-groomed with excellent make-up comes out, I look at her as if she's foreign...
The guys are bound by the tape, so they continue to stand, the son smokes a cigarette, hands it to each one of them.
Someone says, "go on, private people are standing there, maybe you can make an agreement"
I grab the dogs and we continue to go to the gas station. There are really a lot of private traders, when they see us, they all stop: "Where are you going?" "
As in the best times, when you arrive at the station, you go out on the platform .... and taxi drivers offer their services.
"To us in Berdyansk"
The price of the question is only 400 uae, that's enough for us! I have 500..
We just on our way.
About 100 km to Berdyansk, we drove about four hours, it didn't take long.
Seven block of posts everyone has the same procedure, documents, we get out of the car, personal inspection, the son is undressed to his underwear, his bruises are examined, his head is broken, bruises on his face, the jacket is covered in blood, all the time it was necessary to explain that these are the consequences of the piles.
He was probably saved by the fact that he was going with me, with my mother,
Even the dogs were distracting themselves.
All but one blocked posts were checked.
The post, where the pre-examination was the most horrible, they behaved somehow decisively, indifferent, but they emanated a sense of cruelty and in this their indifference felt meaningless to us...
The driver at each checkpoint gave the "inspectors" cigarettes, then coffee, and a "thank you" in the feet.
The last block post, we are entering the city, the driver helps to settle into the house with the mistress.
Occupied Berdyansk, lives a peaceful life, yellow-blue flags are majority at the bus station.
Transport goes, shops, market, private works.
My son asks me "can you hear that??? "
I'm starting to listen, is it really a plane??
Listen:" This is the City ! The sounds of a peaceful city! "
We settled in comfortably, a room, a large kitchen, an electric oven, and most importantly, a heater and a shower, all this for 300 UAH a day.
The hostess brought us hot soup, while we were eating she just stood there and cried.
The Berdyansk market is noisy, Bread! Berdyansk sausages! huge chebureks, everything works! Private, service centers where you can charge and top up your phone.
The city is under occupation, but there is no war here.
Going to the market, the first thing we go to the service center to charge the phone and top up the bill.
The locals say that communication in the city is poor.
Great connection, y’all don’t know what a “bad connection” is and god forbid you never do.
I was not a subscriber to Kyivstar , but only thanks to them I could at least somehow get in touch during the most difficult moments in Mariupol, and then in Berdyansk
Thank you so much guys!
The market is booming .
I will exchange all my remaining wealth, 100 ue in exchange,
,I have enough to survive for three days, a thousand hryvnias for housing, and the rest to "walk" on the market.
Prices in the market are fantastic, dried bagels 500 gr, a bag of coffee 25, sugar 150, but Berdyan sausages the price is nice, as it was.
But they said that prices had already fallen, a week ago, when there was a main influx from Mariupol, it was much more expensive.
Almost at every step I meet acquaintances from Mariupol.
Neighbours ! Alive !
Dima with her family, how glad we were to see each other. We are still dirty, not washed, hungry, and they already look "respectable", they have been in Berdyansk for ten days.
The phone has already been charged in the service room, the bill was topped up so that I could make a call. Asking: "How much do I owe?" ", guys refuse to take money, they say you need it more,
Thank you)
And here it is, the first call. I can hear you ! Masha's voice, I can't speak, my throat squeezed. all I remember was that I could say: "We are in Berdyansk, we got out of the city".....
Returning to the hostess, the dogs were left closed there.
With bread and sausage! with the food!
NOW we're going to get a day's sleep..
We need strength for the road, in a couple of days we need to leave the occupied Berdyansk to Zaporozhye.
And this, as it turned out, will not be easy to do.
