% vim: keymap=russian-jcukenwin
%%beginhead 
 
%%file 31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.cmt.1.passarelli
%%parent 31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.cmt
 
%%url 
 
%%author_id 
%%date 
 
%%tags 
%%title 
 
%%endhead 
\paragraph{Piero Passarelli - Bravo Oliver.... I salute you for your courage and intelligence ...}

\begin{itemize} % {
\iusr{Piero Passarelli}

Bravo Oliver.... I salute you for your courage and intelligence in understanding
the real truth. Please help all of us.... thank you.

\iusr{Сергей Мельниченко}
Mr. Stone.

1. Any American police will tell you that any non-serial killing, which has not
been investigated in hot pursuit will not ever investigated.

In addition. Third party could be the FSB.

2. Poles and Jews have an opinion different from that says the Soviet-Russian
propaganda. Ask the Poles and the Jews who lived in Poland and Ukraine.

3. The Cold War 2.0 began with the annexation of the Crimea from Ukraine.

\iusr{Andrea Chalupa}

You are lying to your fans, Mr Stone. An investigation is ongoing; I know
because I was recently in Kyiv talking to people involved. Sorry Ukraine isn't
moving fast enough for you; it's fighting an invasion by Putin and a collapsed
economy thanks to Yanukovych and his circle stealing an estimated \$70 billion.

Social media helped fuel the revolution; for instance, Ukrainians in the
diaspora around the world could watch Ukrainians in Kyiv being beaten and shot
on multiple livestream news feeds; and in response they organized twitter
storms and facebook storms putting pressure on world leaders to act and on
journalists to cover protesters being killed fighting for Democracy in Ukraine.

The US/EU tried to get protesters to sign a truce with Yanukovych, letting him
stay in power, but the protesters refused and threatened to storm his palace if
he didn't leave by the following morning; Yanukovych fled town the next
morning. Maidan succeeded despite the West, not because of it. If the
protesters had listened to the US/EU then your buddy Yanukovych would still be
living large in his palace paid for by stolen tax dollars. Shame on you for
lying to your fans!!! Come to Ukraine, meet with journalists and scholars and
reform leaders, or are you too scared of your alternative reality being
shattered and of losing your film funding?

\iusr{Anton Shekhovtsov}

Oliver Stone may be critical of the US policies, but his orientalist approach
towards the Ukrainians, whom he is depriving of any agency, reveals typical
American racism. He is essentially an American supremacist, of the worst kind,
because he combines a belief in the omnipotence of the US with self-indulgent
American guilt.

\iusr{Michael Carrier}

I have family in Ukraine, and they are deeply offended at your patronising view
that this a US driven protest. This is rather an out growth of democratic
protest by the young generation who want to end corruption and kleptocracy.

\begin{itemize} % {
\iusr{Oleksiy Babansky}

so, Soros must have been financing the corrupt cleptocratic govt in Ukraine,
because THEY had been the prime reason for unrest and crisis.

It's like, you would have a bad knee, but instead of advising you to go to the
doctor I would blame you for rocking the boat in favor of the USA. "Soros paid
you to injure your knee so that you destabilize our otherwise great nation with
false accusations!"

Yes, what you say is exactly THAT kind of absurd.

\iusr{Oleksiy Babansky}

It's so funny how pro-Moscow voices blame the US but completely avoid talking
about the sheer depravity and corruption of the cleptocratic marionettes who
rob and bleed the country dry BEFORE the crisis starts.

So convenient...
\end{itemize} % }

\iusr{Влад Бурлуцкий}
Mr Stone is a Putin's useful idiot

\iusr{Joanna Prisiajniouk}

You have no conscience Mr. Stone for not thoroughly documenting the truth! Your
comments, thoughts of history and plans for this movie is a huge lie and
disservice to millions of people and you should seriously think about this and
your reputation!!! All who know the truth will not allow your heinous attempt
to make your profit on the souls of the Ukrainian nation and all its ethnic/non
ethnic citizens along with its worldwide diaspora that knows Ukraine's history
well better than you! You have not made any attempts to contact the "experts"
of Ukraine's best on this issue! SHAME, SHAME ON YOU!!!!

\begin{itemize} % {
\iusr{Joanna Prisiajniouk}
Trolls all over this post who are pro Russian idiots, haters and liars! Shame in all of you too! Go to hell!
\end{itemize} % }

\iusr{Ксения Зайцева}

Do you think that CIA orgaized 3000+ people to respond to your post in less
than 24 hours?

\begin{itemize} % {
\iusr{Kosako Sonico}
It Could be done idiot.

\iusr{Dimitri Halby}

I personally know a few dozens including myself who have reacted for free.
Conspirationists are people you can easily manipulate by telling them there is
a plot behind everything...


\iusr{Vladimir Grigorev}
there are very many who iditised
by SIA campaign

\iusr{Emil Wojtechko}
Putin believes Internet was invented by the CIA to undermine Russia. Stone is just as stupid.

\iusr{Marijka Stadnyk}
Trolls and Putin lovers still peddling the 100\% Putin funded "Global Research. Everyone else discarded it long ago.

\iusr{Marijka Stadnyk}

No one loves the western banks, lifestyle and freedom more than the Russian
billionaires. As soon as Russians make some money, they rush to the west, to
invest, to dine, to play, to experience real freedom. That is a fact!

\end{itemize} % }

\iusr{Mykola Voskalo}

>>> back to 1949, when the CIA and strongly anti-Soviet Defense Secretary James
Forrestal created a guerrilla army codenamed ‘Nightingale

>>> prototype of this militia up in 1941 to wreak havoc in famine-racked
regions where Soviet control was loose

you look stupid, mr stone. get your facts straight and waging crusade against
us government you should stay away from ukraine or at least talk to some other
ukrainians, not just yanukovich

\begin{itemize} % {
\iusr{Kosako Sonico}
You look as a US paid idiot, moron

\iusr{Julia Mglosiek}
O, Kosako Sonico - belive me, you look like russian paid idiot. Of course, with Mr. Paid-Russia-O.Stone.
\end{itemize} % }

\iusr{Svitlana Tuchynska}

The truth is much simpler, Mr. Stone. (As it often is) Ukrainians have chosen
European path, just as their neighbors from Poland, Romania, Moldova and Baltic
states have before. But Putin, with his fantasies of bringing back to life
Russian empire/USSR just could not take it. The US, Europe, and other factors
probably played some role, but the core is just that simple. Talk about black
cats and dark rooms.

\begin{itemize} % {
\iusr{Изюзь Изязев}

Референдум юкрэйниансов был? Помнится в двухтысячных украинские депутаты
выбрали другой формат рады, но декаду назаседали в прежнем. You really think
USSR was something bad and gave ex-republics nothing?)

\iusr{Andrea Bodrati}

@ Ruslan: you are right USSR gave ex-republics a lot, for example the
Holodomor, concentration camps, deprivation of private property, forced
transfer of millions of people. All great achivements indeed.

\iusr{Vincent van den Breemen}

\href{https://www.youtube.com/watch?v=yu8KTiLsLJw}{%
Welcome to Nulandistan: Propaganda and the Crisis in Ukraine, GlobalResearchTV, youtube, 24.05.2014
}

\iusr{Vincent van den Breemen}

Svitlana Tuchynska,.. Stay away from the EU... its a farce. The EU is a
fairytail. It failed. Even in the Netherlands alot of people hate te EU. See
what it brings! People overhere get sick off the EU. Don't choose the European
Path,... choose wise!

\iusr{Ramunas Cesonis}

Speak for yourself, Vincent. Good point, Svitlana. And welcome to Europe!

\end{itemize} % }

\iusr{Oksana Halby}

Volunteers organize using FB because there is no other means for people to get
organized against corruption and Kremlin's hand on Ukraine, only social media.
You did not live in former USSR for years and cannot imagine the strength of
Kremlin's propaganda all those years and its attempts to still control minds
now, like it was behind Iron curtain. My husband was accused of being paid by
CIA for supporting Ukraine but I know his motives are my family in Ukraine.
Hundreds of people in Ireland self-organized on FB to support Ukraine, we were
inspired by Ukrainians standing against corruption and Kremlin's hand on
Ukraine. No one paid for organising us. We are donating and collecting money
for sending help to Ukraine because we care. We started our FB groups and saw
them growing; social media unites people who care.

\iusr{Kostyantyn Bazhenov}

This is all very interesting, albeit not very true, but why are you not equally
interested in the crimes of the Russians, how they invaded Ukraine through
Crimea, how they invaded the East of Ukraine, with their trained mercenary
groups, which brings back the memory of the Soviet coup in Afghanistan, how the
Russians were shooting at their own peacekeepers in South Ossetia, in order to
start an invasion of Georgia in 2008. You should examine your facts before you
jump to conclusions. The patterns of Russian organized violence, terrorism and
coups is very clear in Ukraine as well. Have you considered that the shooters
could be Russians?

\iusr{Eric Kraus}

As for corruption - Ukraine had a series of extraordinarily corrupt
governments. Both pro-Western and pro-Russian.

Timoshenko could go mile-per-mile against Yanukovich any day - the Gas
Princesse become a billionaire stealing gas, and is widely believed to have
eliminated numerous competitors - with extreme prejudice.

None of this justifies a foreign sponsored coup d'etat which has torn the
country to shreds. Like Libya, like Syria, like Iraq, The Empire saw them as
mere political pawns to be played with at will - and if the situation of the
locals went from bad to catastrophic - that is no real concern to those hand
which are moving the pieces.

\iusr{Eric Kraus}

You, sir, are speaking the truth to people who are used to living on a diet of
lies. Of course they rebel at the suggestion that their entire world-view has
been hideously distorted by the tame corporate media. Please do not apologise
for anything!

\begin{itemize} % {
\iusr{Max Ballotta}

I completely concur with Stone's point of view, speaking as a European, as
senior partner of a Moscow-based law firm, and as a lecturer in a Masters on
Russia at the University of Bologna, Italy.

\end{itemize} % }

\iusr{Sergiy Stakhovsky}

This post is even more pathetic then your first one... CIA was established in
1947... so 2 years into existence they already operating outside of USA during
WW2?? As somebody said "you have great problems with logic"

If on the territory of our country there were military presence of a foreign
country than i blame Yanukovich for it as he destroyed our defense ministry and
let FSB takeover. Don't be ridiculous mr. Stone you have no clue what you are
writing.

\begin{itemize} % {
\iusr{Павел Лис}
Стаховский ты жалкое чмо

\iusr{Sergiy Stakhovsky}

Смотря кто судит ))

\iusr{Eugen F. Korzhenevski}
Мальчик Паша-серьезный судья,да

\iusr{Gerry Padilla}

It is a silly logical mistake to think that it is impossible for the CIA to
have done this two years into their career. The fact that the CIA was young
doesn't make the fact impossible.

\iusr{Sergiy Stakhovsky}

Do you actually know what was going on during WW2?? The fact that they
presumably supported something during the war in the war zone is a great
speculation..

\iusr{Роман Деньгин}

Why are you asking, Sergiy? What about you? Do you know? Can you prove it? No?
Get lost then!

\iusr{Sergiy Stakhovsky}

You are commenting my post) not vise versa so please be gone))

\iusr{Andrew Joseph}

CIA was the OSS under a different name so you are hopelessly unaware of things.
OSS was around since 1942 so not only was the CIA around (albeit under a
different name) since 1942 at the most conservative estimation, but to claim
that an existence of 5 years would preclude what Mr. Stone claimed is
absolutely ludicrous. Don't debate people with brains - we know the reality.

\iusr{Ксения Зайцева}
\textbf{Andrew Kahn}, have you watched "Usual Suspects"? It is a good movie. You might recognize yourself in agent Kujan.

\iusr{Kaptan Hammet}
1949 is supposed to be "during" the ww2? Where did you take history classes?

\iusr{Sergiy Stakhovsky}

Shoots))) Haha you are right )) just after, during Cold War. OSS don't make
much difference as for intelligence service to work you need network ..for that
you need time..the rest speculation)

\iusr{Sergiy Stakhovsky}

And how you create network during WAR?

\iusr{Sergiy Stakhovsky}

Regime change is one thing.. but to declare that they've been doing it since
1947 is a little to much for my taste. Again I don't care weather they were
involved in euromaydan. What happened was right thing to happen .. The
consequences were unpredictable...

\iusr{Caroline Muzyka McCrea}

Ya guys .... the CIA infiltrated all the Baba's and Dido's in Kiev to bring
food, stand out in the cold for 3 long months and haul in as many tires as they
could to keep a big bon fire going. Seriously, is this what you believe!!!!
People protest all over the world for different reasons. Is the CIA and the
west behind them too.

\iusr{Vira Dziedzic}

Sergiy, Russia employs thousands to spread their own propaganda, Stone,
obviously, ever eager to bash USA, got payed a hefty sum to create his
"masterpiece"about the CIA involvement. Anyway, most of the people you are
arguing here are payed to do so. Stay strong, brother, Thruth always prevails
in in the end. Slava Ukraini!

\iusr{Yanis S. Dyakov}
truth prevails, too bad ukraine won't. sala ukrini

\iusr{Sergiy Stakhovsky}

says nobody who doesnt exist.. pseudo name and pseudo account.

\iusr{Abraham Hazou}
\href{https://www.youtube.com/watch?v=u7Z0incwC2w}{youtube link}

\iusr{Sergiy Stakhovsky}

You mean police force in russia??? i am trying to enjoy my conversation with BOATs ...

\iusr{Sergiy Stakhovsky}

Libya?? did you see any USA or NATO troops on the territory of my country?? i
saw only russians... so tell me please about this USA evil.. when russians are
slaughtering my countrymen..

\iusr{Sergiy Stakhovsky}

HAHHAAH yes yes yes....give me more of this fake)))bring it on!!! especially
the last one!!! VIOLENCE !! because \textbf{\#euromaydan} was a peaceful protest..no
weapons no intention of violence..

\iusr{Abraham Hazou}
\href{https://www.youtube.com/watch?v=RJR1wz7muFI}{youtube link}

"european values" , "democracy"

\iusr{Sergiy Stakhovsky}

Abraham ill tell you more... he deserved much more then just a bin.... you know
when you pass the point of fear??? when politicians are behaving like
gods... when because of them thousands are dying and hundreds walk free from
jail??? believe me much more then just a bin.

\iusr{Andrea Middendorf}

\ifcmt
  ig https://scontent-frx5-2.xx.fbcdn.net/v/t1.18169-9/10891673_831495756891668_7270105381672435300_n.jpg?_nc_cat=109&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=DHTHRIEXg7kAX_NV7MC&_nc_ht=scontent-frx5-2.xx&oh=22296a9c2132778c7e83cd35745f6f90&oe=61CA0024
  @width 0.4
\fi

\iusr{Sergiy Stakhovsky}
well better this then be a russian slave country

\iusr{Sergiy Stakhovsky}
and btw.... you support Gaza from EU... why dont you go and show your support there???

\iusr{Andrea Middendorf}

\ifcmt
  ig https://scontent-frt3-1.xx.fbcdn.net/v/t1.18169-9/10898176_831496330224944_6932553097935798989_n.jpg?_nc_cat=104&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=Ti0Y8cPaL90AX8_xWxp&_nc_ht=scontent-frt3-1.xx&oh=f7631976fe60b6a36a72dbdc4f363f69&oe=61CACDBC
  @width 0.4
\fi

\iusr{Sergiy Stakhovsky}

thats all uve got???

\iusr{Andrea Middendorf}

\ifcmt
  ig https://scontent-frt3-2.xx.fbcdn.net/v/t31.18172-8/10887678_831496716891572_1201410058240952396_o.jpg?_nc_cat=101&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=UUHAypHGx9wAX-g8q6M&_nc_oc=AQnctwdiVhLCUrHtqOSvOHYeRkOnjN8IvEoIyVLyz52Sduol8z8aFCrRaqgzvUPYW8M&_nc_ht=scontent-frt3-2.xx&oh=998abdc62d472e5ab6f1b9ff8b43110c&oe=61CAB05F
  @width 0.4
\fi

\iusr{Sergiy Stakhovsky}

more this is way to old... something new... like eating children or slaves

\iusr{Abraham Hazou}

sergiy, if anyone deserves the trash bin, it's porko, yats, svaboda leaders,
right sector thugs, and of course, kolomoisky. Your country is being robbed
blind and you sadly, can't see it at all. Hopefully soon Greece and the UK
finally exit the eu austerity hell you "maidanites" are cheer leading but can't
yet realize the damage done.

\iusr{Sergiy Stakhovsky}

BARBARIANS???? coming from a guy who admires KADYROV!!! yeah right... whatever... let us judge ourselfs and our country

\iusr{Sergiy Stakhovsky}

Again coming back to our sheep's, we will find the way to build our country.
we will find the way to restore our history(not russia want style) and its up
to us what the future brings to our country.

\iusr{Sergiy Stakhovsky}

and tell me about Bandera Joe... please do.. i am listening...

\iusr{Abraham Hazou}

bandera was so insane, the Nazi Germans put him under house arrest (but still
let him give orders to his "useful" terrorists) ... ww2 was messed up on all
sides, and bandera is no hero at all. Ukraine needs to drop his name.

\iusr{Sergiy Stakhovsky}

Again we shall decide upon that.. not you or no other. Bandera fought for
sovereignty of Ukraine, and thats good enough for me.. was he doing bad things
yes... but havent you done some bad things in your life??

\iusr{Sergiy Stakhovsky}

Or maybe Lenin was better?? or Stalin?? or Putin???

\iusr{Abraham Hazou}

I don't like either Lenin, Stalin, or bandera. The bad things bandera did, even
the German Nazis saw as barbaric (but still useful apparently) , they used you
just like nato is now.

Ukraine should be independent and a link between Russia and Europe, not an
eu/nato puppet against Russia for geopolitical agendas.

\iusr{Sergiy Stakhovsky}

well my head is actually above gunpoint.. you can bring all the nonsense you
have in your messed up head... again.. if Kadyrov is your hero there is not much
you can prove to me... and as it is my comment please leave))

\iusr{Костя Мирошниченко}

Уважаемый Сергей
прокомментируйте тогда пожалуйста Пашинского с винтовкой 18 февраля.

\href{https://www.youtube.com/watch?v=Sxmi87ILEQ4}{%
Куда Пашинский увез винтовку с глушителем? 18.02.2014, Фосген Заринян, youtube, 20.02.2014%
}

В багажнике - штурмовая винтовка на базе американской M16.  Установлен прибор
бесшумной и беспламенной стрельбы.  Флажок предохранителя - в положении
"огонь".

Автомобиль Honda, госномер АА 4774 СО (киевская регистрация).  Рядом - народный
депутат от ВО "Батькивщина" Сергей Пашинский.

Киев, район ул. Институтской, 18 февраля 2014 г.

\iusr{Sergiy Stakhovsky}

Abraham or whatever you are... Barbaric was how Ukrainians where treated in the
begining of 19th century.

\iusr{Sergiy Stakhovsky}

a vy do 18 fevrala nichego na maydane ne videli??? a?? nachinaja s 30
noyabra??? ili mozhet byli poboji, avtozaki itd???

\iusr{Sergiy Stakhovsky}

Kadyrov ))) no he is not for sale now... he is bought by Putin so there is now
way walking on ex-KGB )))

\iusr{Sergiy Stakhovsky}

Kadyrov killed his first russian officer when he was 17... and then he got Geroj
rosii ...pathetic isnt it?? get the medal for killing people of the country you
get medal from...

\iusr{Abraham Hazou}

Barbaric also how banderites responded, everyone was crazy but the crazies of
today use the violence the past to justify their violence today. Destroying
your own country in blind rage instead of building closer relations and making
sure the past mistakes are never repeated. You care about Ukraine's
sovereignty? Then for the sake of sanity and common sense, why the hell are you
about to join the eu when so many others want out?

\iusr{Abraham Hazou}

Kadyrov is a good example of making amends with the past and working to restore
stability in region as opposed to the Chechen terrorists that I've heard you
maidanites call "freedom fighters", many of them are now in isis, of course

\iusr{Костя Мирошниченко}

Видели, Сергей, все прекрасно всё видели. Янукович - редкостный идиот и это
знает вся страна. И никто его не пытается выгораживать. Он должен ответить за
свои преступления. Только это всё никак не обьясняет Пашинского с винтовкой...

Очень бы хотелось, чтобы такие публичные люди как Вы, высказывались по этим
вопросам не только на страничке Стоуна в фейсбуке, а например у наших Авакова и
Геращенко. Возможно они знают ответ на вопрос что делал Пашинский с винтовкой.

Спасибо за понимание. Удачи на кортах

\iusr{Sergiy Stakhovsky}

omg people.... wow... kadyrov is a good example... do you actually believe that
they where terrorist?? the chechens??? do you actually know who blow up the
buildings in Moscow?? i dont care about your opinion any more... sayonara

\iusr{Sergiy Stakhovsky}

destroying our country??? you mean russian invasion i guess ... well we are
defending our country... and believe me we will by any means.. whoever will come
to our country with a gun, will die from a gun.

\iusr{Sergiy Stakhovsky}

Konstantin, u Avakova i Geraschenko nado sprashyvat kuda ushel yanukovich(trudno
veritsa chto on ot nih ushel) pashynskij s vintovkoj, alfa fsb voprosov ochen
mnogo... otvetov k sozhaleniju my ne poluchim... revoluciju delajut romantiki, a
ispolzujut neogdaji.... ce la vie


\iusr{Michael Miles}

Well Sergiy, does the CIA pay you well? Oh yeah, I'd make sure you get dental.
Lol.

\iusr{Andrey Stebelskiy}

Good luck on Australian Open Sergiy, wish you the best! Many of them know
nothing about the real situation in Ukraine including dreamers like Oliver
Stone is.

\iusr{Andrey Stebelskiy}

I'll bet, that no one of you who are pretending being so smart here haven't
just a small tiny imagination and comprehension about ukrainian society,
history, culture, traditions and so on, cleverer like you can't feel that
delicate nerve of nationality we are, as I can't sense your country's nerve,
and that is why I beg you, all of you, russians and their TROLLS and BOATS
especially: "leave us alone, we will fix up all our ukrainian mistakes in our
home by ourselves".

\iusr{Марина Колесникова}

At least here are proofs of CIA work with OUN

\href{https://www.archives.gov/files/iwg/declassified-records/rg-263-cia-records/second-release-lexicon.pdf}{%
Research Aid: Cryptonyms and Terms in Declassified CIA Files %
Nazi War Crimes and Japanese Imperial Government Records Disclosure Acts, %
www.archives.org%
}

\iusr{Ivan Pavlov}

sergei you are a gullible, naive person, and possibly stupid, like you said
earlier, i don't care about your opinion on it so ya, my .o2 cents

\iusr{Andrea Bodrati}

@Scott Kuli : I agree that Crimea is the only territory in Ukraine that is
mostly inhabitated by Russian ethnics but the fact the Crimean people don't
want to live under the Kyiv Government (funny once again a Government which has
a Jews Prime Minister and most of his member Jews is often labeled as Nazi) is
just an opnion (on my point of view it is true indeed) since no real referendum
was ever made (the one who took place was a joke, I have friends that voted few
times even not being Ukrainian). Problem is that there is the international law
and one Nation simply can't invade another one due to the fact in a part of his
territory lives their ethnics. Following this rule Austria could invade a part
of Italy, Italy a part of France and Slovenia, Serbia a part of Kosovo, Albania
a part of Greece, Poland the Western Ukraine, Turkey a part of Iraq and so with
a very long list. Regarding the other territories occupied by Russia I suggest
you to take a walk in Donetsk, Lygansk or, even better, Novoazovsk. It is full
of Russian military equipment and you will also find a lot a people from
Russia, Cecenia, Ossetia. You can also ask the Ukrainian living there if you
know any or can just check the OSCE and UN reports about the number of Russian
militants and equipments everyday illegally crossing the border. Since the
military personel don't loose the status even during license and that you can't
find a T90 or a BM27 at the shop near your home we can say that the Russian
army is well inside Ukraine. Even the former "Minister of Defence" of the DNR
was a colonel of the Russian Army.

\iusr{William P Sheehe}

@Scott, get a fucking clue: so-called Russian cease-fire 12-11-14 (going south
to Mariupol - Sea of Azov; not east)

\href{https://www.youtube.com/watch?v=0PAbaLyNlKk}{%
Порошенко за уголь сдаёт сепарам Мариуполь ??? ч.2, Слава Украине, youtube, 11.12.2014%
}

\iusr{Sergiy Stakhovsky}

Carlo))) you make me LAUGH !!! So KievanRus had a capital where?))) and who build Moscow you GENIUS ??)))

\iusr{Andrii Filipov}
The right map of Ukraine

\ifcmt
  ig https://scontent-frt3-2.xx.fbcdn.net/v/t1.18169-9/10888784_774185599323338_4416386366477142732_n.jpg?_nc_cat=101&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=PArSNocuihQAX8uD_32&_nc_ht=scontent-frt3-2.xx&oh=3896cea784479d7c8166464d3529df7c&oe=61CCA0E8
  @width 0.4
\fi

\iusr{Andrii Filipov}
fascits in terroRuSSia http://youtu.be/noOPSljw5CM

\iusr{Максим Шавкун}
Hope Ukraine is a past!

\iusr{Andrii Filipov}
russia

\ifcmt
  ig https://scontent-frt3-2.xx.fbcdn.net/v/t1.18169-9/10888738_774187025989862_8769346935650520675_n.jpg?_nc_cat=103&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=Attw-2jrvt4AX8ABPs6&_nc_ht=scontent-frt3-2.xx&oh=05f952dc5a0f5539cf6257ab0e11e40f&oe=61CA348F
  @width 0.4
\fi

\iusr{Andrii Filipov}
russian kosacks getting awards from Gebels

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10360913_774187532656478_7811383328356745159_n.jpg?_nc_cat=111&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=YMUHV1VRhsMAX8rb5IZ&_nc_ht=scontent-frx5-1.xx&oh=5390fa9614a16aafb9094a8e7b6f4d8b&oe=61CBC090
  @width 0.4
\fi

\iusr{William P Sheehe}
hey look, it's Putinka's drunken wolfheads' grandpas

\iusr{Lily Goncharova-Maher}

@ Sergiy Stakhovsky. Yanukovic maybe was corrupt but he wasn't a murderer
unlike your new oligarch Poroshenko (the most corrupt man in Ukraine!) who
killing innocent civilians in Donbass. So... the Odessa massacre also doesn't
worry you? No wonder that people in Crimea voted to go back to Russia otherwise
your Ukranian nationalists would bomb then as well as Donetsk or Slaviansk. Do
you want "democracy"only for Ukrainian Nazis? Hypocrite!

\iusr{Sergiy Stakhovsky}

Lilia, start to write about something you know... i was in Slaviansk and i saw
how was it there. Murderer?? you mean russian special ops taking gov. buildings
and give weapons to drugaddicts and drunk psychopaths... altho they didnt last
for long so putin had to move in regular army.. otherwise we would be living in
peace.

\iusr{Piotr Chmurnik}

Until 1897 most of them in Crimea Crimean Tatars (36\%) vs. 33\% of Russians.
Only murder of Tatars and their deportation from Crimea and Russians settle in
the time of Stalin's proportions have changed. Membership Crimea to Ukraine
confirmed signed on December 8, 1991 at the city of Minsk. Signed by Yeltsin.
Crimea referendum was illegal. Confirmed the Venetian commission.

\iusr{Daniel Rajala}

Why is the bullshit about ancient CIA practises relevant in present crisis? Yes
US was involved in escalation of Ukraine's crisis but above all the main
culprit and manipulator has been Russia, it has been evident that on all major
levels Ukraine has been undermined by Russian agents, puppeteers, and kept
deliberately as a Russian buffer region against west and above all abused and
taken advantage of.

The EU and even USA care more about the human rights and freedom of speech and
civil liberties that Russia's regime of authoritarian kleptocrats that jail
their political opposition, occasionally murder and often beat them senseless.
This cold war 2.0 was started by Russia instigating the civil war in Donbass
and illegal annexation of Crimean peninsula. No way west will accept this kind
of occupation of a region of an independent country. I can only hope and am
certain the sanctions will be escalated and tightened and they will last for
years to come. What is certain is Russia suffers more from economic ties
getting broken than EU or USA, and more likely end up a subordinate to China as
a result of this. Good luck with that.

\iusr{William P Sheehe}

Odessa Massacre was a Russian covert operation to incite civil unrest, which
failed, presumably because the hired operatives were simply out-numbered by the
pro-Ukraine football crowd. Try again, Lilia.

\iusr{Mirko Malki}

"... and, you know, Fuck the EU."

Victoria Jane Nuland - assistant secretary of state for European and Eurasian
Affairs at the United States Department of State.

Oh yes, have blind faith in the murrika!!!

\iusr{Tomasz Kiszewski}

Nazi pigs fuck off. Viva Russis. Bandera savages must by eliminated to the last
one

\iusr{Sergiy Stakhovsky}

@igg{fbicon.face.tears.of.joy}{repeat=3} extremely intelligent argument
@igg{fbicon.face.tears.of.joy}{repeat=3} 

\iusr{Rob Decoup}
Oliver Stone has problems with logic and education.
Russian Nazis must be defeated!

\iusr{Акно Рамьо}
Your name says it all; you know it all!!

\iusr{Lily Goncharova-Maher}

William P. Sheehe- Odessa Massacre had nothing to do with Russians, please do
not lie! It was sponsored and orchestrated by oligarch Kolomoiskij. I hope he
is not the main sponsor of Sergey Stakhovky! Blood of innocent victims on his
hands if he accepts the dirty money from Soros, Kolomoiskij or Poroshenko- the
most corrupt and evil people in our planet.

\iusr{Lily Goncharova-Maher}

@ Sergiy Stakhovsky . Please don't patronize me, I have friends and relatives
in Crimea and Donetsk and I know very well what is going on in Ukraine. Your
cheap anti-Russian propaganda won't wash with me! Kolomoiskij organised the
Odessa massacre!

Poroshenko is the most corrupt man in Ukraine and a war criminal and murderer!
Much worse than Yanukovich ever was! There are almost one million refugees who
fled to Russia from your fascist regime in Kiev. George Soros sponsored the
violent coup in Maidan and stupid bloodthirsty people like you are continuing
to LIE and support the killing of innocent women and children in Eastern
Ukraine. That is the truth which you DO NOT WANT TO HEAR - because as a typical
russophobe you only care about "democracy" for Ukrainian nazis.

LINK - globalresearch.ca

\iusr{Sergiy Stakhovsky}

Haha)) bravo!!! What a speech.. tell you for secret I was there and saw
everything with my own eyes.. Now if you are that well informed: where did DNR
and LNR got the weapons from?? I am Russophob you can bet on it.. and I became
him recently.. I would say 9 month.

\iusr{Sergiy Stakhovsky}

My words are not propaganda (although russians are very good at it!) my words
are my view, my truth if you don't like its your problem not mine. But you can
shout about it in a separate comment not in mine.

\iusr{Sergiy Stakhovsky}

Refugees ..yeah I would also run if I would watch RU TV.. but you see that's
the difference here.. it's called KNOWLEDGE , INTELLIGENCE.

\iusr{Sergiy Stakhovsky}

And last DOT. Lilia if you are so patriotic or russia supportive why are you
leaving in London?

\iusr{Lily Goncharova-Maher}

And my final reply to you Sergiy- all the drug addicts and drunk psychopaths
were in Maidan Square! Didn't you notice?

\href{https://tass.com/world/731910}{%
Drug addicts among Ukraine's Maidan protesters — official, tass.com, 16.05.2014%
}

\iusr{Sergiy Stakhovsky}

No I didn't, while I was there I actually saw a lot of people with University
diplomas.. @igg{fbicon.thumb.up.yellow} good bye

\iusr{Sherri Ingrey}

you are a Banderist troll.

\iusr{Lily Goncharova-Maher}

Sergiy, Why I shouldn't live in London? Why are the Nazis always telling people
where they should live and what they should think??? Who do you think you are?
We are all living in ONE SMALL PLANET CALLED- the EARTH!!! If God wants me to
live in London I will live in London! HUMANITY is more IMPORTANT than
NATIONALITY! I AM A PATRIOT of our UNIVERSE! If you, Sergiy, have a
narrow-minded attitude and a brain- smaller than a tennis ball, it's not my
problem. Everyone will face God after the death and the first question from Him
will be: HAVE YOU BEEN A HUMAN BEEN while you were living in the body? And not
what nationality you were? I am not going to waist my time to argue with the
Ukrainian nationalist... boring... boring.. Прощайте, Бог Вам судья!

\iusr{Sergiy Stakhovsky}

Very correct.. and believe me I am living according to it.. unlike you(judging my
knowledge) . The truth will prevail , decency will prevail.. something you know
very little about.. love will prevail(again very little for you). Ukraine is the
country were I was born, and I shall pass it to my children better then it
was, in one piece and better... narrow minded people like you think that there is
higher power that will stop all the bad things.. it doesn't exist.. it is in us
to take a stance and defend the right cause.

\iusr{Linda Green}

Sergiy Starhovsky, you are not a very bright man. Ukraine will be dead sooner
or later because extreme nationalism always leads to the death of the country.

\iusr{Sergiy Stakhovsky}

Linda depends who is judging  @igg{fbicon.smile}  and I think you are not very fitting that
role.. extreme nationalism??? Maybe but if 12 month ago our patriotic feelings
didn't exist, now they actually appear. We should be tolerable ..but I saw way
to many catastrophes because of our believe in somebody else..

\iusr{Georgiy Levchuk}

Lilia Goncharova - ahaha, you posted ITAR-TASS link, government-sponsored
propaganda! This is your "independent source"! What a joke! And Linda Green -
what do you know about "extreme nationalism"? Can you define it? You can't even
define what "bright man" is, it seems

\iusr{Georgiy Levchuk}

Linda Green - by the way, Lviv, the most tolerable city, based on your
assessment is the center of this "nationalism", - would tolerate people like
you. Just go there, talk to people, Russian or English, - unless you believe
ITAR-TASS that they would crucify you first, then drug you, then use you for
target practice, then cut your head off, then force you to sing Ukrainian
national anthem, then eat your kids and force you to eat them too, and then to
top it off - speak to you in Ukrainian, and after speak to you in Russian -
probably to make you lose your mind. Oh, wait, you don't have one... oops

\iusr{Jay Whitten}

OK, you know what? Believe what you want, guys - Russia is bad, Putin is bad,
Russia is invading Ukraine... whatever! If your country is worth fighting for,
and Russia is invading you, then fight, but leave America and Europe out of it.
We don't care. Russia has been nothing but an ally to the US in the past couple
of decades, we have no problems with them whatsoever, and I hate to tell you
this - Ukraine is not worth risking a world war over. OK? I don't care if you
don't like it. Deal with it! Fight if you want, but don't look at us - it is
absolutely NONE OF OUR BUSINESS! Fight and die as Bandera's Heavenly Heroes,
but don't ask American soldiers to join you! Now BUZZ OFF!

\iusr{Sergiy Stakhovsky}

I hope russians read your post.. cause they are sure that US soldiers are
fighting in Ukraine))) we don't (I don't ask for help)..we ask for
understanding ..

\iusr{Natali Walker}

Sergiy Stakhovsky... It looks like you are the one who has problems with logic
and know nothing about CIA and its history. If you believe that the US started
collecting information and conducting covert operations only after CIA's
official establishment, you should do more readings on this matter. Even CIA's
official website says that the "United States has carried out intelligence
activities since the days of George Washington, but only since World War II
have they been coordinated on a government-wide basis."

\href{https://www.cia.gov/about-cia/history-of-the-cia}{%
cia.gov - link%
}

The same applies to FSB and other intelligence agencies. There is always a
prehistory.

\iusr{Sergiy Stakhovsky}

Natalie, if you would read enough you would understand that it's almost impossible to run a web of spies during War..

\iusr{Edmund Dantes}

Sergiy, you are an ignorant troll. The CIA was created by a name change of the
OSS (office of Strategic Services) which existed in the army during WWII. It
gave us such raving maniacs as Ed Lansdale, the first army intelligence officer
to discover the existance of Yamashita's gold and considered by Col Fletcher
Prouty to be one of the architects of the JFK murder. You should educate
yourself to prevent making more false representation of facts.

\iusr{William P Sheehe}

Jay, your deluded rantings are laughable, and tardy. The US has already
committed \$300 M over 3 years, to assist Ukraine's self-defense vs. the
Bolshevik horde. You are on the wrong side. Deal with it.

\iusr{Eric Kraus}

The CIA was a successor agency for American espionage. It marked a shift in
target - nothing else

\iusr{Eric Kraus}

as for defending Ukraine from the Bolshevik hordes, that is nothing compared to
the task of defending it from home grown fascists and oligarchs! it is broken.

\iusr{Emil Wojtechko}

Ще не вмерла України! This is written the Ukrainian language. Ukraine has a
separate language and culture than Russia. Mr. Stone is spreading propaganda as
he listens to the nonsense that the Russians told him. Russia also wants to get
back: Latvia; Estonia; Lithuania; Alaska; Poland; Romania...... Russia has no
rights to any of these countries.

\iusr{Ilhan Shirinov}

ukraine is a shame of the world and should end existence withing its current
borders. and this is happening to fortune!

\iusr{Marusia Stashynsky}

Shirinov you are a sick pathetic idiot! You know nothing so shut up!
Do your research!!!!!

\iusr{Michael J. Cala}

It is apparent that we all agree that it's about time for a great new Turkish
Prison movie.

\iusr{Piotr Chmurnik}
@ Eduard Korbmacher

"And can you somehow prove that there are actually russian troops in ukraine?"

Are you really so naive with that believed in the fairy tale putler, with
tanks, armored vehicles and rockets can be bought in any store plain? Are these
ordinary separatists from Donetsk, who previously mined coal? haha

\ifcmt
  ig https://scontent-frt3-1.xx.fbcdn.net/v/t1.18169-9/1508560_1606704816216324_5185727589928875556_n.jpg?_nc_cat=106&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=iuQxr5xHXUkAX8r1gzD&_nc_ht=scontent-frt3-1.xx&oh=a337a723444c6e2d9df449d94c013efc&oe=61CA1E76
  @width 0.4
\fi

\iusr{Steve Brown}
Well Piotr- whoever they are they are kicking the Ukrainian fascists to hell so GOOD.

\iusr{Pavel Oplt}
correct

\iusr{Ron Monks}

\href{https://www.interpretermag.com/red-cross-official-says-moscow-used-humanitarian-convoys-to-ship-arms-to-militants-in-ukraine/}{%
Moscow Red Cross Official Says Russia Used ‘Humanitarian’ Convoys to Ship Arms to Militants in Ukraine, %
Paul Goble, www.interpretermag.com, 28.12.2014%
}

\iusr{Ron Monks}

Russia calls the freely elected government of Ukraine a "junta". Fact is, a
junta is a government run by a group of military officers. There are no
military officers in the Ukrainian leadership. Now, turn to Moscow. The FSB née
KGB is in fact a military branch. Mr Putin and his closest advisors are FSB.
Therefore, it it Russia - not Ukraine - that is run by a junta.

\iusr{Jay Whitten}

"US soldiers are fighting in Ukraine" - no kidding, really? And we shouldn't be
there. I repeat, it's none of our business. And we shouldn't be wasting our tax
money on you little Bandera fanboys either, so stop begging us to bail you out
and deal with your mess you've made.

\iusr{Vincent van den Breemen}

This is a special message for Sergiy Stakhovsky..... Maybe you should watch
this and than leave some comments.

\href{https://www.youtube.com/watch?v=yu8KTiLsLJw}{%
Welcome to Nulandistan: Propaganda and the Crisis in Ukraine, GlobalResearchTV, youtube, 24.05.2014
}

We are talking about
2014 and not about what happened in the past.

\iusr{Екатерина Стрельченко}

Pathetic you are lost in broad daylight, svidomity. Oliver takes the truth that
burns your eyes. Not Yanukovych, Putin and kill civilians in eastern Ukraine,
have not they made a mess in the country. Do not they arrest journalists, and
not at their gold out of the country of Ukraine. Putin simply defended Russian
people banderlogi ready to kill is not clear why. This Yatsenyuk - the
aggressor and the killer is not necessary to shift the blame on others. I never
liked Yanukovych, I think Putin, too, but he could not give it at the mercy of
the brutal Banderovites ready to sell for pennies and bring all the holy things
in this life.

\iusr{Misha Rudov}
\textbf{Sergiy Stakhovsky} you have no clue what you are writing. Please, just play a tennis and stay out of politics!!!

\iusr{Misha Rudov}
\textbf{Mark Sleboda}

Don't let the Western MSM rewrite history to whitewash the genocidal Stephen
Bandera, OUN, and the UPA - and those who worship at their obscene cult in
Ukraine to excuse the nature of the Maidan Putsch and regime.

"Abstract

During the past decade, particularly under the presidency of the third
Ukrainian president Viktor Yushchenko (2005–2010) there have been repeated
attempts to turn the leading ﬁgures of the Organization of Ukrainian
Nationalists (OUN)and its armed wing, the Ukrainian Insurgent Army (UPA) into
national heroes. As these fascist organizations collaborated with the Nazi
Germany, carried out ethnic cleansing and mass murder on a massive scale, they
are problematic symbols for an aspiring democracy with the stated ambition to
join the European Union. Under Yushchenko, several institutes of memory
management and myth making were organized, a key function of which was to deny
or downplay OUN-UPA atrocities. Unlike many other former Soviet republics, the
Ukrainian government did not need to develop new national myths from scratch,
but imported ready concepts developed in the Ukrainian diaspora. Yushchenko’s
legitimizing historians presented the OUN and UPA as pluralistic and inclusive
organizations, which not only rescued Jews during the Holocaust, but invited
them into their ranks to ﬁght shoulder to shoulder against Hitler and Stalin.
This mythical narrative relied partly on the OUN’s own post-war forgeries,
aimed at cover up the organization’s problematic past. As employees of the
Ukrainian security services, working out of the ofﬁces of the old KGB, the
legitimizing historians ironically dismissed scholarly criticism as Soviet
myths. The present study deals with the myth-making around the OUN, the UPA,
and the Holocaust, tracing their diaspora roots and following their migration
back and forth across the Atlantic."

\href{https://www.academia.edu/1122859/The_OUN_the_UPA_and_the_Holocaust_A_Study_in_the_Manufacturing_of_Historical_Myths_The_Carl_Beck_Papers_in_Russian_and_East_European_Studies_2107_Pittsburgh_University_Center_for_Russian_and_East_European_Studies_2011_}{%
The OUN, the UPA and the Holocaust: A Study in the Manufacturing of Historical Myths, The Carl Beck Papers in Russian and East European Studies 2107 (Pittsburgh: University Center for Russian and East European Studies, 2011), Per Anders Rudling%
}

\iusr{William P Sheehe}

If you know Mark Sleboda, you are a freak. Yushchenko is long gone, this is
outdated and irrelevant. All of this shit has been replaced by Ukraine's ATO
and new National Guard. Perhaps you think that the NKVD were uninvolved in
Himmler's planning and implementation of the Death-camp plan? Grow-up, dipshit.

\href{https://therussianreader.com/2014/02/04/matveev-putin-leftism}{%
Ilya Matveev: A Word to the Wise (On Putin’s \enquote{Leftism} and Solidarity with Russians), %
The Russian Reader, 04.02.2014%
}

\iusr{Ceased To Excist}

This has Gerasimovs and Putins fingerprints all over it since the Syrian
civilwar started and the kleptocrazy of Russia stood to lose their last
navalbase in the mediterrainian sea.

For Russia, the navalbases will make or brake them, hence the seizing of
Ukraine territory (krimea with sevastopol and now trying to connect it with the
mainland).

\iusr{William P Sheehe}

ah yes, the naval base. how many innocent people have already been killed for
that fucking thing?

\iusr{Oleg Moisidis}

By the same token, KGB could not possibly eliminate nazi criminal, the hero of
Ukraine Shukhevych in 1950, since the organization was established only in
1954. So when you call someone else pathetic, try to look in the mirror-you
might find one in there.

\iusr{Misha Rudov}
William P. Sheehe you are a moron!!! So stupid!!!

\iusr{Misha Rudov}

\href{https://russia-insider.com/en/tv_politics_ukraine/2014/11/07/01-12-12pm/nations_stephen_cohen_american_tv_last_night_explaining}{%
The Nation's Stephen Cohen on American TV Last Night Explaining the Donbas Elections, russia-insider.com, 03.11.2014%
}

\iusr{William P Sheehe}

this is 2-months-old, commissar. now, they are recycling shit for dumbfucks
like you to swallow, again.

\iusr{Misha Rudov}

\href{http://www.ronpaulinstitute.org/archives/peace-and-prosperity/2015/january/04/how-many-current-us-wars-lets-ask-obama}{%
How Many Current US Wars? Let's Ask Obama..., 04.01.2015, www.ronpaulinstitute.org%
}

\href{https://obamawhitehouse.archives.gov/the-press-office/2014/12/11/letter-president-six-month-consolidated-war-powers-resolution-report}{%
Letter from the President - Six Month Consolidated War Powers Resolution Report, obamawhitehouse.archives.gov, 11.12.2014%
}

\iusr{Misha Rudov}

\href{https://www.youtube.com/watch?v=_kmYRfNfRkM}{%
'Democracy Projects' Are Not Democratic: The Case of Ukraine \& Russia, LaRouchePAC Live, youtube, 20.02.2014%
}

The recent gaffe of Victoria Nuland being caught using her post in the U.S.
State Department to push a self-proclaimed neo-Nazi into the presidency of
Ukraine reveals a far more contemptible role being played by leading
transatlantic forces, desperate to bring Eurasia under its control for its own
political/economic survival.

\iusr{Daniel Rajala}
Jesus what morons, this wall is epic...

\iusr{Galina Andreyev}
Mr stone is right.

\iusr{Yuriy Gruzglin}

Hey, well-wishers, Ukraine will decide without your input whether it is a
bridge or a link or has some other role between "the Russian world" and Europe.

Funny enough that many of you who despise democracy and hate US nevertheless
move there at your earliest convenience, live there and enjoy the freedoms and
opportunities this country offers you.

\iusr{Isobel Jardine}

Ukraine historically wasn't separate from Russia which is why there are so many
ethnic Russian Ukrainians in the south and east who don't like the changes in
Kiev.

It is really disgusting the way Nuland, McCain and Kerry buddied up with well
known neo Nazis then Kerry lied saying there were no neo Nazis there. Plus
encouraging violent riots - the behaviour of the US is criminal

\iusr{Harry Noemas}

But of course it vould take at lest 6 year to get crime organized, 1953, can
you say, Mossadegh?

\iusr{Nikitina Georgopoulos}

Lots of Nazi trolls here that Oliver should block! Must watch this episode

\href{https://www.youtube.com/watch?v=vd6ngRVovaI}{%
The Unknown War Ep13 Liberation of the Ukraine, greatworldwar, youtube, 09.02.2013%
}

\iusr{Владислав Попков}

Молодец, смешно пишете. Если бы ФСБ хоть немного нормально работало бы, то
сейчас в украине была бы Советская власть, тишина и порядок.

А то, что сейчас творится, как раз и говорит о том, что ни хера оно не работало
а хлопало ушами и все прохлопало.

+++++++++++

The good fellow, ridiculously you write. If FSB though a little normally would
work, now in Ukraine there would be the Soviet power, silence and an order.

And that now is created, just and says that line it didn't work and looked
blank and everything missed.

\iusr{Alexander Chan}

Your first post is completely incorrect. WW2 ended in 1945, and yes CIA from
the very beginning operated outside of the United states. Yanukovych did not
destroy any defence ministry whatsoever, there was no external threat to
Ukraine until November 2013. The fact you cannot even bother to answer any of
the things that Oliver Stone has said and instead resort to ad hominem attacks
against him really does show that you don't have a clue about what happened in
Ukraine and you support the Nazi and openly fascistic elements which toppled
the democratically elected President of Ukraine.

\iusr{Marie Clns}

Er! Wasnt it the COI, then the OSS prior to becoming the CIA. In any event,
there was an Intelligence Agency prior to - a - CIA

\iusr{Leo Foster}

Much like the FSB, the CIA has origins in a predecessor agency, and was hardly
born in 1947.

\iusr{James Rowlands}
\textbf{Sergiy Stakhovsky} 

... you made a valid point about the need for a network for an intelligence
service to operate. And you're also right that the OSS was not hugely
effective. And to question whether the CIA could do something like this is
absolutely valid based on those concerns, but I'm going to go out on a limb and
assume you don't know what the Gehlen Organisation was? Or the other stay
behinds recruited from 1945 onwards?

In fact, those very SS officers, that the CIA brought into their umbrella were
one and the same that had managed the Nachtangale battalion. And they did
nearly the same thing in every Western European country.


\end{itemize} % }

\iusr{Vira Dziedzic}

What a slap on the face to the people of Ukraine. You quote the most corrupt
president, as you have said yourself, and based on that only you undermine the
courage, the pain, the struggle Ukrainians indured to overthrow that monster.

One side presented only.

Shame on you.

The whole world is not only about USA. There are other nations that want to
define their own destiny.

\begin{itemize} % {
\iusr{Steve Poe}

The other side is all we have been getting from US media for a year now. Oliver
is just pointing out the side that the other half of Ukrainians see.There
wouldn't be a civil war in Ukraine if all Ukrainians agreed with the coup.


\iusr{Vira Dziedzic}

There is no civil war. The wAr is in Donetsk and Luhansk, 7\% of population of
Ukraine, the rest 93\%!!! Supports the new government. Please get your facts
checked and don't be influenced by populism.

\iusr{Igor Nakonechnyy}

Vira, you are being very civilized with idiots. It's a waste of time. Fuck
them. Let them untangle CIA plot in their underware.

\iusr{Steve Poe}

Why is political repression of people of Kharkov, Odessa, Mariupol, Zaporozhie
so strong then? Why are opposition protests banned in Ukraine? There are
millions of people who oppose this government.

\iusr{Steve Poe}

Just because West Ukrainians have taken 97\% of Ukraine by military force it
does not mean that 97\% of Ukraine support them. But then fascists don't care
what the people think. You just kill the dissenters.

\iusr{Vira Dziedzic}

What military???? The military force was completely dismembered by previous
president. The whole country is standing up to Russian aggression supplying the
volunteers that picked up a gun to protect their own country!!!! People, not
the government supply the brave ones on the front line. Where do you get your
facts?????? Russian propaganda TV?

Well, good luck. Ukraine has had elections. People of Ukraine voted in a new
government. Respect its outcome, even Putin, the "angel of goodness"
acknowledged its legitimacy. And, idk, get off the cool-aid. Or enjoy your
paycheck.


\iusr{Vira Dziedzic}
Ahhh... yet another agent!

\iusr{Vira Dziedzic}

Mass media are not controlled. I get all my information from people on the
ground. Many fight and disagree with each other, yet... You guys all speak in
such unison, how peculiar ...

Get your paycheck I responded  @igg{fbicon.wink} 

\iusr{Vira Dziedzic}
Your google translate didn't do a very good job.

\iusr{Igor Nakonechnyy}
Wrestler Joe, translate this: пішов нахуй!

\iusr{Vira Dziedzic}
Forgive my friend, he has made a mistake, it should say - пішов на хуй.

\iusr{Vira Dziedzic}

Your post is full of contradictions.

You are an agent as well.

Your knowledge of Ukrainian situation is one sided. The problem of Ukraine is
complex. You go in depth to present the side of Russian propaganda TV and yet
you slide over the other side with incredible over-simplicity.

Leave Ukraine alone. Let us decide on our own what to do. We didn't attack or
annex Russian territory, why blame us for Russian atrocities and bland
international crime. Ahh, its an old trick! Attack is the best form of defense!
KGB psychology 101.

\iusr{Vira Dziedzic}

do you even know how easy it is to detect you guys? lol you gotta be one, you
all speak in unison, you don't make logical sense or disagree with each other.
you are like minions. Ukrainians on the other hand are coming with different
approaches to the same situation, they disagree, they fight, they show a
spectrum of ideas. No, not you, you attack, you paint everything with the same
brush strokes, you don't say anything unique, outside of propaganda slogans...
capisce? its quite easy. OR you are brainwashed, unoriginal, nonthinking
individuals spoonfead by russian propaganda. in any case, very pitiful.

\iusr{Vira Dziedzic}

Atack, atack, atack. People matter. They alway do. That what the revolution if
dignity was, about the people. Why do you bluntly accuse me of all of these
things without knowing what I stand for. That, my dear is a kgb tactic-atack
first. There are 45 mil people in Ukraine, I mil in emigration. Why paint
everyone with the same brush. We fight and disagree with each other all the
time. If you know Ukrainians you know that every one is an atoman, we are not
like Russians, we are all very opinionated. We have disagreements. That is why
it is so easy to see a troll. You just don't know us. That's all.

\iusr{Vira Dziedzic}
Ps. We call Majdan - the revolution of dignity.

\iusr{Vira Dziedzic}

oy... where to start... people you have mentioned from the right wing, are in
the opposition to the government. the right sector won less than 2 \% of the
vote. did you see the whole country march with torches or just few hundred
people? Do you know the \% of right wing ideologists in other countries? we are
a democracy, we have a place for different ideas. Its usually the North Korea
or Russia or Venesualla that has a 98\% -100\% approval for the government. the
rest... leave it to Ukrainians to figure it out, ok? If you want the change
(and Ukrainian citizenship) go and vote and don't play around with conspiracy
theories like a school girl. If you don't, leave us alone! and let Ukrainians
figure it out, without the help from Russian green men.


\iusr{Vira Dziedzic}

having ukrainian blood has nothing to do with understanding Ukrainians. There
were many russian, jewish, muslim Ukrainians that fought for their rights to
live in democracy free from corruption. there are many "pure blooded
ukrainians" than would sell their country for bigger pension.

\iusr{Vira Dziedzic}

why do you think I or anyone else forget??? we don't! thants why we had Majdan,
so that the people in government would never forget who, by Constitution ch5,
is in charge of the country. we have to work with what we have. when we get
better qualified, we hire them (economists from abroad !!!). But at the end new
government knows, if they mess up, they will end up like Yanik. That my friend
is democracy! and that is what Majdan was all about. the rest is a hard way...
there will be many mistakes and fails, democracy is hard. I just wish Russia
would back off and let us be and let us build our own country, mistakes and
successes, but on our own terms.

\iusr{Vira Dziedzic}

You contradict yourself again. We don't live in the shadow of Russia, we are
invaded by Russia and our territory is annexed by Russia. We have been in the
neutral zone all the time trying to work with both sides. That is why when
Yanukovich ran away and Russia annexed Crimea, we felt as if out old friend put
the knife in our back. People couldn't believe they could do it to us, if
volunteers wouldn't pick up guns to protect the east, there would be no Ukraine
by now. We feel betrayed by Russia. They signed the treaty to protect our
borders in 1996 in exchange for us giving them all of our nuclear weapons. They
broke their own treaty. We don't stand a chance to fight them back
alone.meanwhile Russian politicians keep talking about wiping us out as a
nation sending Russian troops and tanks to the east. What would you suggest we
should do? Capitulate? Give up, after all these years of independence, many
deaths during the revolution? What would you do? Idk. It's futile to explain.
Ukrainians are free in their hearts. Ukraine is Not Russia. We will fight to
the end. For our freedom.

\iusr{Vira Dziedzic}

We are the oldest European nation, we had democracy long ago in запоріжська
Січ, we can handle it, trust me.

\iusr{Vira Dziedzic}

i can't even respond to that. so russians can poop on my blanket, and i should
play by their rules, because they are more than just brothers??? wtf?? I don't
feel any connection to russia. they kill my people, destroy my land... i don't
give shit about how they feel. I care for little kids left without a father and
soldiers coming home mutilated. i think you are so brainwashed about events
that never took place, you are misinformed in so many ways.... I pray one day
the Haag tribunal will declare the truth and send Putin and the likes to serve
for all the atrocities committed and all the propaganda spread. I am done
talking. I know who you are.

\iusr{Vira Dziedzic}

and you are right I meant to say one of the oldest Europian nations. no
ethnocentricity here. All the ethnocentricity is left to the "brother" that
poops on the blanket.

\iusr{Igor Nakonechnyy}

Vira, don't bother with morons. They are so utterly fake. Just like their fake
names suggest. To hell with them.

\iusr{Vira Dziedzic}

for a moment he made me think he was real. good training.

\iusr{Igor Nakonechnyy}

Vira, this says it all:

\url{http://prntscr.com/5oyau9}

\iusr{Vira Dziedzic}

i checked him all out beforehand, I know. It was just a moment of a doubt,
hoping to reach out on a human level. what can i say, i am a girl. they are all
there... not just Kadyrov... and Ani Lorak! haha

\iusr{Vira Dziedzic}

\ifcmt
  ig https://podrobnosti.ua/upload/news/2015/01/06/1010115_3.jpg?fbclid=IwAR1-tVGNx9k35mtsRD7VM05kShxsD1Kf7bUpG54-SfrfRv0PzDuWvfSy6xw
  @width 0.4
\fi

\end{itemize} % }

\iusr{Viktoriya Gryb}

Mr. Stone, such level of ignorance is not expected from YOU. Emotions aside,
you need to get your facts straight before you maneuver the public opinion into
a certain direction.

\begin{itemize} % {
\iusr{Viktoriya Gryb}

Tate, I have family and friends in the area. You don't need to tell me what's
up with MY country, I already know. You, on the other hand, are extremely
confused. And Stone only adds fuel to the fire.


\iusr{Ilhan Shirinov}
shut your sick ukrainian minds. ukraine is a shame, bandit fail state.

\iusr{Viktoriya Gryb}

Yes, Mr Shirinov, that was exactly what Oliver Stone wanted to convey. You
should be his assistant producer. Too bad such brilliant mind as yours is being
wasted on trolling.

\end{itemize} % }

\iusr{Julia Davis}

Dissecting the deception: anatomy of Russia’s propaganda in the West
\url{http://t.co/hRxIGCY01F}

\begin{itemize} % {
\iusr{Eric Kraus}

The funny thing is that the Western media is totally propogandistic, and very
professionally so. And yet, they are outraged, outraged that anyone else could
be partisan!

\end{itemize} % }

\iusr{Tom Dal Magro}

So Mr Stone, you are rightly saying that Yanukovych was "most corrupt president
Ukraine’s ever had", but can't understand that the ppl of Ukraine wanted him
out?

The ppl of Ukraine were smart enough to ouster Yanukovych on their own. If you
had the impression that it was all done by "Victoria Nuland, John McCain etc."
because these are the folks you have seen on CNN, than you are just saying that
you have no idea what has actually going on there.

And what has 1949 to do with the current situation? - Nothing at all, no bigger
picture but connections that don't exist.

\begin{itemize} % {
\iusr{Tom Dal Magro}
Tate Ulsaker lol conspiracy dumbfuck, just tell me why terrorists from Russia took the ppl of Lugansk as hostages, than we can talk about "the corruption" of Poroshenko (you apparently don't even know his name)
\end{itemize} % }

\iusr{Bohdan Pechenyak}

Oliver, you are completely out of your depth and it is just painfully obvious.
"The bigger picture" you talk about is some KGB-produced myth you have eaten up
like Putin's lapdog, I"m sorry to say.

Just a few facts. The "Nightingale" battalion existed - but it existed in early
1940s, being disbanded by 1942. And it had absolutely nothing to do with USA or
CIA (which did not even exist back then). You can't even get that little fact
right, not to mention the so-called "bigger picture".

"CIA parachuted Ukrainian infiltrators"? Are you completely devoid of any sense
of history? CIA had nothing to do with what was taking place in Ukraine in
1940s and 1950s - those were the Stalinist years, when NKVD (the precursor of
KGB) ran rampant, murdering and pillaging Ukrainians all around.

Besides, all this is largely irrelevant to what is happening RIGHT NOW. You are
meddling with a hot conflict that is far from being resolved. Your celebrity
carries responsibility - and you are failing the test here. You preach on about
Nuland, McCain, etc., yet for some reason you are not bothered by the much more
flagrant Russian imperialism and meddling in Ukrainian affairs. Such double
standards are simply despicable.

Ukrainians are thankful that the world finally got engaged in the situation and
didn't let the Siberian bear trample all over Ukraine. Even so, their reaction
came late, was equivocal and enabled the annexation of Crimea, the unpunished
shooting down of the MH17 airliner, the manufacturing of the conflict in the
East. And you are worried about the fact that those riot policemen, who were
killed on Maidan, go unavenged? How about all those unarmed, innocent people
killed? Nobody was punished for their deaths either! It's may be a problem of
certain incompetence, etc. - but that has nothing to do with CIA or anything
else like that.

You are so obsessed and paranoid about the American power that you fail to see
what's at stake here and what's really happening. Yanukovych is not just the
most corrupt Ukrainian president in recent history - he is also the most direct
tool of the Kremlin. And you are becoming just such a propaganda tool yourself.
If you take even ONE word from Yanukovych or anyone close to Putin seriously -
you are already a lost cause. You ramble on about CIA? How about the KGB, of
which Putin's regime is a direct offspring?

I suggest you stick to those topics you are a bit better acquainted with,
because you are clearly going off the deep end into the abyss.

\begin{itemize} % {
\iusr{Eric Kraus}

the pro-fascist camp is in denial - but they are losing the war, Crimea is
gone, and Ukraine is partitioned - and yet they are in too deep, and cannot
admit to themselves that they were fooled by the Americansl


\iusr{Bohdan Pechenyak}
Eric and Gaby, you are clearly morons without a clue ))). Go suck on some lollipop, because this isn't playground for children ))

\iusr{Maximus Berezov}
Bohdan pe4en'ka watch your own logic and mouth. Your delusional ukropitek.

\iusr{Bohdan Pechenyak}
)))) Again, suck on a lollipop, oh little one ). Ruscists are not welcome here ))

\iusr{Abraham Hazou}

"peaceful protesters" with guns and molotovs attacking security forces that
were ordered for months to be restrained.. ya, try that in America and west
Europe and see what will happen to you  @igg{fbicon.face.persevering}  silly banderites

\iusr{Bohdan Pechenyak}

Do I care about your opinion, Wrestler? No. So piss off. I ain't your "bro" and
never will be.

\iusr{Bohdan Pechenyak}

Abraham, you are an idiot. Context is everything.
Reminder: lollipop, lollipop )))

\iusr{Bohdan Pechenyak}

BTW, my credibility has got nothing to do with anything. Just learn history, you Russophile fools. The truth shall set you free.
Or you can stay paranoid and ignorant, for all I care. You are and will remain irrelevant anyway.

\iusr{Martin Schröder}

Why does voice of eastern ukraine never get into US news media? Something must
be very wrong.. 

\href{https://www.youtube.com/watch?v=7GzOaIXnkPs}{%
youtube link
}

\iusr{Bohdan Pechenyak}

))))) "Voice of Eastern Ukraine?" You must mean the Kremlin-sponsored
terrorists who pretend to be those artificial "people's republics". Yes, those
Russian "humanitarian convoys" help supply the ammo and weaponry needed to keep
the people sufficiently terrorized.

So many fools around... Even in this age of information, ignorance rules,
maintained by deliberate misinformation.

Stop watching Russia Today and other Kremlin propaganda.

\iusr{Bohdan Pechenyak}

It seems having "Sсhröder" as last name is a hazard for being a Putinist toad
)). Gerhard, Martin, who else? ))


\iusr{Bohdan Pechenyak}

Nothing to do with "blood" - you are simply an idiot. Good riddance!

\iusr{Bohdan Pechenyak}

Support the war?! You are out of your effing mind. Nobody is supporting war -
we want to end it ASAP! But not by capitulating to aggressive imperialists!

The war is Putin''s creation and his thugs are responsible for its
continuation. As well as continued weapons and ammo supplies from Russia
masqueraded as "humanitarian convoys".

Get a clue, you morons, before opening your mouths.

\iusr{Bohdan Pechenyak}

This ridiculous "right-wing" menace is nothing but a myth. Only ignorant fools
believe in such nonsense. Learn the facts, and preferably not from some idiotic
YouTube videos... Or The Nation, this mindless mouthpiece for Stephen Cohen, a
well-known Putinist toad, and his editor-in-chief wife Katrina vanden Heuvel.

Just pathetic...

\iusr{Юліян Гайда}

Where's the hoopla over France's neo-fascist National Front Party getting 15\%
in the last elections, while Svoboda and Pravyj Sektor get less than a combined
3\%?

\iusr{Юліян Гайда}

Or what about Hungary's Jobbik party with 20\% popular support. I'd say that's
far more of a threat.

\iusr{Daniel Rajala}

Good analysis Bohdan, it's plain obvious who doesn't let the people develop and
find their own ground, after all these corpses, annexations and
deaths... Ukrainians must truly hate what Putin and his cronies did for mere
imperialist interests. Slava Ukraina! Hope you end up making a free nation one
day...

\iusr{Ilhan Shirinov}

shut your ukrainian sick mind!

\iusr{Dowbusz Stephanie}

\href{https://www.thedailybeast.com/exclusive-photographs-expose-russian-trained-killers-in-kiev}{%
Exclusive: Photographs Expose Russian-Trained Killers in Kiev, Jamie Dettmer, thedailybeast.com, 30.05.2014%
}

\iusr{Anastasia Paluch}
Bravo Bohdan, what an excellent comment. Thank you for standing up against Oliver Stone's blatant stupidity.

\iusr{Bohdan Pechenyak}
Ilhan Shirinov
Shirinka, bug off ))

\iusr{Bohdan Pechenyak}

)))) Again, ignorance is screaming. "Udar" is a party of Vitaliy Klitschko, the
boxing champion and currently the mayor in Kyiv, not a "nazi battalion" )).
Azov does have some unsavory characters, and everyone is aware. They are
marginal and have no direct say in anything other than actually defending
Ukraine against the Russian aggressors. Right-wing radicals have no political
future in Ukraine - and it's quite obvious. So, stop lapping up Kremlin's
propaganda about "fascists" and "Nazis" in Ukraine. Worry about the National
Front that supports Putin''s shenanigans. And what about France wanting to sell
Mistral military ships to Russia? What do you call that?

Again, please show some critical thinking.

\iusr{Bohdan Pechenyak}

Perhaps you meant "Aidar" - there is a battalion with that name. There is
nothing "nazi" about it. There are many other battalions as well - Donbas,
Dnipro-1, Dnipro-2, etc., etc., etc. These are all volunteers, who are
complementing the efforts of the regular army, which has been rendered bankrupt
and inadequate by the previous criminal regime. Much has improved since, but
many corrupt bureaucrats are still in the middle tiers of various bureaucracies
- it's not easy to get rid of them all at once, as anybody who knows anything
about administration will agree - so the regular military sorely needs help.

But this is all beside the point. Once the Russian thugs get out of Ukraine -
then the legitimately elected Ukrainian government can focus on building a
prosperous, successful state and nation. If the government will be incompetent,
the people will choose another one, as it's normally done in democratic
countries. Period.

Bottom line: Russia, get your filthy imperialist hands out of Ukraine!

\iusr{Ramunas Cesonis}

Thank you, Bohdan, a very good reply to this madness. Apparently, Mr Stone is
going nuts - totally so.

\iusr{Peter Kratochvíl}

We have to stop this fascist agressors which bombing innocent people and lie.
World is not with you!


\end{itemize} % }

\iusr{Igor Des}

Like any typical propaganda piece, your writings contain about 10\% of facts and
the other 90\% is a narrative spun out of them to fit a pre-ordained agenda..

A) Nuland and McCain didn't interfere but merely showed up to show their
support to a popular democratic movement which was already well under way.. The
movement was there and was bound to evolve no matter whether Americans or
Europeans showed solidarity with it or not. One has to be delusional to claim
that hundreds of thousands of Ukrainians who spent 3 months in freezing cold
protesting an increasingly authoritarian government, had no real reasons or
grievances that moved them to protest and that they were out in force merely to
get some "free cookies" from US officials

@igg{fbicon.face.smiling.sunglasses}  the new government IS investigating the
events of February 18-20th.. And a number of culprits have already been named.
However, this will take a long time especially as Yanukovich and his cronies
burned countless government documents before leaving the country. For example,
the bombing of PanAm by Lybia took 3yrs to investigate

C) the truth is that civil war wasn't over on the territory of ukraine in 1920s
but lasted well into 1950s with Ukrainian nationalists, particularly those from
western Ukraine (a part that was invaded and illegally annexed by USSR in 1939)
fought for independence and against political and cultural subjugation by ussr.
Whether there was CIA support or not during Cold War for the groups that have
been fighting soviet government for 30yrs is not relevant.

D) Your grasp of the Cold War events is at best weak and at the worst
deceptive. USSR not only incorporated lands and countries illegally annexed
during WW2 it also politically and militarily dominated most of Easter Europe,
using tanks and paratroopers at will to keep it under its heel, as we saw in
Czech Republic and Hungary where democratic uprising were addressed with soviet
tanks.. If CIA did come to the aid of freedom seeking democratic movements - it
did so after those movement have been well under way and it was clearly on the
right side of history

\begin{itemize} % {
\iusr{Eric Kraus}

The Americans bragged about having spent \$5bn to bring about regime change,
then act terribly offended when anyone accuses them of interference...


\iusr{Igor Des}
\textbf{Eric Kraus} 

Americans certainly didn't say that.. While the \$5bn figure is factual, the narrative around it created by Kremlin media is pure propaganda - gets back to 10/90 ratio..

\$5bn is the total cumulative funds received by NGOs dedicated to promoting
civil society and democratic institutions over 23yrs since ukraine's
independence in 1991..

The promotion of democratic institutions is a standard practice undertaken in
all developing countries, especially those emerging from authoritarian past..
They have been successful in helping most east European countries transition to
liberal democracy..

In fact, the funds invested in similar NGOs in Russia since 1991 total \$20bn..

\iusr{Maximus Berezov}

Ngo were/are in Libya, Syria, Hong Kong, and everywhere else, where the cia
needs to coup the goverment. Ngo's finance the protesters, then media shows a
huge "unhappy" crowd demonstrations, which are portrait as a regular citizens.

WHAT OTHER DEMOCRATIC VALUES YOU ARE TALKING ABOUT? I really whould like to
hear.

\iusr{Igor Des}

So basically, the million Ukrainians who spent 3mo on maidan were all employees
of some CIA-backed NGO and the initial student protests were not beaten up by
Berkut but by undercover CIA agents? Is that what you are trying to say?

\iusr{Igor Des}

America is fighting russia in ukraine? Let's focus on facts and not science
fiction..

If you want to discuss the activities of the multinational energy companies,
they are very active all over the world, including Russia because they have the
experience, the technology and the know-how.. Without partnering up with Exxon,
etc.. Russia wouldn't be able to access more than have of its oil reserves..

So yes, western companies getting involved in Ukraine to help it extract and
export natural resources is great for its economy because otherwise ukraine
doesn't have the technology to extract shale oil and gas by itself, lacking the
technology to do so..

However, this is a huge problem for russia, since if ukraine does become energy
self-reliant russia will lose and export market as well as an economic lever to
keep ukraine under its thumb

\iusr{Steve Poe}

I talk to Maidan supporters and they inevitably say that without visibile US
support they would not have dared to take on the elected government of Ukraine.
These Nazis were emboldened by open US support. Without US support these Nazis
would be a marginalized fringe group much like Nazis in US.

\iusr{Igor Des}
\textbf{Steve Poe} 

what US support are you referring to? Victoria Nuland coming out with a jar of
cookies one day? Don't be ludicrous.. The first mass protest that numbered
hundreds of thousands took place after Berkut severely beat up and kidnapped
scores of students.. According to surveys some 20\% of the population at one
point or another actively participated in Euromaidan protests.. While the moral
support of a few U.S. officials was appreciated, the revolution was well
underway and had to do with democratic desires of Ukrainians citizens and with
reprehensible conduct of corrupt, power-usurping government of Yanukovich..

Let me just close this by reminding that Yanukovich's son within 2yrs of his
dad coming to power turned from a mere dentists into the richest billionaire in
Ukraine.. This is one of the symbols of corruption which brought people out in
the streets, especially when beatings of students started and when civil
liberties started to get curtailed

\end{itemize} % }

\iusr{Olya Stawiski}

I just love how the biggest critics of the west and of democratic values, and
the biggest lovers of Putin and totalitarianism CHOOSE to live in the most
democratic countries in the world. If you despise the west so much, all you
critics, go and live in Russia for a while. You'll all be scampering back to
your comfortable little western lifestyles in no time. As for you Oliver Stone
you are a tragic conspiracy theorist, who chooses not to explore both sides of
the story. If you took the time to discover what the majority of people in
Ukraine know and feel about the situation in Ukraine, instead of the taking the
word of that corrupt little slimebag Yanukovich, you might be a little more
credible in the eyes of the world. Yanukovich and Putin will be rubbing their
hands in glee that that snared someone like you to spread their disgusting
propaganda. Well done, Mr Stone.

\begin{itemize} % {
\iusr{Nancy Hammond}
Same ole idiotic reply

\iusr{Steve Poe}

You can dislike Putin and still disagree with a violent coup and suppression of
the opinions of Southeast Ukrainians. And this is and English language page so
you naturally get more people who live in English-speaking countries. There are
plenty of Russian-language pages that are full of people still living in East
Ukraine.


\iusr{Olya Stawiski}

It was not a violent coupSteve, it was a peaceful protest until Yanukovich gave
the order to start firing at the crowd an beating people. Then it became a
blood bath. They were excersing their democratic right to peaceful protest but
when they were attacked they started to defend themselves rather than
scampering off like scared rabbits, like Yanukovich expected them to.

\iusr{Александр Янчук}

Steve, I'am agree with u. it's very good that some people from West understand
the reality despite of media attempts to turn over the true. We are walking
fast to a global conflict and we have to understand both sides to manner in
correct way. We shouldn't cover things and tell as it is.

\iusr{Marijka Stadnyk}

There was no coup; that is just Russian rhetoric and propaganda. Yanuk, the
corrupt criminal thug was doomed and it was just a matter of time:

\href{https://www.nytimes.com/2015/01/04/world/europe/ukraine-leader-was-defeated-even-before-he-was-ousted.html}{%
Ukraine leader was defeated even before he was ousted, nytimes.com, 04.01.2015%
}

\end{itemize} % }

\iusr{Лъчезар Лазаров}

Mr. Stone, you are one of the reasons for some people still thinking in
America!!! God bless you and happy New year!

\iusr{Lutz Brellenthien}

Mr. Stone. If you want to see and feel the Ukraine you should go to Ukraine;
not to Moscow. If you want to get told about the Ukraine you should go there
and let the people of Ukraine tell you; not Mr. Yanukowytsch or Mr. Putin.

And if you want to see what happens in the eastern parts of Ukraine wich are
under control of terroristic military agents from Russia you should go there..
but not just talking to Mr. Sacharchenko. Better talking to normal ukrainian
citizens there.

I could give some adresses there. Adresses from friends, realtives, former
collegues of my wife and her mother. My wife was growing up in Donezk, and we
can here day by day what happens there. We just need to pick up the phone.

I really had alot of respect for you and your work. But this respect is just
melting away rapidely.

\begin{itemize} % {
\iusr{Robert De Cherry}
I don't think a coward would have the balls to do a movie on JFK's assasination.

\iusr{Lisa Plakinger}

Mr. Stone will lediglich seine Bücher erfolgreich in Russland verkaufen. Mit
dieser Aktion wird es im gelingen. Über den Konflikt zwischen den russen und
ukrainern hat er keine Ahnung. Man muß russe oder ukrainer sein, am besten
beides, um das zu verstehen. Ein Ami hat genau soviel Ahnung von der Ukraine
und Russland, wie meine Mutter über Amerika. Ich würde sagen: Mr. Stone "не в
то корыто вы залезли".

\iusr{Martin Schröder}

Oliver should visit Donetsk, Marinovka, gorlovka..

\iusr{Lutz Brellenthien}

Yeah. In eastern Ukraine he will meet the terrorussian Nazis who grow up a
terror regime over the people. a regime of turture, killing people who are
against them.. a total breakdown of every upblic order, human right and peoples
rights..  just read the reports of the High Commission for Human Right of The
United Nations.

\href{https://jamestown.org/program/the-involvement-of-russian-ultra-nationalists-in-the-donbas-conflict/}{%
The Involvement of Russian Ultra-Nationalists in the Donbas Conflict, %
Richard Arnold, jamestown.org, 11.06.2014%
}

\iusr{Lutz Brellenthien}

\href{http://time.com/3545855/russia-ukraine-war-history/}{%
Russians Rewrite History to Slur Ukraine Over War, time.com, 29.10.2014%
}

\iusr{Lutz Brellenthien}

\href{https://gay.americablog.com/2014/03/meet-vladimir-putin-favorite-neo-nazis-russia-crimea.html}{%
Putin is against Nazis in Ukraine, but he loves them in Russia, %
gay.amerikablog.com, 04.03.2014%
}

\iusr{Lutz Brellenthien}

\href{https://www.usnews.com/news/articles/2014/04/01/behind-russias-neo-nazi-propaganda-campaign-in-ukraine}{%
Behind Russia's 'Neo-Nazi' Propaganda Campaign in Ukraine, Paul D. Shinkman, usnews.com, 01.04.2014%
}

\iusr{Lutz Brellenthien}

\href{https://www.interpretermag.com/russian-neo-nazis-fighting-for-moscow-in-ukraine-ukrainian-jewish-leader-says/}{%
Russian Neo-Nazis Fighting for Moscow in Ukraine, Ukrainian Jewish Leader Says, %
Paul Goble, interpretermag.com, 31.08.2014%
}

\iusr{Lutz Brellenthien}

\href{http://anton-shekhovtsov.blogspot.com/2014/08/neo-nazi-russian-national-unity-in.html}{%
Neo-Nazi Russian National Unity in Eastern Ukraine, anton-shekhovtsov.blogspot.com, %
14.08.2014%
}

\iusr{Lutz Brellenthien}

\href{http://euromaidanpress.com/2014/08/27/russian-neo-nazi-kornilovtsy-battalion-operating-in-ukraine/}{%
Russian neo-Nazi \enquote{Kornilovtsy} battalion operating in Ukraine, euromaidanpress.com, 27.08.2014%
}

\iusr{Lutz Brellenthien}

Yes. Go and see what the russian fascists launched there.

\iusr{Rost Rost}

ha-ha, it's made by russian terrorists

\end{itemize} % }

\iusr{Dima Gavrysh}

Oliver, have you been to Kiev and spoke to people there? Have you travel to the
East of Ukraine? What is your methodology for this project?

\begin{itemize} % {
\iusr{Dima Gavrysh}

So? Did he annex the Crimea, or shot down MH17? Have you ever been to Ukraine
and know the people and culture? Or the intricacies of Ukrainian geopolitics
are much better seen from Timbuktu?

\iusr{Elena Selkova}

solo gli ucraini criticano è basta, se volete sapare qualche per essere meglio
informati sono 1)la russia ha preso la crimea per 2 motivi : ci sono le basi
miltare cosa succede se l'ucraina entra nella nato, le basi scompaiono, esempio
durante l'agressione usa in libia avevamo una base militare e indovina un pò
cosa è successo, poi la crimea è sempre stata fatta parte della russia devi
conoscere un po di storia, strano che che il giorno dopo dell'abbattimento
dell'aereo malese gli usa hanno deciso insieme agli ucraini prove di
esercitazione sul traffico aereo e infine finalmente hanno trovato un testimone
nn dall' occidente ovviamente e poi perchè la malesia nn può partecipare alle
indagini

\iusr{Andrea Bodrati}

@Elena Selkova penso sarebbe meglio scrivere in inglese visto che questo è un
forum in cui partecipano persone da tutto il mondo ma, da persona che vive in
Ucraina, ti dico che : Le basi militari Russe sono in affitto e quindi
l'Ucraina può decidere di interrompere l'affitto quando vuole, perchè la NATO
possa entrare in Ucraina ci vuole un referendum che, prima dell'invasione
Russa, non avrebbe mai avuto possibilità di passare (ora le cose sono
cambiate), la Crimea storicamente non è Russa ma è Tatara, la Russia l'ha
occupata per un periodo relativamente breve di tempo (300 anni circa)
massacrando i Tatari e sostituendoli con cittadini Russi. 2) Chi ti ha dato
questa informazine sull'esercitazione sul traffico aereo ? Ti assicuro che è
completamente falsa in quanto gli USA non forniscono nessun tipo di apparato o
consulenza sul traffico aereo Ucraino che è gestito interamente con apparati di
fabbricazione sovietica. Alle indagini partecipa eccome la Malesia, solo che
per convenione le indagini vengono svolte dal centro dell'ICAO (la stessa
organizzazione che ha obbligato l'Ucraina ad aprire il proprio spazio aereo
nonostante la stessa fosse preoccupata per la sicurezza) e quindi Londra con il
supporto appunto degli investigatori Olandesi e Malesi che coordinano le
indagini (basta leggere i report ufficiali dove sono riportati in nomi degli
ispettori).

\end{itemize} % }

\iusr{Oksana Putsylo}
Шоб ти здох

\begin{itemize} % {
\iusr{Максим Симонов}
Вот оно, истинное лицо поклонника переворота)))

\iusr{Svitlana Boyd}

Може, трошки і різкенько, ну він же плете страшну дурницю. Або йому Росія добре
платить або він застряв у своїх ветерансько-наркоманських снах. Мерзота просто,
фу...

\end{itemize} % }

\iusr{Victoria Barcelona}

Mr. Oliver, look at my profile and tell me: am I Nazi? I've been to Maidan. My
relative was killed 18. 02. 14 (64) by sniper. Was he Nazi? No. Nazi in Ukraine
is the myth made by KGB during Second World War to hide the fact that MORE THAN
1 M Russians for fighting with Hitler army. Learn history not from Russian TV.
How much money do you need for the movie about Ukrainian revolution? We will
pay double of what Yanukovitch and his guys offered if you make it with real
facts.

\begin{itemize} % {
\iusr{Dmitri Da}

Dear Victoria, you obviously haven't been following Mr. Stone's career  @igg{fbicon.smile}  if
you still hope that he is concerned with facts at all. Up until now, he was
regarded as a crazy but harmless conspiracy theorist. He just graduated to a
criminal accomplice of a murderous regime.

\iusr{Lisa Marie White}

Yeah except it's well documented that Ukrainians sided with Hitler and the
Soviet Army fought the Wehrmacht. So, I'm not sure who you think fought the
Nazis in Europe because it sure as hell wasn't the Allies, as they didn't
succeed in a land invasion until 1944. So...not sure what it is you are
smoking.

\iusr{Lisa Marie White}

link - fortruss.blogspot.com

Also, there's this.

\iusr{Victoria Barcelona}

Lisa, 50 k ukrainians vs 1 M russians. And if you don't know the history it's
better not to interfere. And for your info, officially more
than 11 million of Ukrainian soldiers were died in the W2.
Again, stop listening for a russian propoganda. Go to the
library.

\iusr{Victoria Barcelona}

Lisa, 50 k ukrainians vs 1 M russians. And if you don't know the history it's
better not to interfere. And for your info, officially more than 11 million of
Ukrainian soldiers were died in the W2. Again, stop listening for a russian
propoganda. Go to the library.


\iusr{Victoria Barcelona}

Lisa, are u kidding? You are sending me the link with the quote "Read what
russians read". Again, stop following only one source of information! It's 21
century, read and make analysis if you want to find the truth. Why don't you
want to show me link to the photos of thousands russian - nazi in Moscow?

\iusr{Robert De Cherry}

\href{https://ukraine-human-rights.org/the-pogrom-of-korsun/}{%
THE POGROM OF KORSUN, 14.08.2014%
}

\iusr{Robert De Cherry}

Victoria, it is stories like this link that use that word. But we all know they
only existed under Hitler and then it came to an end. I think their are people
who still chose this name in Germany and they are the 'skin-heads' and they
like the name, so they resurrect it. But you are right, it is a diversion and
is used as disinformation to categorize a specific group of people in
comparison with a group from the past. It is not very intelligent or effective,
and is confusing to people elsewhere in the world who do not know WHAT is going
on in Ukraine. And we know that we probably cannot believe what we read in
American newspapers. So your point is well taken, thank you.


\iusr{Victoria Barcelona}

Robert, the link u sent is a stupid, cheap lie. There are 3 group of people who
can believe and share this kind of low calibre propaganda: unintelligent
people, "trolls" paid by FSB to spread this bullshit worldwide and people, who
are lazy to search for more facts.

\iusr{Vladan Vraštanović}

What you talking about, you made one big mess  @igg{fbicon.smile}  It is clear that there are
nazis in Ukraine like they are in every Europe country. Diference is that nazis
in Ukraine have some power. That is a diference Victoria. Also KGB, Russians in
Wehrmacht, it is history fact that German army had units from Russians,
Ukrainians, Georgians...but it is also history fact that USSR crashed III Reich
almoust alone until 1944.

\iusr{Victoria Barcelona}

Vladan, don't take my time for writing the same answer: go to the library.
Obviously, you have gaps about WW2. Also read definitions what is Nazism,
Fascism and their core believes. Nazi in Ukraine powerful - bullshit. USSR was
an Allies of Hitler till 1941. Good luck with studying.

\iusr{Vladan Vraštanović}

Gaps about WW 2  @igg{fbicon.smile}  I read more books about WW 2 then you will read in your
entire life  @igg{fbicon.smile}  And what is wrong about that what I say, do you even know what
is Ostlegionen, what is Waffen-SS Galizien division, where it formed, you are a
joke, nothing but pure propagandist. And you talk me abou Nazism...USSR was
allie of Hitler until 1941, sure, but what bring them to that, do you even know
core of that, Munchen agreement in 1938, any idea? How Svoboda formed, what was
name of that party when it formed?


\iusr{Vladan Vraštanović}

You think that we are all here stupid CNN watchers which doesnt even know where
is Ukraine, well there are things which you dont learn from CNN, library I
think that it will be usefull that you also spend some time there arent  @igg{fbicon.wink} 

\iusr{Victoria Barcelona}

Bla-bla-bla-bla. Don't waste my time. RONA, Vlasow, RNNA.

\iusr{Vladan Vraštanović}

Haha, I hit you were it hurst  @igg{fbicon.smile}  Less CNN more books, less CNN more books  @igg{fbicon.smile} 
When you talk about RONA, do you know difference between Waffen SS and RONA?
And Vlasov, how he ended, remind me? Dont mess with expert  @igg{fbicon.smile} 

\iusr{Victoria Barcelona}

It seems that you are FSB troll. Go and get your salary. No heart, no soul, no
dignity.

\iusr{Vladan Vraštanović}

Offcorse I just received 10000 EUR check from mr. Putin for this few
comments:-) Girl just one advice if you want to talk about history and WW II
first be sure that person with you talking is not professor in that. Blaming
FSB for your empty brain is also not good option  @igg{fbicon.smile} 

\iusr{Victoria Barcelona}
Vladan, you are a cool man! Your mother must be proud of you.

\iusr{Serhiy Uryn}

Victoria, thank you. This line is packed either with Putin's trolls or "useful
idiots" as another madman - Lenin - once defined them. We, in Ukraine do not
have money to pay for the first group, but Russia apparently still has the
budget. Not for long, though


\iusr{Katerina Kramorenko}
well done Mr.Oliver

\iusr{Martin Schröder}
Which side were the snipers on if they shot people of both sides?

\iusr{Maria Shysh}
Hitler and Stalin were buddies who carved up Europe amongst themselves, until they had a spat  @igg{fbicon.smile} 

\iusr{Oksana Kudrya}
Ты - мож и не наци, а так, просто себе дура набитая.

\iusr{Alex Alex}

Victoria your goverment will soon sel your country for cents for USA, so better
better go and make some real good things for your Ukraina and not reply hear at
Facebook for Putin trolls))))

\iusr{Peter Kratochvíl}

Yes, they are nacist. May be they do not know anout that. If they fight agsinst
people in east and not against nacist government in kiev, what wirld can think?
Please, do not believe to kiew or usa propaganda, more people in eu is
absolutelly against your government. Do you think eu or our country eill send
you money? No. Finish. You just get money for weapons. What you will eat? Do
you like your parluament new laws?

\iusr{Victoria Barcelona}

I don't give a shit what you think about my Ukraine. I don't care about you,
because you are "0". So mind your own business and improve your own life,
loosers. And yes, we are weak now. But we will win. And you will remain stupid
slaves forever.

\iusr{Борис Забудский}

Ни хрена вы не победите. Фашистов били и будут бить во всём мире!

\iusr{Philippe Hanmann}

Lisa Marie White seems to be forgetting that the Nazis and the Soviets were
great friends and carved up Europe between them. The so-called 'Great Patriotic
War' only started when one evil dictator fell out with the other.

\iusr{Marijka Stadnyk}

Fact, Putin's father was a Nazi himself, a collaborator. Apple doesn't fall
from the tree. Usually, the ones who go around accusing others, are that
themselves.

\href{https://www.youtube.com/watch?v=ACoJKdNKX2A}{%
Vladimir Putin's Father a NAZI Collaborator ?!, youtube, 27.09.2013%
}

\end{itemize} % }

\iusr{Alexander Gevorkyan}

I am just a moviegoer. I never had a wish to communicate to moviemakers, to
send them messages or something like this.

First time when I wanted to do this was after I've seen your film Alexander
many years ago. I was disappointed, I was upset. I could not understand how a
famous director could spoil such theme. You had a chance to tell about the man
who raised himself to the level of gods.

You had a chance to tell about the man who opened new horizons to his
contemporaries. You had a chance to tell about the man who laid the basement of
our civilization. You did not do this. The only thing you said was the
statement that Alexander was a gay. You did not find anything else to tell
about Alexander. I have not written anything to you then.

You corrupted the image of Alexander. Well you can tell that it was your vision
so it is ok.

Why do I write to you today? Because I live in Ukraine! You know, the people in
my country have shown so many examples of courage, generosity and devotion to
the ideals of freedom like nowhere on the Earth this year. But you seem are not
going to tell about this.

You listen to Yanukovich. I do not think that you are so naive to believe to
the Yanukovich's words. But you pretend that you believe him.

I do not ask you why. I just want you to stop for a moment and to think. What
side are on - Good or Evil?

How will you feel when you will corrupt the image of my country.

I do not care about your soul, I think about a lot of your fans who trust you.
Do not corrupt their souls.

\begin{itemize} % {
\iusr{Tatyana Burak}

Спасибо за вашу информацию о бандеровцах и т.д. Надеюсь, что это хоть кому-то
поможет изменить свою позицию. Это особенно касается нашего донецкого региона,
где большинство людей, вскормленные советской пропагандой, понятия не имеют о
реальной деятельности Бандеры, УПА и о том, что происходило в Западной Украине
после войны.


\iusr{Martin Schröder}
You should direct your "generosity" at restoring Donbas.

\iusr{Svitlana Boyd}
Дякую Вам, Олександре!

\iusr{Alexander Gevorkyan}

To Gérard Ecorcheville: only fools and scoundrels say such things. The first
ones just cannot tell the truth from lies, the second ones get profit by saying
that.

\end{itemize} % }

\iusr{Никита Козачинский}

Yanukovych - the man who prepared the Ukraine, for the annexation of the Crimea
... This guy was a Russian agent. But Yanukovych was a dictator., Man has put
all public offices, its people .. They completely destroyed the Ukrainian army
.. and unleashed in the east of my country's war . I participated in the
protests in Kiev. Some of my friends have already died .. Or in Kiev or in the
east ... Every day of the soldiers killed someone else .. You're talking about
the Cold War, while a 2-hour drive from my house, people are dying every day ..
Over their choice for their freedom. Come to Ukraine., See for yourself. Talk
to people. Sanctions work. But special assistance from the United States, we did
not get .. Very hard to resist Russia alone .. They are simply much more ... We
are in need of international assistance to support ..Protective equipment,
transportation, medicine, international experience... The US government may be
three times insidiously .. But cha talking about something else., About my
country, which Russia wants to break into pieces ..

\ifcmt
  ig https://scontent-frt3-1.xx.fbcdn.net/v/t1.18169-9/10888959_893359147362693_2102857977891552056_n.jpg?_nc_cat=102&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=nMBtDzMKAFIAX8ELL17&_nc_ht=scontent-frt3-1.xx&oh=4e70f2871e5fa20a9bfeaeac5747ccea&oe=61CDA428
  @width 0.4
\fi

\begin{itemize} % {
\iusr{Vincenzo Lachimera}

Kharkiv, Odessa, Kherson all want out. The Kiev insanity and oppression of the
predominantly Russian speaking regions will expand the civil war beyond the
Donbass. Ukraine is an artificial country created after WW1, it will return to
its former borders..after very much bloodshed, hooray!

\iusr{Tom Dal Magro}
\textbf{Vincenzo Lachimera} Thank you for your ignorance.

\iusr{Steve Poe}

Parts of Southeast Ukraine that are occupied by West Ukrainian nationalists are
seeing the level of political repression, political mureders and arrests at the
hands of Neo-Nazis that Ukraine hasn't seen since Stalin. To say that most of
Ukraine lives in "pease and harmony" is a blatant lie.

\iusr{Александра Смилянская}

Steve Poe. Does somebody pay you for that bullshit or you just like to lie?
Every people who was in power during Yanukovich's time is still keeping that
power today. It's no arrests, Steve. No one.

\iusr{Изюзь Изязев}

Точные процентики постят политсры доцентики для пущей убедительности)

\iusr{Yulia Porozhna}
\textbf{Vincenzo Lachimera}, were're you live?? In Kharkiv, Odessa, Kherson? Therefore, shut your mouth and shut up, please.

\iusr{Andrea Bodrati}

@Vincenzo Lachimera : even most of Donetsk and Lugansk people don't want out of
Ukraine and, in fact, have decided to live in other cities in Ukraine, official
UN statistics speaks of about 1,1 million peoples. I would also like to remind
there was a referendum where all the Regions you mention voted for indipendence
from Russia and for Ukrainian State, not citing multiple opion polls made even
by Russian companies. In Kherson there are thousands of volunteers training to
fight in case of invasion and in Kharkiv at the last separatists meeting
attened less than 50 persons.

\iusr{Александр Янчук}
If Yanukovich was the Dicator, than Poroshenko is simply Murderer. This is only one comment here.

\iusr{Юрий Сорока}

I speak Russian and have no desire to live in Russia's GULAG. I will fight for
the freedom of my country Ukraine untill Russia collapses and gets dismantled,
reduced to the size of jail cell for Putin and his thugs. And we are MILLIONS!

\end{itemize} % }

\iusr{Johan de Broyer}

\ifcmt
  ig https://scontent-frt3-1.xx.fbcdn.net/v/t1.18169-9/10888974_10152531995838045_6805410348334441594_n.jpg?_nc_cat=102&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=MVn9QNfDb8oAX8Q67dS&_nc_ht=scontent-frt3-1.xx&oh=7b1ca9fbafb92e7b1747cde6d9532c6c&oe=61CDBF81
  @width 0.4
\fi

\begin{itemize} % {
\iusr{Svitlana Tuchynska}
no, this is Putin's democracy

\iusr{Mike Dobrin}
blame Putin

\iusr{Arthur Rogers}
Russia invaded Ukraine. People are dying in Donestsk because Russia invaded. IS there something wrong with your brain?

\iusr{Abraham Hazou}

Russia sends in humanitarian aid, obama sends more weapons to the puppets in
Kiev to subdue (murder any opposition) in Donbass where Joseph Biden's son
tried to exploit the shale gas reserves in the region.


\iusr{Fatimah Zerga}

The sad truth is that it's neither of them. Ukrainian soldiers are killing
their own citizens...... Whatever someone's political belief, shooting at them
because of it is a warcrime. So blame Putin, we know it's scum like you doing
it.

\iusr{Ярослав Вішталюк}

Abraham Hazou, "humanitarian aid", really? Why russians was not allowed Red
Cross check this "humanitarian aid"?

\iusr{Юрий Сорока}

Putin's "humanitarian aid" in Eastern Ukraine made it to the New York Times:

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t31.18172-8/10857389_10203406966516480_7565675344988866439_o.jpg?_nc_cat=100&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=SSR85PqnYUoAX-R6zQS&_nc_ht=scontent-frx5-1.xx&oh=1b1f1d95f09f66b776017a71ccd26b43&oe=61CCFB6B
  @width 0.4
\fi

\iusr{Юрий Сорока}
Putin's great democracy:

\ifcmt
  ig https://scontent-frt3-2.xx.fbcdn.net/v/t1.18169-9/10897878_10203406973436653_5576332219808678693_n.jpg?_nc_cat=103&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=sFseeYG4dGEAX8AQ7hL&_nc_ht=scontent-frt3-2.xx&oh=575660b786ac9284a04c9b3c5ed0a4b6&oe=61CD4C70
  @width 0.4
\fi

\iusr{Johan de Broyer}

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10897846_10152545709443045_9120663982460638962_n.jpg?_nc_cat=105&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=IKBcr66mAhMAX9E_lV-&_nc_ht=scontent-frx5-1.xx&oh=34570fad25c893fbf4976e2a7d27fa0d&oe=61CB123D
  @width 0.4
\fi

\iusr{Ilhan Shirinov}
Putin is a rescuer of peoples´ lives, whereas ukraine is a bandit failed state

\iusr{Johan de Broyer}

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10885122_10152545771483045_2291898652892639044_n.jpg?_nc_cat=111&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=2khO6q8d2WgAX8IQ90L&_nc_ht=scontent-frx5-1.xx&oh=07491e7813eed7fc53899c212ebdf147&oe=61CB00BD
  @width 0.4
\fi

\iusr{Piotr Chmurnik}

Putler is an officer of the KGB and had ordered the killing of people in
Ukraine That Russia invaded a sovereign country and is the bandit.

\iusr{Johan de Broyer}

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10897846_10152545709443045_9120663982460638962_n.jpg?_nc_cat=105&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=IKBcr66mAhMAX9E_lV-&_nc_ht=scontent-frx5-1.xx&oh=34570fad25c893fbf4976e2a7d27fa0d&oe=61CB123D
  @width 0.4
\fi

\iusr{Johan de Broyer}

\ifcmt
  ig https://scontent-frt3-1.xx.fbcdn.net/v/t1.18169-9/10603785_10152546300753045_9179912487864336604_n.jpg?_nc_cat=102&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=k0nzODM0CCYAX_tEeZn&_nc_ht=scontent-frt3-1.xx&oh=d753a1a405634a660bff5ebe38571ef4&oe=61CBA204
  @width 0.4
\fi

\iusr{Arthur Rogers}

\ifcmt
  ig https://scontent-frt3-1.xx.fbcdn.net/v/t1.18169-9/10891669_10152883175101066_3861843023193505812_n.jpg?_nc_cat=102&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=vZtqePDjdgMAX9F4l2n&_nc_ht=scontent-frt3-1.xx&oh=07bc084446714479d7187d4a662f8224&oe=61CB247D
  @width 0.4
\fi

\iusr{Arthur Rogers}

Putin's "humanitarian aid" is troops and weapons. Are you really so stupid to
take it at face value?

\iusr{Arthur Rogers}

\ifcmt
  ig https://scontent-frt3-2.xx.fbcdn.net/v/t1.18169-9/10406508_10152883175821066_1570649831251079200_n.jpg?_nc_cat=103&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=F8lEUw4avqkAX-Cc-V5&_nc_ht=scontent-frt3-2.xx&oh=d275f1ced672d0aeaf8dd872a2e0b913&oe=61CA8B35
  @width 0.4
\fi

\iusr{Arthur Rogers}

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10888752_10152883176121066_648996064781750625_n.jpg?_nc_cat=111&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=9iti137K0BoAX-9KbFW&_nc_ht=scontent-frx5-1.xx&oh=46a85f1e795d57dab4f11eeadfb93806&oe=61CAA383
  @width 0.4
\fi

\iusr{Oleksandr Povietkin}
many citizens were shoot by pro-russian separatists and terrorist, what does obama have to do with it?

\iusr{Ceased To Excist}
Putler...
Biggest f-ing nazi-swine since the real thing!
:))

\ifcmt
  ig https://scontent-frt3-1.xx.fbcdn.net/v/t1.18169-9/10384585_560487787415421_7740718002503447027_n.jpg?_nc_cat=102&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=P7HcVv1dghoAX-hyvTf&_nc_oc=AQkdfxiyO_qxH1cEoGjORgZmyp91Wtf_8xQ5Ni55y_JPk2s6OtvfPxXQtYktTDMxzeE&_nc_ht=scontent-frt3-1.xx&oh=ccb3448f07de23628f54356d9bc112c7&oe=61CDC050
  @width 0.4
\fi

\iusr{Philippe Hanmann}
Just another Moscow troll.

\iusr{Dušan Radosavljević}

Arthur Rogers, really...with the photo that shows ukrainian nazis (you can see
the flag on the right side of the Hitler's flag)...

\ifcmt
  ig https://scontent-frt3-1.xx.fbcdn.net/v/t1.18169-9/10968586_428381920651757_6221004703715761565_n.jpg?_nc_cat=106&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=OYnh2XCmUoIAX-EqCDj&_nc_ht=scontent-frt3-1.xx&oh=a4aeefb9d7754b93c8d3d17a3ba848d9&oe=61CD18F8
  @width 0.4
\fi

\end{itemize} % }

\iusr{Bogdan Kolesnyk}

More conspiracy, this is getting dull. Did you bother to ask Ukrainians about
their own history? Hardly, as you wouldn't let yourself look ridiculous,
spewing this nonsense. If you are interested in the big picture, you might need
to expand your horizons beyond pseudo-historical conspiracy theories and engage
with broader issues affecting Ukraine

\begin{itemize} % {
\iusr{Александр Янчук}

Богдан, а ты сам то историю хорошо знаешь? Если так- пойми наконец, что на
востоке и на западе Украины живут разные люди. И то, что вы не слышите восток-
это плохо очень. Там люди тоже сделаны из мяса и у них есть свои интересы.
Нужно как то договариваться, а не сжигать их и не бомбить.

\iusr{Bogdan Kolesnyk}

понимаешь, Александр. Так уж вышло, что есть суверенное государство и отдельная
страна Украина. Так вот внутри этой страны в последние десятилетия особых
проблем между, как ты говоришь, "разными" людьми востока и запада не было. Но
оказалось, что если заслать в эту страну кадровых военных, политтехнологов и
всяких маргиналов с оружием из страны соседней - то результат будет война. Так
что всем кто справедливо волнуется за судьбу людей на Донбассе стоит активно
противодействовать интервенциям со стороны вот той самой соседней страны.

\end{itemize} % }

\iusr{Оганесян Иван}

So far we have worse government ever! Not only corrupted, but fucking bloody
one! Thous fuckers stealing so much from the most poor people, sending them to
kill each other, and explaining that no one is guilty but Putin, and i'm sure
you know that! Just wanna people to get more information from the inside of UA,
cos i'm from Kiev I'm Ukrainian, born in UA, thanx for your real human
position!cheers and a happy NYE. Ivan

\begin{itemize} % {
\iusr{Eric Kraus}

yes, for all his sins, Yanukovich refused to use the army against his own
people - something which the Kiev regime has never hesitated to do


\iusr{Kevin Keating}

Putin an acolyte of the drunken bum Yeltsin. Both Lenin and Stalin guided the
construction of the world's first Socialist State. Stalin smashed the Nazi's,
repelled their invasion of the USSR and as General Dwight Eisenhower said: "One
of the most brilliant military campaigns/victory in world history."

\end{itemize} % }

\end{itemize} % }
