% vim: keymap=russian-jcukenwin
%%beginhead 
 
%%file 02_05_2022.fb.solovjov_mikita.harkov.demsokyra.1.hronika.eng
%%parent 02_05_2022.fb.solovjov_mikita.harkov.demsokyra.1.hronika
 
%%url 
 
%%author_id 
%%date 
 
%%tags 
%%title 
 
%%endhead 

Chronicle of Kharkov, May 2.

A little more shelling today than in the last two days. In addition to the
traditional Saltovka and Pyatihatok, there were flights along the KHTZ. That
is, still noticeable less than a week ago, but more than the previous couple of
days. I honestly can't understand where the HTZ was fired.

There are plenty of shooting around the area. From the famous Malaya Danilovka,
Zolochev, Bogodukhov, Chuguev, a very strong Slatino shelling. There are
victims. Naturally, a lot of destruction.

In the city and region, where possible, active infrastructure restoration work
continues. In addition to the point lathe holes to somehow provide light and
other things, serious works are carried out in some places, such as the
replaying of medium diameter pipes. (Just in case. Everything except the main
road is called "average". In fact, this is the largest diameter and pressure
you can ever find in the city. ) Road works are actively continuing. Don't
judge the area. But in the city without electricity and gas, there are only
those microdistricts in which the restoration of networks is impossible and
they have to be completely pulled again. At least on many sites.

Sometimes I wonder about the evacuation situation. Now not only in the most
affected neighborhoods of Kharkov, but also in other settlements of the region.
Here is Slatino example. Regular shelling. The utility networks do not work at
all. No light, water, gas, almost no mobile connection. Of course, there are no
operating shops. A sea of possibilities. Only volunteers constantly offer
options. But about 200 people continue to sit there firmly. This is quite a
small percentage, order 3-5 from the pre-war level. But people resist and
refuse to leave. And this is not an exception, this is a standard situation. In
the less affected settlements, even more percentage of the remaining. Even with
daily or regular shelling.

And two things are clear. That with such mass destruction, the infrastructure
will not be possible to quickly restore. Especially, with regular shelling. It
is theoretically possible to conduct some economic activity. (Don't be
surprised much, but many of the gardens are already planted right under
shelling. ) But it all increases the risks many times. I think it is critically
important to understand why people refuse to leave and try to eliminate these
reasons for refusal. To persuade. In critical cases, both Slatino or R.
Lozovaya, it is possible to announce a mandatory evacuation. There is a good
right like this in the temporary military administration.

Perhaps in a couple of days I will be able to tell you more about these
refusals. I'm going to hang out with them in the coming days, first in the
outskirts of the city.

And in the center of the city, some kind of life and some kind of life are
getting better. It looks like spring coming or morning glow. Every day seems
like no noticeable change from yesterday. But a couple of weeks later, and
everything has already changed. More and more services are running. More and
more people are just walking on the streets. More and more people (although
still very few, of course) have found some occupation and a way to earn money.
More and more cars. The city doesn't look like it did two or three weeks ago.
But it feels like the city needs some push for further recovery. And I can't
think of anything more important than starting public transport.

Kharkov is standing!

Glory to Ukraine!

A low bow to our defenders!

\#ХроникаХарькова
