% vim: keymap=russian-jcukenwin
%%beginhead 
 
%%file 31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.cmt.popov.brave_man
%%parent 31_12_2014.fb.stoun_oliver.kinorezhisser.usa.1.nightingale_in_ukraine.cmt
 
%%url 
 
%%author_id 
%%date 
 
%%tags 
%%title 
 
%%endhead 

\paragraph{Nikolai Popov - Mr. Oliver Stone, you are very brave man !!!}

\begin{itemize} % {
\iusr{Nikolai Popov}

Mr. Oliver Stone, you are very brave man !!!. I don't care about angry people
... I like you want show the true .. Its not easy ...

I hope angry people will understand later ... Thank you. Happy New Year! All
the best, good health to you, your family and friends. Nikolai.

\begin{itemize} % {
\iusr{Ihor Semyda}
shut up pridurok!

\iusr{Nikolai Popov}
The war in Ukraine, because same people like you are !

\iusr{Nikolai Popov}
And I am surprised, mr. igor Semida, you have finished university in the Kiev, you don't sound as intelligent person ....

\iusr{Dmitry Bocharov}
Да они все такие

\iusr{Nikolai Popov}
Спасибо. С Новым Годом Вас и Ваших родных и близких !

\iusr{Piotr Chmurnik}
\textbf{Dmitry Bocharov}
Это не украинцы атаковали Руси, только Россия напала на Украину. То, что Россия бандит.

\iusr{Тата Аталон}

Россия- страна агрессор, подлый и низкий. Это говорю вам (специально с
маленькой буквы- без уважения) украинка из русскоязычного Харькова. Я презираю
вас.

\iusr{Sergiy Stakhovsky}

Says russian who lives in Canada))) what a joke))

\iusr{Arthur Rogers}
Showing the truth is especially hard when you are lying.

\iusr{Nikolai Popov}

I don't think you are real Ukrainian, ; to make war in Ukraine is your choice,
but not to make piece; ; to make conflicts in Canada is not your business, you
are really behind hundred years , you need more education, I think, or just to
be a human...

\iusr{Nikolai Popov}

Time will show the truth...

\iusr{Nikolai Popov}
To: Tata;
Russia saved your brothers and sisters from Nazi, some of them were killed and burned during War 2
You need more education and just read
The History , if your Ukranian older relatives did not tell the past

\iusr{Nikolai Popov}
To Tata : Symbol Hitler'ss on banner in Ukraine

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10888567_393871820770070_4883822210083832961_n.jpg?_nc_cat=111&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=1ukyujIxb-8AX9c29mj&_nc_ht=scontent-frx5-1.xx&oh=6f9664cd44226e01ea2bd7134935da84&oe=61CDCA6F
  @width 0.4
\fi

\iusr{Yaroslav Zadorovskyy}

"Russia saved your brothers and sisters from Nazi"

BAHAHAHAHA yeah right! But first they became close Nazi allies to help them
train and build up Hitler's army in order to split up Europe. Soviet and Nazi
troops training together as brothers, performing on common parades, kissing and
hugging on old photos. :)))

\iusr{Martin Schröder}

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t31.18172-8/10714146_692866524164452_3831124159610218020_o.jpg?_nc_cat=105&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=oGhbhKa26zIAX9D22vi&_nc_ht=scontent-frx5-1.xx&oh=1ae82d46d9a32d2f9bfe6cd22b3d9bda&oe=61CE2DFC
  @width 0.4
\fi

\iusr{Martin Schröder}
I will file a petition to put a nazi symbol, or two  @igg{fbicon.wink} , on every flag of the earth.. becuz it's kewl..  @igg{fbicon.wink} 

\iusr{Nikolai Popov}

Your choice... You will do it probably , because different time now , and no
option to go Nazi chamber for you yourself .,. Only jail for your safety ...


\iusr{Nikolai Popov}

To Yaroslav Zadorovskyy , I live now and don't support Nazi, if you are ...
Waist of time to talk with you that's why war in Ukraine ,

Probably people like you or other who brainwashed and put Nazi Symbol on
Ukrainian Flag...

\iusr{Nikolai Popov}
File petition Martin Schröder, but before doing this Don t hide photos in your file ...
... And go to hell

\iusr{Христина Грищук}
Popóv or Pópov, why you live in Canada?! you have to live in your the best ever ruSSia

\iusr{Sergiy Stakhovsky}

Russians saved?? Really?? Ribbentrop-Molotov agreement killed how many?? Russian invaded Poland ..if that is saving they you are more dump the I though

\iusr{Nikolai Popov}
You mistaken I don't suppprt SS, you sounds , you are , Gryshchuk,
Sounds angry, that's why war in Ukraine , don't think you should live in Ukraine, it's not your Country , yours is SS place

\iusr{Nikolai Popov}
I m sure , once the border will be open, you will run away from Ukraine,,

\iusr{Nikolai Popov}

Yes, many mistakes of politicians in the past and now , the fact is Russians
won the war , and russian people were killed by Russians , same as in Ukraine
now...many soldiers died for Poland against Nazi , I saw cementary in Poland.
Polish people respect Russian people , who fight for them .,, Russians don't
put SS symbols on Russian flag, Some Ukranian do..

Why ? Do you have explanation?


\iusr{Rob Decoup}

Nikolai you would also be angry if Russia invaded your country and killed over 5000 of your citizens!
Dont listen to russian propaganda.
Biggest nazi is the little man in the kremlin!

\iusr{Yaroslav Zadorovskyy}

Nazi Symbol on Ukrainian Flag...

1. Ukrainian flag does not have any symbols on it - just Sky blue and light
yellow  @igg{fbicon.smile} 

2. That's not a Nazi symbol, but an old rune. Soviet symbols are also
prohibited in EU for example, but that makes me wonder why nobody from EU
accuses China or US for using five pointed star on their flags :)))

3. Finally, Putin is and always was widely supported by neonazi parties that
shout Russia is for Russians only etc. Their parades are full of young people
with neonazi flags mixed with soviet symbols and ultra-right slogans. Why don't
you say something about that for a change?  @igg{fbicon.wink} 


\iusr{Nikolai Popov}

To Mark, I against any Nazi, don't understand your point ... But I can see
Ukranian flag on background... What does it mean ?

\iusr{Nikolai Popov}
On it , or with it (about symbol on flag)
no big
Differents , Some
Not people with Ukranian flag marching with Nazi flag , and people like you don't stop them ... That's why war in Ukraine... I love Ukraine and love good Ukranian people , who stands for Peace .

\iusr{Nikolai Popov}
To Yaroslav

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10422559_394249127399006_6245941543962508600_n.jpg?_nc_cat=105&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=Dz9uRwDAdzEAX_EBiXa&_nc_ht=scontent-frx5-1.xx&oh=2a66c4b3c648617a42666a45d3e05343&oe=61CDF805
  @width 0.4
\fi

\iusr{Nikolai Popov}

Rob , how you can prove about Russian people? Do you live in Ukraine? In
Russia? Did you see that ? Do you have evidence ?

Why for expression opinions and trying to find the true , people from Ukraine (
they are not real Ukranian) wish to die to mr Oliver Stone and all supporters
(???) is it not Nazi people...(???), why they put together symbol of SS and
Ukranian flag , and why they don't stop yet,,,, why support them ?

\iusr{Nikolai Popov}

To Yaroslav, it's not just about symbol, it's abou angry and hate...

This type of people want to build life , piece, based on Angry , hate , wishing
to die or kill other people... even to torure them ..: do you support them ???

\iusr{Nikolai Popov}

Why many countries separated from Russia, most of the without killings, ???

What happened in Kiev ? Why People killing each other ??? Who is who ? If you
have prove , just put in Media or sent to mr. Oliver Stone, why people from
Ukraine angry and wish to die,! are they real Ukranian people or just criminals
... living in Ukraine

\iusr{Yaroslav Zadorovskyy}

we don't kill each other and don't hate each other. We live on our God given
land and want to live in peace, but if anyone will try to take it from us we
will fight and we will kill - just any of 200 countries on the Globe. There is
no other hate but hate for our enemies capturing our land, but do you really
think we should love them?


\iusr{Nikolai Popov}

What about people in Kiev, who were there ? Who killed Ukranians ... Russians
??? I feel sorry for innocent people who died ...no killing were in many other
countries for Piece and I independents ..,

Time will show the true ...

\iusr{Yaroslav Zadorovskyy}

In Kyiv civilians were shot by militia and special forces loyal to corrupt
government of Yanukovych that was in fact supported by V. Putin.

\iusr{Nikolai Popov}
How do you know , it's not other agents ? Not foreign countries ...
too much hate in Ukraine, ;
Why it did not happened in other former republic of
USSR , like Baltic countries separated without killing people

\iusr{Nikolai Popov}
You want to say no corruption now in Ukraine ?

\iusr{Yaroslav Zadorovskyy}

Some of them were other agents - FSB in fact. There is much corruption even in
EU, but now in Ukraine government does not kill or arrest civilians just for
going out for a protest.

What do you know about hate, are you a hate expert, or smth that you throw
these words just like that? Can you give us all an estimate on exact hate
numbers or percentage perhaps?  @igg{fbicon.smile} 

\iusr{Nikolai Popov}

Number of hate ? You need another 100 or more years to change or be better
::you throw the word "kill", to kill your ex president , you voted for him, to
kill other presidents , any body who take your land, even own Ukranians who
want normal life, no war.. You don't know what you talking about to "kill", if
real war you live 30 min, me too

Think before you turn on your emotions ... Non of Ukrainian mother wants her
son fight for land at cemetery ...you ignoring the fact that Baltic countries
become independent without killing , they not far from you ...

I know many examples , real stories about people in Ukraine , don't play stupy

\iusr{Yaroslav Zadorovskyy}

I didn't vote for him just as other tens of millions of Ukrainians. He fixed
his elections and in fact was illegal president from the start. No one wants to
kill or die but it's better to die as a free man, than live as a slave. So
don't be stupid yourself - you would have done the same thing if China or US
invaded Russia, so cut your rubbish chat about normal life. Sometimes you just
have to fight for it just like your grandpa did during WW2.

\iusr{Nikolai Popov}

You did not vote, other Ukrainians did ... I don't live in Russia, I live in
North America , where more then 300 hundreds nationalities live here and they
are not slaves and they are not fight and kill each other , even in your
statements too much negativity "better to die", this is your choice , people
like you ,,

make war, and get lessons from this war , unfortunately innocent people die ..,

"Play stupy" and "don't be stupy" it's different meaning ... My grandpa and
grandmo born in Ukraine ..and German soldier saved her with 2 kids from SS Army
You need another 100 years , we speak "different" language

Many statements of people who live in Ukraine are very angry , they against
Russians, same Slavic group of people, in America people get married black with
white , Asian with Caucasian , you are one of angry people and " better die"
your words ,, nobody want make you slave , slavery time were in USA, but you
support agents from USA, and don't want see the true ...

\iusr{Orest Andrijiw}

Mr. Popov. Suggest you read normal history books. Russians are not and never
been Slavs. This is fact. Unfortunately for you, your version of history is
based on old russian lies and propaganda.


\iusr{Nikolai Popov}
Orest you don't know me to make your statement,
you read the books ,
go back far , Kiev was a capita of old Russia

\iusr{Nikolai Popov}
Capital city

\iusr{Nikolai Popov}
Yes , language is very similar and close, but its not the main points
I hear you : people like you make war in Ukraine,
but you run away from Ukraine
Not sure if you also support Nazi

\iusr{Marusia Stashynsky}

You want the truth?! Go to Ukraine! Talk to the people!!
Listening to a corrupt killer and thief has no credibility!

\iusr{Myla Ustymenko}

Nikolai, Kyiv was a capital of Rus, not Russia. Russia was called Moskovia up
to 1721. It did not have anything to do with Kiev Rus, except the fact that
Kievan Prince Yuri Dolgoruki founded Moscow.

Also, I want to remind you that Soviet Union sided with Nazis from the
beginning of the WWII up to June 22,1941. Soviets not only sided with Nazis but
invaded Poland together, held a joint military parade, and had a joint
NKVD-Gestapo conference. Red Army supported Nazis. You admire Red Army. Does it
make you a Nazi supporter?

\iusr{Nikolai Popov}

Myla, I did not say anything about Red Army , you do , do you support Nazi ? I
am against Nazi . Some people in Ukraine put together symbol SS and Ukrainian
flag ; you support this , they did support Hitler'ss, do you ??? It's a crime
against humanity... Be human don't send your children , if you have, to die...


\iusr{Nikolai Popov}

For Myla , is this "people " in Ukraine not NAZI ? You have to live now and
believe facts, is it humans, Ukranian soldiers sent missiles to civilian
buildings , killing children and women... Do you know that . I feel you support
more Army , and again you are one of many numbers angry people, who boost the
war ..

But probably you don't have son and children who can die there , read more
books

\ifcmt
  ig https://scontent-frt3-2.xx.fbcdn.net/v/t1.18169-9/10690097_394481014042484_7283752279044289637_n.jpg?_nc_cat=103&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=28VFWu7bYu8AX_jFzKT&_nc_ht=scontent-frt3-2.xx&oh=7c621dc01f08c97d0bfb1b0536a4eaeb&oe=61CC38B2
  @width 0.4
\fi

\iusr{Nikolai Popov}

Myla, you are one of the angry people who lives in Ukraine , one of them , who
wants the war.. You making and changing my words in your way, very provocative,
but you are not in Ukraine now , you don't know what is drama there and people
die, because people like you "put more gasoline " in fire of the war ... You
need to be more educated and be more human


\iusr{Nataliya Kukhar}
Popov you are kremlin troll

\iusr{Nikolai Popov}
Kukhar you don't know me ... You are one of the angry "people " in Ukraine, who creates the war ... Be human, save your children , if you have

\iusr{Nikolai Popov}
For Kukhar , do you support them ?

\ifcmt
  ig https://scontent-frt3-2.xx.fbcdn.net/v/t1.18169-9/10690097_394481014042484_7283752279044289637_n.jpg?_nc_cat=103&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=28VFWu7bYu8AX_jFzKT&_nc_ht=scontent-frt3-2.xx&oh=7c621dc01f08c97d0bfb1b0536a4eaeb&oe=61CC38B2
  @width 0.4
\fi

\iusr{Nikolai Popov}
Kukhar , unfortunately you don't know what is the war...if real war happened , it s not gonna help you , even you run away in USA, you , all, me too have not much time to live ...
Think , before you "support " Ukraine been in USA, saying provocative angry statements ...

\iusr{Yuri Vsevolod}
\textbf{Nikolai popov}, I do know what the war is. The fact that new Ukr govt is not nazi along with other Moscow propaganda has been approved by UN, OSCE and other world peace organizations. The fact that Russia is ripping Ukraine apart to build a new Empire- has been proven at the level of UN General Assy. People like you support Putin's crimes against humanity. People like you supported Hitler annexation of Austria, Czech, and Poland.

\iusr{Nikolai Popov}
\textbf{Yuri Vsevolod} , do you support them ?

\ifcmt
  ig https://scontent-frt3-2.xx.fbcdn.net/v/t1.18169-9/10690097_394481014042484_7283752279044289637_n.jpg?_nc_cat=103&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=28VFWu7bYu8AX_jFzKT&_nc_ht=scontent-frt3-2.xx&oh=7c621dc01f08c97d0bfb1b0536a4eaeb&oe=61CC38B2
  @width 0.4
\fi

\iusr{Nikolai Popov}

I support mr. Oliver Stone, he is American, lol. Don't change my words ! You
are one of the hundreds people who wants the war, but do not live in Ukraine,
go there take machine gun from your photo and just go there , to fight for
humanity, lol

\iusr{Nikolai Popov}
...hope Mr, Obama will stop you .. Lol

\iusr{Nikolai Popov}
Kukhar... I never been in Kremlin, lol

\iusr{Yuri Vsevolod}

\ifcmt
  ig https://foreignpolicynews.org/wp-content/uploads/2013/11/Russian-Nazis.jpg?fbclid=IwAR3S-0otgapP0Uhf3Y6oz1cOj1UWYXhfr_-g7zVZdxgtLRTUov59RxQOdVU
  @width 0.4
\fi

Do you support these people? Its very immature of you trying to cling to the
same arguments that have been already proven to be false. What will you say
next? That NATO tried to make Crimea a military base and thats why Russia
occupied that place in force, while lying that its not them? Or will you say
that free people of Donbass are fighting against Nazi occupiers?

\iusr{Stefan Sass}

If Nikolai Popov wants to assist with whitewashing Yanukovych it onlky proves
that sadly you can fool some of the people all of the time.

\iusr{Yaroslav Zadorovskyy}
\textbf{Nikolai Popov}, 

I really doubt you are from Canada - Canadians NEVER call their country North
America, but people pretending to do so often do, just as those who think there
is a line "nationality" in Ukrainian passport.

Where in all of my posts you've read that I hate Russians or other Slavs? Stop
thinking up what is missing. I hate those who invaded my land and brought war
and I don't care wether they are Russians or Canadians of origin. We've lived
peacefuly 23 years and there was no hatred whatsoever until putin started
messing up things when he realised he's loosing control over Ukraine, after his
puppet Yanukovych fled to his puppetmaster.

"Kiev was a capita of old Russia" There was never such a thing you call old
Russia. Kyiv was the capital of Kyevan Rus. Name Russia was first introduced
only in 18th century.

\iusr{Dave Antill}

Nikolai let's hope mr stone make a film about Mr Putin's corruption and murders
too . There is no shortage of incidents

\iusr{Nikolai Popov}

For all angry people " statements, I don't want read them all, because you
don't answering my questions , you changing my words and statements, you make
your own conclusions for me, and many people like you doing that , who "fight"
for humanity in Ukraine, , for the true, for the Peace and Freedom same time
support Nazi. Nazi is Nazi , any country, I do not support any of them ! Time
will show the true, and if you want the War , your choice , you will get
lessons from the War you support, I am for Peace. No meter what I say, you will
be Angry, calling me bad names and changing my words... , put lies here

Which is proves : you don't want True , you are afraid the true. "Kill, die ,
and many many similar , these are your words , you lives with them; nonsense .
You need another 100 or more years to change, be better, you forget War 2,
short memory


\iusr{Yaroslav Zadorovskyy}
Seems that our North American troll here is out of arguments :)))

\iusr{Nikolai Popov}
Waist of time talking with Angry people from Ukraine , get lessons and Argumens from the War you created ; time will show the True .

\iusr{Yaroslav Zadorovskyy}
We gave you facts you called us angry - waist of time indeed...

\iusr{Inessa Windmill}

Popov, that's nice that you have learned English! I thought it's impossible for
a Russian! I hope you won't ask Putin to come to Canada to protect you? In
Canada many Ukrainian migrants! They can drink you blood or eat your children,
if you have any!

\iusr{Nikolai Popov}
Melnychuk, you are another one who changing my words and create the War ' ! I did not say anything about Mr. Putin . ... It's your mistake you are in Canada. I am for Peace in Canada. You are for the war, go back to Ukraine for the war ... May be jail to Stop you from violence ..?

\iusr{Nikolai Popov}
I m not sure if you are Canadian , or real Ukranian ,,,
NAZI ? Don't know.. for Migrant like you no place in peaceful Canada ,.: we Canadians do NOT need war hear ., go back

\iusr{Nikolai Popov}
If you want " eat your children" , eat your "shit", you have too much ...

\iusr{Лиза Пикерсгиль}
Николай Попов, глубокое уважение Вам от меня!!! И привет от адекватных людей из Украины! Вы-молодец!!!

\iusr{Nikolai Popov}
Spasibo, Liza

\iusr{Roman Makuch}
Nikolai, your another titushko. Don't forget to make sure that they pay you

\iusr{Yuriy Gruzglin}
This is Lugansk, several days ago.

\href{http://youtu.be/I0EX_uVUf1U}{%
драка двух посетительниц кафе "Калинка" в Луганске (18+), Frozen, youtube, 30.12.2014%
}

В Луганске возле кафе "Калинка" две девушки устроили пьяную драку. Конфликт
начался в самом кафе, но драться там девушки не стали.  За этой потасовкой
наблюдала толпа людей: посетители кафе, проходящие люди, зеваки. Наряд
патрульно-постовой службы, который видел происходящее,  не спешил разнимать
девушек а просто наблюдал за происходящим.

Разнять девушек не пришло в голову никому. Более того, нетрезвых дамочек
подстрекали к продолжению разборок, выкрикивая: "Бей кулаками" и "Пусть сдохнут
обе", снимали всё на видео и выложили в интернет. А когда одна из девушек
неожиданно сняла юбку во время потасовки, восторгу зрителей не было предела.

\url{http://lugradar.net/2013/11/6993}

Материал взят отсюда: \url{https://frankensstein.livejournal.com/461289.html}

\iusr{Aga Zaród}
truth?? 

\href{https://www.facebook.com/video.php?v=754199491361130}{facebook video}


\end{itemize} % }

\iusr{Johnny Benson}

I don't subscribe to this idea that Yanukovych was this super-corrupt demon. He
didn't bomb countries into the stone age to support domestic commercial
factions in the energy, arms and construction industries unlike certain states
that like to hector states on matters of "corruption". No halos for Yanu of
course but the idea that he was someway uniquely "corrupt" is hysterical.
Yanukovych's actual crime is that he actually guarded Ukrainian sovereignty and
he didn't turn his country over to Western loan sharks - so for the West, he
had to go.

\begin{itemize} % {
\iusr{Алекс Каплан}

Obviously you didn't do any kind of research on him or his family. Shortly
after he became president, his sons became basically the wealthiest people in
the country. The Corruption index rated Ukraine in the top 3 most corrupt
countries on earth in 2012. All you have to do is look at hos actions,and what
he did since the overthrow; he ran to his puppet master in Moscow; that is all
he was the entire time... Putin's Puppet. Hell he was even a convicted criminal
and spent time in jail (for theft). I dont think you quite understand what
happened. He failed to sign the EU economic deal instead signing the Russian
trade federation deal, pissing off pretty much everyone in western and central
Ukraine; the only people who stood to profit were the far east Ukrainians and
people from his home city in Donetsk who would profit from coal sales and
industry ties. He was not a Demon, he was and is however, super corrupt, among
the most in the world. He was not "guarding Ukrainian sovereignty"- that is a
joke, he was ruling Ukraine as a proxy for Putin who was pretending it was a
Faux soviet Union nation state.

\iusr{Johnny Benson}

I don't care about "corruption indexes", tables, breakdown charts, or any of
the other jibberish interference mass produced by globalist organs in order to
maul a man who's real crime in the West's eyes was to protect Ukrainian
sovereignty. Real corruption is represented by the Atlantic bloc who have set
the world on fire in pursuit of petty commercial goals. Yanukovych is a
benevolent character in comparison.

\iusr{Andre Maurer}

What John is saying, I think, is that yes he was corrupt, but he is far from
the only corrupt politician. We can cite examples of Dick Cheney's Haliburton
getting billions of dollars in contracts from the Iraqi war which Cheney
himself started.

\iusr{Johnny Benson}

Technocratic corruption indexes doesn't detect the war profiteering Bush
family, it doesn't detect the billionaire Queen of Britain awarding her
offspring enormous wealth from state coffers on terms of inheritance, it
doesn't detect the corruption of malicious vampires setting the world on fire
putting millions into misery. Technocratic indexes doesn't detect that kind of
extreme moral corruption at all. I don't like either - but old style corruption
seems like a blessing compared to rioting planetary pyromaniacs like goggle
eyed Clintoon and John McCrazy.

\iusr{Dianne Witiuk}
Yanukovych is a potato farmer who sold his soul to the devil incarnate.

\iusr{Myron Pyzyk}

Everybody, please. Ukraine doesn't care if Yanuk. wins the boobie prize as the
most corrupt President. You must be sitting on a comfortable couch outside of
Ukraine to make that opinion as well as not having any family there. Yanuk was
a corrupt President and UKRAINIANS in Ukraine were fed up. Really fed up. The
previous generation was still Soviet-trained to shut the hell up and take it on
the chin or even die in a gulag. Stoic people but sheep. The new generation of
Ukrainian kids were born in Ukraine or, at the very least, grew up in a very
young nation with a long history called Ukraine. Proud they didn't take any
more BS. Poroshenko et al better move fast otherwise, Deja vu.

\iusr{Aleks Djee}

@Myron Pyzyk: "Fed up" yes, they were for sure. But that's why the new regime
prohibited Russian language as second state language? Or thats why all Russian
channels were closed in Ukraine right after Poroshenko elections? That's why
they bombed Donbass? Now about "previous generation" and "long history of
Ukraine". Ukraine in Russian means "U Kraya" and is spelled like "At The
Edge/Periphery". It's former Russian Empire periphery territory and Kiev city
is the origin of Russian Orthodox Cristian Church and maybe the whole Russian
and Slavonic history.... Ukraine was 500 years the Russian Empire land and
Ukrainians and Russians were one united brother folk. Ukraine ( Zaporoskaya
Sech) asked Russian Empire to protect its people from polish "panov" who gang
banged them back in centuries... So trying to deprive Ukraine from Russia and
divide one folk into two and more of this to flame the hostage between them
(saying like old soviet generation and new generation or long history of
Ukraine without Russia) is substituting the history of our two nations.... It's
being done by current Poroshenko regime as it plays the game in which US sets
the rules. Russia and Mr Putin only defends Russian interest.

\iusr{Bohdan Pechenyak}

"Russian interest" is stone-age imperialism. It's aggressive, jingoist,
KGB-inspired, oil-drenched madness. Those are "Russian interests".

You've got to be pretty cynical and ignorant to choose such a formulation.


\iusr{Aleks Djee}
Богдан - ты мудак полный, да простит меня Господи.

\iusr{Aleks Djee}

Russian interest is the next: to protect Russians in near located countries,
not to allow the NATO to expand near Russian borders, make transit of gas
smooth, predictable, safe, transparent and yes controlled, to have friendly and
close and trustworthy relations with neighbors and brother nations like
Ukrainians and Belorussians who mostly speak the same and one Russian language
and have more than 500 years of one history....

\iusr{Aleks Djee}
Ah, Bohgan Pechenyak is from Lvov.... That explains everything....

\iusr{Eric Kraus}

Ukraine had a series of extraordinarily corrupt governments. Both pro-Western
and pro-Russian. Timoshenko could go mile-per-mile against Yanukovich any day -
the Gas Princesse become a billionaire stealing gas, and is widely believed to
have eliminated numerous competitors with extreme prejudice. None of this
justifies a foreign sponsored coup d'etat which has torn the country to shreds.

\iusr{Johnny Benson}

Yanukovich's transgressions aren't a big deal when confronted with the
collection of toads, gargoyles, "foreign citizens", robber-barons, vampires
that are happy to launch airstrikes against civilian districts and have
pampered vampire-clowns such as "Joe Biden"and John McCrazy cheering them on.
We need to get our head around this idea. Raging from dawn to dusk against
Yanukovich like he's lucifer 2.0 whilst shrugging our shoulders at the jackals
laying waste to one half of Ukraine and robbin' the rest is like ragin' against
a prolific shoplifter whilst apologisin' for the local serial killer./arsonist
. And notwithstanding the moral fibre of yesterday's man Yanukovich, you Kiev
people are being played by the toads in charge of Kiev TODAY. That is beyond
dispute.


\iusr{Sherri Ingrey}

how dare anyone in Murica Inc LLP dare accuse leaders of corruption when almost
every single politico there is taking graft, bribes and payola from the day
they start to think about entering politics!!!! Not everyone is as dumb as
Muricans who think by calling it lobbying, contributions and appointments, it
is not corruption.

\end{itemize} % }

\iusr{Theo Botoulas}

Your analysis was 100\% correct. Western politicians of today are ignorant of
both history and religion and their effect on modern societies. To understand
the action of President Putin in Crimea, all one has to do is read Chapter 1 of
Orlando Figes book, Crimea.


\iusr{Gunslinger}

"It's easier to fool people than to convince them that they have been fooled."
Mark Twain and U.S. government know this very well. Don't stop.

\begin{itemize} % {
\iusr{Viktoria Dmytrivna}
Russian government knows that too and enjooooys fooling everyone around.

\iusr{Ksenia Silvester}
Thank you

\iusr{Bohdan Pechenyak}

Yes, throwing a quote around clears everything up, doesn't it? Oh, no, wait, it
doesn't AT ALL. You are the one who's a fool here, failing to see the
manipulation wrought by state-sponsored Russian propaganda. Do you watch
"Russia Today"?


\iusr{Helen Maciuk}
There are videos taken directly form the scene that were available on the day of, not orchestrated...over 100 protesters killed, 8 policemen; who was doing the killings \& who was protecting themeselfs... but u believe what u wanna believe...

\iusr{Gunslinger}
To clarify, yes the Russian government is guilty of this too.
\end{itemize} % }

\iusr{Steve Pacholka}
Well said!
Happy New Year Mr. Stone.

\begin{itemize} % {
\iusr{Serge Sirota}
What is «well», pig?

\iusr{Zbigniew Dąbrowski}
I wish Russia in New Year Democracy Freedom and Truth. It's great country and need this value to be a world good leader

\iusr{Igor Nakonechnyy}
Fuck Russia and fuck idiots who love Russia.

\iusr{Igor Nakonechnyy}
\textbf{Zbigniew Dąbrowski}, jak bym byl polakiem, to bylo by mi wstyd pisac takie glupoty.

\iusr{Nikolai Popov}
To Igor ; go to school and study proper English or just f..k yourself...

\iusr{Marusia Stashynsky}
Get over your propoganda info and paranoia!
CIA? Really? What else the world is a triangle?
Do your research people! Wake up!!!!

\iusr{Ralan Kuliev}

\ifcmt
  ig https://scontent-frt3-1.xx.fbcdn.net/v/t1.18169-9/10906190_840503886010884_8281295961053249653_n.jpg?_nc_cat=108&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=WeLmQe20DlIAX-6tgkO&_nc_ht=scontent-frt3-1.xx&oh=458779ffe7d61d6bafaedbe93ac18482&oe=61CB9601
  @width 0.4
\fi

\end{itemize} % }

\iusr{Lydia Hluszczyk Singura}

Again, Mr. Stone, I suggest you get the TRUTH from a UKRAINIAN professor at
Harvard who knows the true history not from a gangster!! Research Yanukovych's
past!! It is way easy to put a spin on even history these days!!! Hollywood
does it magnificently! Russia has used Ukraine, raped her of her treasures, and
starved her people in the famine of 1913. Movies and documentaries have been
made about the Jewish Holocaust, but why not educate about the Ukrainian
Holocaust and get the truth out about that? Ukrainian history has been trampled
on and distorted by Russia for generations. They even took credit for and
celebrated 1,000 years of Christianity, when in fact it was Ukraine who
accepted Christianity and disseminated to Russian and other countries and that
is just the tip of misinformation. Yanukovych is NOT a resource for ANYTHING!!
He is a Russian puppet!

\begin{itemize} % {
\iusr{Kirill Dky}

Are u out of your mind? Ukraine didn't even exists 2000 years ago. Not did
Russia! It was the Russian people (and modern Ukrainians where part of that),
who accepted Christianity! Unbelievable what nonsense u are saying

\iusr{Vincenzo Lachimera}

Ukraine is the motherland of all Russia. From Kaliningrad to Kamchatka
Ukrainian surnames populate every city and village. Kiev is the mother of all
Russian cities and the Kievan RUS are the mother of all Russian people.
Ukrainians are Russians, the ones promoting the idea that they are a separate
people are from the west of modern Ukraine which was Poland and Lithuania
formerly. There was no famine in 1913, there was famine in 1931-32 and millions
died all across Russia from this famine. There were many reasons for the high
death toll, partly because Stalin had murdered all the best farm managers as
Kulaki, my German Mennonite ancestors among them, and to a lesser degree the
indifference of bureaucrats in Moscow and Kiev. Millions also died on the
Indian sub-continent fromthe same famine. Ukrainian history is Russian history,
the eastward march of Muscovy was a continuation of the north eastward march of
Kievan Rus! I would not be so impressed with Harvard professors, graduate
students at Harvard are no better at geography than the set decorators that
work at CNN! Lastly, Ukraine is a Russian word, it means borderland, borderland
of the Kievan Rus, who dwell in the modern great nation of Russia that all the
ancestors of the true Ukrainian people pioneered and created!!!

\iusr{Lisa Marie White}

fortruss.blogspot.com link

\iusr{Andrey Stebelskiy}

The problem is in case, that many of you can't truly catch the definition
between "russians" which are dwelling in Russia now or Grand Duchy of Moscow in
the past (the population of 146 millions) and "rus'ki" or "rusin" or "rusnak"
which are dwelling on theirs roots own lands that were compound in one Kievan
Rus' empire (included: Ukraine 46 mln, Belarus = 9.5 mln and just a small part
of nowadays Russia territory). Its a big trick of history that russians use all
the time, just replacing the definitions.

\iusr{Robert De Cherry}

I see this is going to be a complex untying of a very old and very complicated
knot. This will take time Vincenzo. Please add references to some of your
facts, links or references to maps and books so we can improve our knowledge of
this prior geography. Much appreciated, thank you.

\iusr{Tanya Lydia}

Wow, many Putin Puppets can't handle the truth! Disgusting propogand show! You
are all as twisted as Putin! Stone is a moron, and Yanukovich a thug, theif and
criminal!


\end{itemize} % }

\iusr{Euan MacDonald}

By parroting the absurd Russian propaganda nonsense of a "fascist/CIA takeover"
in Ukraine, you make yourself look foolish, ill-informed and closed-minded. Are
you going to interview any of the Ukrainian politicians you pass off as CIA
puppets? As a person who has a disproportionate measure of influence, you
should at least take your responsibility as a film-maker seriously, and not
spread falsehoods.

\iusr{Hurd Harley}

you are full of shit. i was there. I saw everything. I will never believe
another word you say. W hich of the world's greatest liars will you interview
next, Putler or Liarov?


\iusr{Rafał Chwiliński}

I think this topic is far more complicated. It is not just about Russians and
US, Ukrainians and US, etc. There are Poles and Jews here, there are many
problems that came for centuries. It is not that easy.

Yanikovich has had stood up against his own people. As I well remember he ran away!

I always admired your movies but now I think you start playing with ptopaganda
- not only Russian's but propaganda in their hands is the devil. You will see
later on how you have been used.


\iusr{Sveta Bilan}

Thank you Mr Stone for spotlighting Ukraine by your publications! Your work is
greatly appreciated by all seeking the truth. Moving toward prosperous tomorrow
is not possible without revealing faces of the past. Your involvement is truly
significant.

\iusr{Мартин Паркер}

Choosing the Rus Govt side of the debate is not the bigger picture. It's small
minded and ignorant. Go to Chechnya and Transnistria and see how the Russian
Government handles dissent in autonomous regions. But you can't; your cameras
are not allowed there. Thousands have died in Ukraine for nothing. Don't be on
the wrong side of history. Be truly independent.

\begin{itemize} % {
\iusr{Мартин Паркер}

Impossible. Russian government doesn't allow freedom of travel to such regions.
Only uberpatriots are allowed in. Tour operators are not running package tours
as far as I know either. Are you headed there for New Years? If so, С Новым
Годом Вас!

\iusr{Vladan Vraštanović}
Offcorse that he was  @igg{fbicon.smile}  He just turn on CNN and he travel the world  @igg{fbicon.smile} 

\iusr{Мартин Паркер}
I get all my news from Oliver Stone. He's a great expert on life in Russia. Offcourse, indeed.

\iusr{Vincenzo Lachimera}

Thousands of people have died in Ukraine because USA will not accept the
federalization of the different regions of Ukraine. The people who were
massacred in Odessa were promoting a petition to hold a plebiscite for
federalization. For exercising a basic democratic activity they were murdered,
and the present President has declared this a good and rightful act of
violence. Children were killed that day including a pregnant women! The people
of Chechnya are very happy not being ruled by Islamist warlords. They are
delighted to be enjoying a level of prosperity and security of person they have
never known in their history under the government of Рамзан Кадыров!
Transnistrian referendum results show an overwhelming indication the people
want nothing to do with Moldovan corruption or the Ukrainian fiasco. Vladan hit
the nail on the head, your purulent response confirms that!

\iusr{Александр Янчук}

Martin, this is bullshit! I can buy you a ticket. Would you like to go? And
after that we'll speak.

\iusr{Мартин Паркер}

Please buy me a ticket. I'm waiting urgently. BTW, how many of your family and
friends have been there? Exactly. Please show me all the Aeroflot flights to
Grozny.

\end{itemize} % }

\iusr{Alberto Dietz}
Spot on, Oliver!! Happy New Year!!

\iusr{Richard Carpenter}
Jake love Mr Stone

\iusr{Serhiy Uryn}
Mr.Stone's "bigger picture" is, actually Putin's picture. Nothing original

\iusr{Johan de Broyer}
War crimes committed by Dictator and War Criminal Poroshenko, sponsored by NATO, EU and US.

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10881515_10152531993853045_216383801334520088_n.jpg?_nc_cat=111&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=fLW8F_jxg8UAX_wGkQi&_nc_ht=scontent-frx5-1.xx&oh=8d5a1827df8ca0f10dfaf14a2791b94c&oe=61CCE847
  @width 0.5
\fi

\begin{itemize} % {
\iusr{Dmytro Khavro}
It´s a fucking democracy!

\iusr{Александр Янчук}
And NATO is going to arm Kiev again.... Looks we're falling into next war. STOP IT!!!!
\end{itemize} % }

\iusr{Юрий Сорока}

Why some people who live in the West, protected by the law and democracy, go
and find some perverts like Hitler, Putin, Chaushesku, Yanukovych, etc. and
then come back home and whine about how great leaders those are and how bad
America is. You sucker go live in the GULAG or \#Russia-occupied Donbass, where
a bunch of \#Kremlin backed thugs will torture and rape you before they choke
you with your own intestines, and then they will brag about shooting a civilian
airliner calling the passengers "spies" \#mh17

\iusr{Yarema Bachynsky}

Dude, you are totally f*cked up! You don't know your history and you are just
another Putler Propagandist. And an unprofessional moron to boot.

\iusr{Tom Lasica}

All security agencies do shit FSB Kgb FBI but either you have a brief or are so
incredibly naive to think that in Kyiv Moscows backyard it wasn't the Kgb who
weren't playing every vile trick in the book to force Yanukovych to play ball
the way Putin wanted

\iusr{Joe Mestas}

Oliver thank you for speaking up. It was the same situation in South Ossetia.
The Bush Regime goaded Saakashvili into attacking South Ossetia. Keep looking,
keep talking, the people in the US and the West need to learn the truth.

\iusr{Scott Newton}

I'm completely intrigued by the whole situation, especially because I'm at such
a distance, being in Adelaide, South Australia Where the only mainstream news
is completely heavily western influenced, to have alternative prospective is
better than none at all !!!

Keep going O.Stone, don't stop, without people like you - our global
prospective is extremely ugly

\iusr{Max Smetannikov}

You don't have to apologize... It is what it is. It's important that the truth
be told. Thank you, God bless, and happy new year.

\iusr{David A. Cates}

Thank you Mr. Stone for being a beacon of light and truth in a country without
a real media or moral compass to speak of.

\iusr{Valentine Azbelle}

One more important point. I think you're confusing a nationalist with a Nazi. A
nationalist does not hate other nations. A nationalist simply loves his own.
But when another (neighboring) nation does everything possible to erase any
traces of his/her cultural and linguistic national identity in order to
subjugate and ultimately absorb his/her people, what's a nationalist to do but
fight?

But speaking specifically about the Nachtigall unit the accusations of the
atrocities have since been proven FALSE by the international commission at The
Hague. The conclusion reads: "After four months of inquiries and the evaluation
of 232 statements by witnesses from all circles involved, it can be established
that the accusations against the Battalion Nachtigall and against the then
Lieutenant and currently Federal Minister Oberländer have no foundation in
fact". It was just a Soviet attempt to discredit the nationalist movement in
Ukraine as well as the German government in the late 50's.

\begin{itemize} % {
\iusr{Valentine Azbelle}

Wrestler Joe: Of course we could have a debate about the intricacies of the
Polish-Ukrainian relations that led to the tragedy, and we could discuss the
atrocities committed by the Red Army (and in particular the atrocities the
Soviet NKVD committed against the poles AND the Ukrainians), as well as look
into the number of the torchlit marches participants (which is quite small), or
the nature of the collaboration of their hero with the Nazis, or even abstract
concepts like symbolism vs. a real person... But sorry, I don't see a point of
having a debate with someone expressing an outrage over terrorizing civilians
and POW's while simultaneously being a Ramzan Kadyrov fan.


\iusr{Valentine Azbelle}
If by "he" you mean Kadyrov, he's a murderer and a war criminal.

\iusr{Valentine Azbelle}

I don't know who you mean by "you guys" - I don't scream anything. And yes,
we're all human, and some of us humans are assholes - like your hero Kadyrov
for example. As for the tired and stupid Black Sea joke, which you post under
like every comment, what the fuck does it have to do with what's being
discussed?

\iusr{Valentine Azbelle}
Oh please... Your boys? 

\href{https://www.youtube.com/watch?v=klkyfbnS0TA}{%
Russian nationalists attack immigrants on St Petersburg metro - Truthloader, Point, youtube, 06.11.2013%
}

\iusr{Valentine Azbelle}

\href{https://www.youtube.com/watch?v=zOZXxujwBic}{%
youtube video%
}

\iusr{Valentine Azbelle}

I could post a hundred videos of Russian idiots with Nazi insignia making
ridiculous claims as well as being violent towards other ethnicities.

Your words were "Kadyrov... he's a real man". Sounds like a high praise to me
(unless you were trying to convince me that he indeed existed and existed as a
man, and was in fact not a woman pretending to be a man, but a real man). Also
Kadyrov is among your FB likes.

I don't know who decided that Russians aren't Slavs. But I do know that "your
boys" (whatever that means) decided that Ukrainians aren't even a nation. I'm
all about all of humanity but if one particular part of humanity attacks
another, it is absolutely the right of the attacked humanity to tell the
attacker to fuck off. And if that doesn't work, kick the attacker's ass.

Anyway, I"m going to ignore your comments in this thread after this. I have
more productive ways to spend my time. Cheers.

\end{itemize} % }

\iusr{Mark Kirk}
Keep up the good work, thanks for trying to bring the truth to light.

\iusr{Patricia Fornera}
The truth always hurt: happy New Year M. Stone

\iusr{Dmytro Bazulin}
Mr. Stone. The rumor has it the CIA was behind crucifixion of JS. Totally worth checking this out.

\iusr{Myron Gudz}

But what has Russia done to Ukrainians over the centuries, repress their
language, forced labor camps, famines, etc.? Every country has its blemishes
but Stone can kiss my fucking ass!

\begin{itemize} % {
\iusr{Yulia Boltach}
Also gave them over 50\% of the land they call theirs today.. liberated them from the nazis, just to name a few

\iusr{Myron Gudz}

They got land only to be forced to turn over the proceeds and cause the
starvation of over 6 million people in the 1930s. Liberated from the Nazis?
Stalin caused more deaths than did Hitler.

\end{itemize} % }

\iusr{Christian Serra}

\ifcmt
  ig https://scontent-frt3-2.xx.fbcdn.net/v/t1.18169-9/10390225_10153320555111542_1681426607089789267_n.jpg?_nc_cat=103&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=48qAKQ7trLYAX-2nTL-&_nc_ht=scontent-frt3-2.xx&oh=985d56893b17a9b5c16f445711008fbf&oe=61CCC887
  @width 0.4
\fi

\iusr{Gary Yuri Tabach}

Mr Stone. I am the first soviet born Jew who became a commissioned officer in
the U. S. armed forces and after 36 years of service I rose to a senior rank.
Some of my duties included Russia, Ukraine, Poland, Georgia and Kazakhstan. I
was in Moscow on 3 Oct 93. I was in Abkhazia in 97-98. I served 3 differed
tours in Russia as a US and NATO rep. I was in Odessa on 2 May 14 and witnessed
the criminal acts conducted there by the Russian thugs and many more that are
too long to list. Putin and Yanukovich must face international court marshal
for crimes against humanity. Help to bring their crimes to light. I am no fan
of intel community, but 40 years ago Americans saved my life and lives of my
loved ones. As an American I felt I had to do the same for others. Ukrainian
people need our help to rid this world of a modern day hitler. Do not dishonor
and discredit us with your film.

\iusr{Olga Vasko}

You name it interference, Mr. Stone, I name it support. You are asking why the
death of policemen still not invastigated. I'm asking you why the death of over
hundred young anarmed man shot on Maidan not invastigated either. Ukrainians
are looking out for western support, but not for russian man and weapons in
Donbas.

\iusr{Ярослав Иванов}
\textbf{Oliver Stone} Спасибо за правду.

\iusr{Carol Green}

Thank you Oliver Stone for speaking truth. I've followed this story closely
from the original unrest in Kyiv and there's never been any doubt the U.S. has
been behind the coup that has caused the deaths of over 4,000 innocent
Ukrainians.

Historically, since the breakup of the Soviet Union in the late 1980s, Crimea
has NEVER wanted to be a part of Ukraine... EVER... and in every election they
chose Crimean leaders who would distance them from Ukraine.

• Like it or not, the majority of Crimeans never wanted any relationship with
Ukraine whatsoever. The history proves this.

• Like it or not, the majority of Crimeans wanted closer relations with Russia
and in 1995 voted for a president whose platform was to have Crimea join the
Russian Federation. The history proves this.

The Historical Record shows that Crimeans have overwhelmingly objected to the
Kiev appointed Executive Branch that has been forced upon them for over two
decades.

2,000,000 citizens in Crimea

1995: 73\% of Crimeans voted for pro-Russian president whose platform in the
Crimean elections was to join Russia.

Say 100\% of people voted.

73\% of 2000000 == 1,460,000 people voted for joining Russia.

2014: 93\% voted to secede and join Russia.

And this is with 83\% of the Crimean people voting.

83\% of 2,000,000 == 1,660,000 people voted

93\% of 1,660,000 == 1,543,800 people voted for joining Russia

1,543,800 – 1,460,000 == 83,800 changed their minds?

Percent of total population that changed their minds: 83,800 / 2,000,000 == .04\%

Here's more Crimean voting results since the dissolution of the Soviet Union
that shows the tug of war between the people of Crimea who desperately wanted
independence from Ukraine and overwhelmingly voted for that independence
throughout the years and the Ukrainian central government :

\href{https://www.lewrockwell.com/lrc-blog/status-of-crimea-under-existing-constitution-of-ukraine/}{%
Status of Crimea Under Existing Constitution of Ukraine, Michael S. Rozeff, lewrockwell.com, 07.03.2014%
}

\iusr{Oksamyt Tweet}

Mr. Stone "do you want make the movie about Ukraine? You already made it. Your
film " Salvador "- it's a true story about Ukraine." Vitaliy Portnikov.


\iusr{Antonio Guzman-Avalos}

It's seems that most of the persons who criticize the research of Mr Stones get
their information just from TV and manipulated media. It doesn't surprise me
how small and biased view of the reality they have.  @igg{fbicon.face.confused} 


\iusr{Maurizio Morris Aschero}

Still, you made Yanukovich look like a victim. Before airing the interview, you
should have spoken to those who fought in Maidan to send him away, you should
have studied the extent of corruption, violence and misery that Yanukovich (and
his predecessors) gifted to the country. Then with the two different points of
view, you'd look fairer and balanced. Yanukovich is the most hideous and hated
person in the country, with his golden bread and toilets, and with the 27 bln
USD stolen to the country. Why you didn't ask him about that? Why you spoke to
him like to a person? Have you studied his history before? Have you seen the
images of the guys shot in the head by russian snipers? There are pictures,
names, facts. Yes,USA was obviously involved too, you always are,
unfortunately, but it doesn't give you the right to justify that criminal.


\iusr{Iryna Tenitska Singh}

The root of legends about hatred of western Ukrainan to Russians such as
"москалі на ножі" etc lies in time before WWII when USSR annexed part of Poland
which became western Ukraine. After coming to that part of land KGB people
killed thousands of native citizens. Do you really think it's not enough reason
for hatred.

But it has nothing to do with modern times, lots of Russians are in western
Ukraine becoz of soviet policy of assimilation population. Those Russians are
living there in peace and happiness. Nobody kills or harms them.

\begin{itemize} % {
\iusr{Andrei Kostromin}
Слава украине, дегенератам слава!
\end{itemize} % }

\iusr{Iryna Tenitska Singh}

I don't have that much information about role of USA in Ukrainian Maydan. I
know that people from all our the country was going there by own will. And
those who couldn't go to kiev were going to maydans in their own cities. It was
great self organisation. Same as people are showing now by creating the biggest
volunteers movement in Ukraine.

\iusr{Aleksey Shulepoff}

Respect to Mr. Stone for standing up for his beliefs

\iusr{Roman Pereyaslavsky}

Dear Oliver Stone. Sometimes it's better to shut your mouth and look like an
idiot than opening it and removing any possible doubt...

\iusr{Nataliya Paschenko}

No country or person is perfect either Poroshenko or CIA or you, Mr. Oliver
Stone yourself! All assessments should be done on relative scale: CIA
supposedly supported Ukrainian Nationalist organizations to damage Stalin's
regime which killed millions of Soviet people and blackmailed entire world with
nuclear bomb! So what organization is worse, Mr.Stone?

\iusr{Nicholas Koshiw}

Perhaps Mr Stone can pull a Depardieu and become a Russian citizen as he's
clearly drinking Putin's koolaid. PS - Wall Street: Money Never Sleeps was
terrible.

\iusr{Georgiy Levchuk}

The only third party involvement in Ukraine is Russia installing a puppet
president Yanukovich, then sending in its FSB operatives to dismantle Ukrainian
military and internal intelligence from within, then sending its operatives to
kill people at Maidan to create chaos, then sending green men to take over
Crimea, then sending its operatives to tske down SBU and police headquarters in
Donetsk, Luhansk, etc., then installing puppet "authorities" there (all Russian
citizens!), then sending tanks and heavy military to kill Ukrainian soldiers,
and shooting down civilian airliner in the process, then waging full scale
military invasion when Putin realized Ukrainian army was about to end this
Russia-constructed conflict. And you are blaming Nuland and USAID and National
Endowment for Democracy??? You totally lost your mind, director Stone

\begin{itemize} % {
\iusr{Rob Decoup}
He is a director of stupidity. If i ever see him in LA i will smack his ugly face!
\end{itemize} % }

\iusr{Qris Ebeatu}

Sorry state of a man who lost touch with reality, taking money from putin and
yanukovich to post nonsense makes you look like an old loser.


\iusr{Anatoli Gres}

Hi, Just have read your very poor excuse. To write on political matters is a very
responsible thing. You should be aware of many facts from both sides at least.
The texts shows that you have very poor knowledges in Ukrainian history. So your
judgements insults majority of Ukrainians dependless of their
language (Ukrainian, Russian or else). In Ukraine we always call all things
directly vely seldom using hints. So in my personal view (I do hope that it is
supported by many Ukrainians) you are just cynical American bastard trying to
earn money on Russian-Ukrainian conflict (actually a bloody war) supporting
putin's propaganda machine. Hoping that you will understand it.

\iusr{Ruslan Petrychka}

I wish you would interview Yanukovych when he is in jail. Now you just helping
a thief and a murderer.... please do your next story on how Russian secret
police had infiltrated Ukrainian government and army, undermining Ukraine from
within. Investigate Putin, don't help dictators.

\iusr{Lily Goncharova-Maher}
Thank God, for honest and sensible men -like Mr Stone.

\iusr{Sam Smith}
Mr Stone thank you!

\iusr{Myron Gudz}

Perhaps if you had studied Ukrainian history you might understand that after
over 3 centuries of repression, Ukrainians might finally want a country of
their own, without Russian interference. This situation has finally opened the
eyes of Ukrainians to what the Russian government actually has in mind. Putin
actually told Bush that Ukraine is a fake nationality. We have a different
language with its own version of the Cyrillic alphabet. Ukraine is older than
Russia and traded with European nations before Russia (Muscovy) ever existed.

\begin{itemize} % {
\iusr{Steven Trop}

Then why didn't Ukraine's just wait 2 months for elections in May 2014. Russia
could do nothing had the transfer of power had been legitimate. That it wasn't
wasn't Russia's fault. Hate to break it to you, democracy is also waiting till
the next election

\iusr{Myron Gudz}

The people didn't believe the elections would be fair and having been out there
in the Maidan for 2 months protesting peacefully with no results before being
set upon by snipers and police. Russian subversion didn't start and didn't stop
with the Soviet Union.

\iusr{Marijka Stadnyk}

Yanukovich was abandoned, for dead, by his own party and closest allies - even
before he was ousted.

\href{https://www.nytimes.com/2015/01/04/world/europe/ukraine-leader-was-defeated-even-before-he-was-ousted.html}{%
Ukraine Leader Was Defeated Even Before He Was Ousted, nytimes, 04.01.2015%
}

\iusr{Myron Gudz}
They came to their senses. Why should he be bitter? He has billions overseas.


\end{itemize} % }

\iusr{Carlos Loureiro}

Thank you very much Mr. Oliver Stone for helping us to have an independent
vision about all the situation in Ukraïn.


\iusr{Ola Sturik}

REMOVED? Check your facts Mr. Stone. Yanukovich packed his bags and fled along
with the billions of dollars he stole from the Ukrainian people. You have been
doing a wonderful job discrediting yourself over the last several years. I
predict that joining Putin's propaganda machine will be your greatest downfall.
Shameful!


\iusr{Сергій Гриценко}

Mr. Stone I have only one question: When putin's lie will totaly destroyed, you
will go to International Court of Justice to pay for you personal lie or you
will hide from justice like meny nazi do after the World War in 1945 ?

\begin{itemize} % {
\iusr{Александр Янчук}
Real nazi were hidden in Ukraine as appears from facts. First Court should call Turchinov, Yatsenuk and Poroshenko.

\iusr{Сергій Гриценко}

Real nazi are not hide in Kremlin. They did meny of things like Hitler and
Goebbels did 75 years ago. In propaganda Kremlin elders even exceeded their
predecessors. And it is very big misfortune for Russia because russian citizens
will pay for what their "elite" did already.

\end{itemize} % }

\iusr{Lyudmyla Yankina}

I am sorry dear Oliver, but you are even do not emagine how much you have wrong
point of view. Ukraine is the country, which was suffer from yanukovych and
kremlin many years. And after many millions people just do not want suffer any
more cause in the eng we have our dignity. So we stand off against corruption,
criminals in law and politics who do not know what is human rights. You are
seems like a smurt person but your realasing based on a pictures (?!) and nice
conversatind with kremlin person (?!) that's it? you didn't make any deep
analizing of the situation in general from the inside. You didn't spoke with
any victim or participant of the revolution or war. 

Your point of view is not objective and not deep. Should I ask you how much
cremlin pay for this? Should I asl will you have somw matelial advantages from
it? Because only like this I can understand why you did it. If you like to not
be ashamed in the books of the history on the future - speak with us? with real
participants of the situation, that you name nazi. 

Don't be affraide, we will not drink your blood and kill you. In reality - we
are very peaceful people with high level of culture and dignity. 

We can tell you everything and it will be very big case for your movie because
we are many people and each have own reason to be a revolutioneer and stand off
against yanukovych-putin regime. Most of us very good educated people and we
are able to give you the base for objectivnes.  Speak with us - real people,
ask us, do not ashame yourselve. You will find all real unswers for all your
"picture" questions. 

We are not nazi! Ukrainian - it is a nation of dignity, not of violance! But
saddnly we should defend ourselves many years and exactly the last year from
the violance, propaganga and artifisual dirt - on what you base your point of
view about us. Very painfully mr. Stone. 

Do not turn history upside down just because you are not able to work well with
historical material, which is still in the making, exactly when millions of
participants of the history alive and many of them right now dying on the war
from russian weapon.

\begin{itemize} % {
\iusr{Linda Green}
\textbf{Lyudmila Yankina}, 

"Ukrainian - it is a nation of dignity, not of violence!" You can lie to
yourself as much as you like! What can you tell about the Odessa massacre? How
many people your "peaceful" Ukrainian army did kill in Donbas region?

Yanukovich was not an angel but at least he didn't kill and bomb innocent women
and children, unlike the war criminal and bloodthirsty oligarch– Poroshenko!

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10881515_10152531993853045_216383801334520088_n.jpg?_nc_cat=111&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=fLW8F_jxg8UAX_wGkQi&_nc_ht=scontent-frx5-1.xx&oh=8d5a1827df8ca0f10dfaf14a2791b94c&oe=61CCE847
  @width 0.4
\fi

\iusr{Linda Green}
\href{https://www.youtube.com/watch?v=B7TScRvpwqo}{%
youtube video%
}

\iusr{Andrea Bodrati}

@Linda Green : really ? Can you tell me who signed order n. 347 of 19 February
2014 that allowed the police to kill more than 100 young Ukrainian people ?


\end{itemize} % }

\iusr{Eric Eyutchae}
Awesome Oliver! I'm with you all the way! Anyone who dosent like the truth can
go and commit suicide for all I care. Well done!


\iusr{Rokas Sinkevičius}

Thank you for explaining pro-soviet version of history to us. In Lithuania you
will be remembered as one of Putin's bitches.

\begin{itemize} % {
\iusr{Александр Янчук}
Рокас, а ты откуда вообще взялся?)) Из какого туннеля?

\iusr{Rokas Sinkevičius}
CIA перебросила через границу.
\end{itemize} % }

\iusr{Елена Кайдалова}

Once you were Great director. Then you were so-so director. Now.. I do not even
know what to say. What hapenned to your talant? You, 've become communist and
hypocrit. Guess what, communists (KGB, NKVD) slaughtered my closest relatives
for no reasons. So I DO know who they are If you think that CIA is an evil -
fine (it is pretty close call) BUT It does not make FSB, KGB good guys. They
are not. They are Monsters. I wish You never ever knew what is that to be their
victims. It is awful to wish that even for such hypocritical person as You.


\iusr{Tatyana Burak}

Mr. Stone, I've always been a fan of your talent but now I am ashamed of you.
It's indecent to speak about things you have no idea about and claim things you
haven't witnessed. It's a shame to be a tool of Russian propaganda. People of
Ukraine overthrew Yanukovich because they were tired of his crimes. We will do
the same with the present President if he doesn't do what he should do for the
country. Some commenters praised your bravery. It's not brave to say something
you have no idea about, it's arrogant. I live in Donetsk region which produced
Yanukovich but I am for the new Ukraine and so are many people around. Stop
seeing the hand of CIA everywhere! What about the people who live here? Don't
they mean anything? Don't they have the right to choose how they want to live?

\begin{itemize} % {
\iusr{Steve Poe}

How about Ukraine joins the democratic world and removes corrupt politicians
with their votes not guns. If majority of Ukrainians were really against
Yanukovich they would have removed him at the early elections he agreed to. Was
all this bloodshed worth removing him 2 months before the election?

\iusr{Maximus Berezov}
Also, what 2nd flag is on SBU building in Kiev? :))
And why Ukrainian employees can't go on the 4th floor.

\iusr{Tatyana Burak}

There were a lot of falsifications at the previous elections. Why do you think
Yanukovich and his servants wouldn't do the same again? They have stolen enough
money to buy as many votes as they need.

\iusr{Vladimir Grigorev}
It was not possible to do without SIA

\iusr{Marijka Stadnyk}

Putin lovers, why all the concern about Ukraine's politicians. You best be
concerned with cleaning up your own backyard before casting aspersions on
others.

\href{https://www.nybooks.com/articles/2014/12/18/how-he-and-his-cronies-stole-russia/}{%
How He and His Cronies Stole Russia, Anne Applebaum, nybooks.com, 18.12.2014%
}

\end{itemize} % }

\iusr{Victor Salitrennik}

Please try to understand. This is not about who Yanukovych is/was. And not
about your right to your own opinion, however misguided it can be. It is about
your statements that make no sense and contradict the obvious facts. "Well
armed" neo-Nazy? Well armed with plywood shields, sticks and stun guns? They
ousted the president protected by many thousands of well trained and really
well armed men? Have you even bothered to check the basic facts, or is your
sense of "smell" is enough?

\iusr{Екатерина Гетьман}
Оливер, Вы смелый и сильный человек))) Счастья Вам, удачи и процветания в 2015 году! С Новым годом)))

\iusr{Mirjana Joksimovic}
Thank You !

\ifcmt
  ig https://scontent-frt3-2.xx.fbcdn.net/v/t1.18169-9/10400816_10152935030038334_7678284344633087254_n.jpg?_nc_cat=103&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=uIYvRG4Bf2kAX9Xo32-&_nc_ht=scontent-frt3-2.xx&oh=3bf158ec6de7497edd358cd8e4876b27&oe=61CCD813
  @width 0.4
\fi

\iusr{Yuriy One}

You can try and attach any conspiracy you "see" is connected to the events on
Maidan. The truth is much simpler - about 300 students started the protest due
to president's refusal to follow his promises to associate with EU. Those
students were dispersed and beaten. This brought outrage and thousands people
to the streets, they wanted this to be investigated and the guilty punished.
But the beatings persisted and even more police force arrived. This brought
even more people onto the streets, this time demanding president's resignation
due to him failing in his duties to the people - they simply had enough of this
BS. But wait, you see CIA in this. I bet all 300 students were paid off. I bet
the president was paid off by CIA too, he had to escalate the situation just
right and keep pushing for people to rise up. But there is more, there were
about 300 students protesting, right? It must mean that Sparta had its hand in
it too! Everybody knows Sparta fights in squads of 300. Yes, that must be it!
Good job.


\iusr{Mark A Wareham}
Well said Oliver.

\iusr{Clifton Ellis}

Great job Mr. Stone. Continue the good job in helping ordinary people
understand complex issues that are riddled and tainted with propaganda, smoke
screens and partial truths. We mere mortals who are at the mercy of the big
news corporations who massage the truth to suit their various political angles
need dissenting voices that challenge their narratives. Thanks for your efforts
and we are actually tuned in! Peace. Clifton


\iusr{Viktoria Dmytrivna}

I like the way american, polish, peruvian and other spanish language speakers
talk about Ukrainian history sitting on their sofas and blaming american
government. Bravo!

\begin{itemize} % {
\iusr{Norine Murrell}

Viktoria, they are most likely sitting in a basement in Moscow paid by Putler.
Many names appear made up, many of the comments are similar in content.

\end{itemize} % }

\iusr{Ewing Jesús Falla Arévalo}

To Oliver Stone ( Second letter )

Mr. Stone, please try to focus in that Ukrainians want to be the authors of
their own destiny.

You said: "The big picture is the US has never given up on using Ukraine as a
launching pad to the underbelly of the Soviet Union".

And what about the attitude of Soviet Union (now Russia) with Ukraine, do you
remember the Holodomor?, do you remember the russian scum that is killing and
destroying the lives of hundred of civilians in the East of Ukraine.?

Mr. Stone the big picture is: Ukraine had the president and government most
corrupt. And when Ukrainians wanted to change all that, the russians jumped
into the jugular.

Forget to the Ukrainians please, and let they find solutions his problems.

Maybe you can continue doing good movies, maybe about Maduro or Chavez or about
how venezuelans lost his rights and live under poverty thresholds.

For the moment people in Ukraine don't want to know about you.

Best regards!!

\begin{itemize} % {
\iusr{Lisa Marie White}

They're a US colony know so I hope they enjoy their "independence." East of
Ukraine in Holodomar, you say? Yes, because it was only Ukrainian speaking
Ukrainians who died in that famine? Forget the starvation deaths in Moscow, and
the 1 million who died during the same famine in Siberia. What about the Poles,
Germans, Roma, Tatar, and ethnic Russians who died as a result of that famine?
It was not a genocide against Ukrainians. It was the result of failed
collectivization programs put in place by Stalin. Way to deflect from Ukraine's
alliance with Hitler and their involvement in the Holocaust. Drinking that
Bandera kool-aid, are we? Chavez was a good leader and he stood up to the West,
too. The US overthrew him, demonized him, and his people rose up and put him
back into power. Yanukovych may have been corrupt, but they were going to have
elections to vote him out. Ukraine has been in charge of its destiny for 23
years, and what does it have to show for itself except bankruptcy and extremist
nationalism? Venezuela is rising out of the ashes of the US trying to control
and impoverish their nation. You don't speak for everyone who lives in Ukraine
or anywhere else. There are people there in the East now and they know who is
using illegal cluster bombs on them an they know it is Poroshenko. Here's a
picture of your friends, with their hero, the Nazi collaborator and war
criminal Bandera.

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10897963_10205581692762069_8737627965897263741_n.jpg?_nc_cat=100&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=svDaMRd5AS0AX9KLvKS&_nc_ht=scontent-frx5-1.xx&oh=437fab61b9e8f70b485d8ba957df9754&oe=61CE37F2
  @width 0.4
\fi

\iusr{Ewing Jesús Falla Arévalo}

Chavez good leader? Ok I am superman  @igg{fbicon.wink} 

By the way maybe do you need go and live in Venezuela and feel all misery that
venezuelans live.

It's easy talk from the comfort of your armchair. I have some friends in
Venezuela and the reality is more cruel than your news from TV.

Check your beliefs.!!

\iusr{Lisa Marie White}

fortruss.blogspot.com - youtube link

\iusr{Ewing Jesús Falla Arévalo}

One swallow doesn't make a summer. !!


\end{itemize} % }

\iusr{Lesya Shovkun}
*facepalm*

\iusr{Alex Goridko}

I hope your new friend Putler will apprecite this conspirological piece of
shit. How much did he pay you? Ukrainian blood is also on your hands now.

\begin{itemize} % {
\iusr{Robert Oleksik}
You are stupid ukrainian agent.
\end{itemize} % }

\iusr{William Danger Jumper}
Thank you Mr. Stone

\iusr{Michael Carrier}

This is simply untrue, and you've been taken in by Russian propganda. There was
no coup - all the elected representatives stayed in place, and just the
president ran away with trucks full of booty.

\iusr{Олександра Мельник}

How much Janukovich or Putin paid you for this "truth"? I saw Maidan, I was
there, I brought my money and money of my friends there just with one idea: "We
have to win, we will win!" We wanted, and we still want to live in the country
with real justice, without corruption. Our Konstitution says: "People are the
source of power", so we just helped it to work.

\iusr{Stanislav Rico}

Oliver, where have the Neo-Nazis diappeared? maybe you should apologize for it,
no? as you called me, my Jewish, Russian, Armenian, Ukrainian and other friends
who took part in the Ukrainian Revolution of Dignity. not due to some mythical
americans, but because it was their heart's will. usa might have supported us,
but definitely they didn't do the revolution, as our society was ready to get
rid of this criminal

\iusr{Keith Chawrun}

Your history sir, does not even touch the surface why Ukrainians don't want to
be part of Russia and under Russian control of any kind. 1000 years of history,
and cultural differences. Things are finally changing for good in Ukraine. The
people finally get the freedom they've always desired. And now you want to turn
it into something negative!! Shame on you!! Slava Ukraini and Herom Slava!!

\begin{itemize} % {
\iusr{Maximus Berezov}

Herojam sala. What 1000 year old history you talking about? The size of
Ukraine(before maidan) was based on addition of crimea (by hrushov in 1967) +
by sralin in 1947 + by lenin in 1922. Without these additions Ukraine whould be
10\% of what it is even now (without donbas and crimea) maybe ukranians are
dating back to dinosaurs?

\end{itemize} % }

\iusr{Chris Wynnyk Wilson}
I suppose you think Guevara was a hero!

\begin{itemize} % {
\iusr{Steven Trop}
You don't?
\end{itemize} % }

\iusr{Susan Lagg May}

Oliver, I watch your Showtime Networks series epidsodes 5-10 last night on the
5th of July. Brilliant - and certainly an eye opener for me. I have recommended
this my FB friends, and asked them to share the post and find a way - any way -
to watch. Most timely to catch it just before the 2016 election cycle gets in
full swing. Thank you!


\iusr{Rob J Jarva}

Totally agree... I lived half of my life in Canada and went to visit my friends
in the Western Ukraine back in February 2014 and witnessed the events.
Naturally I've been very well" prepped" by the Western media and sincerely
wanted to be with my friends during the time of the "revolution"... "Revolution
my a. s", were some of the responses! I stayed around , went to Kiev , took pics
and just could NOT believe what was happening and more importantly how the so
called "free and independent" were reporting on the events.. or rather not
reporting on many of them. Yours was one of the few voices of wisdom that are
barely coming through! Kudos!


\iusr{Kobus Johannes}

Oliver Stone, you are 100\% correct. I’ve been to Ukraine and met people who
accepted Western bribes as protestors for Maiden, another false color
revolution serving Western interests only. It must be known that the vast
majority of Donbas people (E. Ukrainians) are local Russian speaking Ukrainian
residents who identify themselves as Ukrainians, not Russians from mother
Russia. No foreign invasion by mother Russia has ever occurred. Images of
Russian tanks are Western forgeries from a previous war in South Ossetia.

\enquote{Russian insurgents or Russian terrorists} are Western propaganda and lies,
cleverly used words used to stereotype the local Russian speaking Ukrainian
population and to create anti-Russia hysteria. These locals are only defending
their own economic interests. Their only crime is that they refused to subject
themselves to a new U.S. fascist installed government whose aim is to impose
upon them the same European style austerity, a form of economic slavery. This
same formula has been applied to many nations. 

The U.S., EU, IMF, World bank,
etc. who operates under the umbrella of an international banking mafia is
responsible for instigating for-profit false wars, false revolutions in order
to install puppet regimes in countries. 

The new puppet leaders facilitate in bankrupting their nation by accepting an
IMF \enquote{poison pill loan}, thereby guaranteeing a near collapse, forcing
further dependency on the IMF. These new creditors (hyenas) now move in for the
kill to rape, pillage, loot and take control of that country’s resources. 

While the puppets and oligarchs fill their coffers, the people pay a heavy
price through an IMF re-structuring program known as \enquote{austerity}. It is
manifested in many ways, e.g. hyper inflation, 50\% reduction in pension,
devaluation of banking assets, raising of gas prices, reduction in salaries,
creating mass unemployment and unsustainable economy turning people into
beggars. This has been the main cause and reason for mass riots in many EU
nations. 

Greece and Iceland are good examples of economies that have been ravaged by
these western thieves and pirates. Greece finally decided to draw the line and
take back control of their nation and we see how quickly Iceland has recovered
after expelling these corrupt banksters.

Most Ukrainian politicians and oligarchs have been bribed and bought by western
powers for years who then siphon off and sold cheaply to the West the wealth,
resources and labor of the Ukrainian people. This is why the Ukrainian economy
has been kept in a state of stupor and no progress, and the reason why people
remain impoverished. The median monthly salary for people in Ukraine is between
\$80 - \$300 USD. How do they survive on this? They just live together with
parents in tiny apartments. 

In every country the U.S. is involved there is
division, war, death, chaos and economic bankruptcy and only the American
people benefit. In Ukraine I can live like a rich man with my US dollars. 

The people of Donbas simply refused the newly U.S. installed puppet leaders
from imposing the same economic medicine to their regions. This is why their
cities and population center became the target of ethnic cleansing through
daily bombarded by Kiev with grad rockets, prosperous bombs and other
international banned weapons... all directed and orchestrated by Washington. 

America MUST head a recent warning issued by Putin \enquote{The spring can only
be stretched so far before it snaps back}. It is time to wake up and realize
who are the enemies of mankind. It is not Islam, ISIS or some other terrorist
insurgency which is a creation by the U.S. and those that control it. Lets not
forget that the United States is not a country or a nation, it is a Federal
corporation 28 USC § 3002 (15)(A). Corporations is what runs the world. This is
the true face of fascism.

\iusr{Robert Drake}

\enquote{...and although many (perhaps a majority) wanted him out....} Time to head for
Crimea Ollie, go in depth, or get shot or arrested trying... perhaps you would
prefer we did NOT help these people? It was an anti-criminal revolution, and if
you want to challenge the corruption and oligarchy that exists in the USA...
the Maidan is a good example of direct action. Stop being objective and
balanced, and be real and truthful... there is a difference in the journalistic
tendency, and the later is actually honest.

\iusr{Robert Drake}

\href{http://euromaidanpress.com/2015/02/14/rebuttal-wall-street-journal-article-stopping-putin-without-firing-shot/}{%
A rebuttal to Wall Street Journal article \enquote{Stopping Putin Without Firing a Shot}, %
Victor Rud, euromaidanpress.com, 14.02.2015%
}

\iusr{Steve Poe}

Oliver Stone can't come to Ukraine. Anybody famous who is not in line with the
official coup propaganda gets beaten up and thrown in a trash can. Someone who
is not as well known would be just kidnapped and tortured to death like it was
done with so many opposition figures in the coup Ukraine. There is not freedom
of speech in post-coup Ukraine. Asking someone what they think in Ukraine is
like asking a North Korean what they think about their government.

\begin{itemize} % {
\iusr{Menachem Boruch Askin}
You have no idea what you are talking about.

\iusr{Вадим Кудрявцев}
Surely Boruch should know, stop covering everything everywhere
\end{itemize} % }

\iusr{Nataliya Kukhar}

Hey Oliver Stone, can you help Interpol to find Yanukovitch? Looks like you did interview with him recently

\url{http://www.interpol.int/notice/search/wanted/2014-13031}

\iusr{Інна Гриньова}

Your post is awful. I make my own decision. The same as millions of Ukrainians.
And we decided to change our country for the better, we decided to say NO to
dictatorship. It's our choice and we made it with our hands. America has
nothing to do with it. Not a single american person was killed at the
revolution. So don't involve States to every event in the world.

I understand that you have problems and conflicts with US government. But,
please, keep Ukrainians aside cause you're offending us for no reason.


\iusr{Irina Stepanenko}

Oliver, thank you very much for giving the view of the true picture of what
happened in Ukraine during Maidan and what is happening now.. It requires a
great courage to dig out and show the truth. The same way as you did with your
great film about JFK. Ukraine has a long story of corruption, this is true, but
it hasn't started and hasn't ended on Yanukovich. And what is true is that he
hasn't sent one part of his nation against another part, this is done by
pro-Western goverment now just in order to weaken Russia. By the way, Ukraine
now has the Ministry of censorship, that is trying to close second biggest
Ukrainian TV chanel "Inter" for them showing Russian and Ukrainian singers,
that also perform in Russia during New Year Night program. Do they have such
ministry in Russia? No. Somewhere else? Espresso TV channel also had a problem
with this ministry. This is a "Democracy" and "Democratic power", that is
founded in Ukraine as a result of "Revolution of Spirit", but indeed is a
victory of brain washing media, intellegence and people, who are too lazy to
think and have an indepedent mind. Thank you!

\iusr{Nataliya Bodnar}

Have you visited Ukraine? Have you talked to people in Kyiv, Lviv, Odessa? Or
you are only showing your story from one point of view? Do you really think
that Yanukovich, who destroyed the army and stollen millions will tell you the
truth? If yes, you are no better than russian news reporter that only learned
to lie.

\iusr{Christian Serra}

\ifcmt
  ig https://scontent-frt3-1.xx.fbcdn.net/v/t1.18169-9/10915260_10153309656866542_4245356060286237311_n.jpg?_nc_cat=104&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=j8x5TKTlHuYAX_uWY8t&_nc_ht=scontent-frt3-1.xx&oh=69d2cafe239a0f289017ccf18b0cda93&oe=61CEA21E
  @width 0.4
\fi

\iusr{Gergely Ortutay}
You are either a Putin lover or a complete idiot.

\iusr{Iryna Tenitska Singh}

In Ukraine there are no fascists. Fascists are those who are killing Ukrainian
army from behind of eastern Ukrainian women and kids. Making war from windows
of hospitals and schools. Those who are promoting idea of "Russky Mir"..
Forcefully..

What is fascism by definition? Fascism is a form of radical authoritarian
nationalism. Isn't it that what Russians are showing by trying to interfere in
Ukraine and converting everybody into "Russky" by saying that everything
Russian stands above Ukrainian?

\iusr{Taras Atrazine}

Mr. Oliver,

I, personally, think that people like you should keep your opinions for
themselves and not plant such seed in the history.

Ukraine, as an independent country, will be able to handle it's own history
book.

There are no fascists in Ukraine! Unless I look like one, because young men
those you see on video tapes are fighting for their future! They have a right,
it's their home! Please, do not get involved into Russian propaganda!


\iusr{Jean Keryk}
I guess Stone learned all of this from talking to Yanukovych.

\iusr{Valeria Knight}
Am I to understand Mr. Stone is in debt, and will take money from anybody?

\iusr{Alexandra Chalupa}

It sounds like you're only interviewing one side and are on a mission to sell
Russian propaganda. You're probably being paid very generously for this,
probably from some of the \$70 billion Yanukovych stole from Ukraine. Who have
you met with in the new Ukrainian government? Which Ukrainian soldiers
sacrifing their lives have you sat down with? What about the leaders of Maidan?
You're not brave for putting this misinformation out there as some other
Putinites have commented, you're negligent and sloppy in your information
gathering which, coming from someone with your background can only mean you're
pushing an agenda. Unfortunately, it's Putin's agenda you seem to be profiting
off of amplifying. Shame on you. You're going to lose a lot of fans with this
project who rightful will no longer trust you.

\iusr{Jerry Kuziw}

Hi Oliver, Why not do an epic movie about "hunting-down" the
Bolshevik/Communist Party perpetrators of the HOLODOMOR??? Many who survived
the killing of 10 million Ukrainian farmers are still alive to testify and
bring to justice those criminals. We are told that quite a few of those
criminals are living in Miami Florida.

\iusr{Konstyantyn Shcherbakov}

Too bad you didn't get to interview Bin Laden before his death Mr. Stone. I'm
sure he'd be happy to share evidence of CIA involvement in the 9/11 attacks.

I understand that you have bills to pay but it's a shame that you chose to
accept such a lowly way of making a buck. Perhaps it would be much better
solution to sell you properties in the US and moving to one of the countries
that you defend at such a great length- russia or venezuela.


\iusr{Jerry Prytulak}

Who cares if the CIA , MI5 or even Mossad were involved to overthrow
Yanukovitch's corrupt Kremlin backed government. The most important outcome was
that Ukraine has rid itself of the 'cancer' implanted by previous Soviet
governments and in turn has helped the civilized world rid itself of Kremlin
involvement.

\iusr{Jame Smace}

No wonder there are so many Russian speakers in Eastern Ukraine. The Russians
killed all the Ukrainians and replaced them with Russians.

\href{https://ideas.time.com/2013/12/17/how-to-explain-whats-happening-in-the-ukraine/}{%
How to Explain What’s Happening in Ukraine, Andrea Chalupa, ideas.time.com, 17.12.2013%
}

\begin{itemize} % {
\iusr{Gail Patenaude}

Still the same old journalism out of the US. Just enough truth, but not fully.
Extend your reading material somewhat, say some wise university professors and
ex-CIA chaps with inside story.


\iusr{Jame Smace}

Will you be offering any substance or just ad hominems? The last refuge of a
failed argument is personal attacks. What facts in the US Congressional
Commission on the Ukrainian Famine do you dispute? There are 7 volumes - take
your time in responding

\end{itemize} % }

\iusr{Jame Smace}

When does your Holodomor movie come out - Russia's invasion that murdered a
third of Ukraine.

\iusr{Василиса Войнова}

Да Стоун ты попал. Свидомые теперь тебе загадят всю ленту. Но это считай как
признание, чем больше их тут, тем очевиднее твоя правота. Правильным путём
значит идешь, товарищ. Заодно и хорошо видно всю степень их агрессивности,
русофобии и дебилизма. Европа, забирайте этих скакунов скорее к себе. Не
нарадуетесь

\begin{itemize} % {
\iusr{Menachem Boruch Askin}
What an idiot you are!
\end{itemize} % }

\iusr{AxelNunez Vazquez}
You are 100\% correct in your analysis

\iusr{Олег Святка}
what is your price, Oliver Stone?

\iusr{Yulia Porozhna}
Mr. Stone, you are idiot. Learn the history of Ukraine \& should stay away from Ukraine.

\iusr{Мария Яворская}

What do you expect from a guy who thinks Hitler was a "scapegoat" and Stalin an
"underrated war hero?" Great rebuttal here:

\url{https://nobsrussia.com/2014/12/31/useful-idiot-of-2014-oliver-stone}

\iusr{Roman Hultso}

"Great men are not always wise; neither do the aged understand judgment." You
are making it even worse, Mr. Stone, please. Better go somewhere else (N. Korea
might be your choice?) Leave Ukraine to Ukrainians, don't look for the US
soldiers here, because you will not find any.


\iusr{Borys Shchepanskyy}
shut the fuck up

\iusr{Kosako Sonico}
Cock sucker

\iusr{Lida Zinko}

In the last elections, the ultra far-right Ukrainian parties received less than
5\% vote, one of the lowest showing in the entire Europe ( 25\% France anyone?)
yet Russia, with its highest concentration of Neo Nazis in the entire world,
continues to barrage and troll the media that Ukrainians are nazi thugs.
Perhaps, Mr. Stone, next time you're there, you should ask why Mr. Putin openly
funds France's ultra-nationalistic Front National.


\iusr{Lida Zinko}

Your other comment that Ukrainians murdered Jews, Soviets and Poles in 1941 is
hateful and has no place here. I am not going to argue this, although you
should read some alternative history not written by the Soviet Russia. However
with this comment you're actually asking the reader to infer that Ukrainians
are ultra-nationalistic Nazi thugs without actually making this statement, as
you know very well that it's hateful. Just keep this in mind, Russians took
over Crimea and Eastern Ukraine in order to " protect their own ethnic
Russians" ( who are actually Ukrainians citzens) - isn't it the ultimate in the
tribalism and ultra nationalism.

\iusr{Orest Andrijiw}

Old, old, well-known russian propagandist attitude that was, is and will be
known for what it is, exactly that Mr. Stone - imperialist russian propaganda,
true, very well planned and executed, but nevertheless, just simply, russian
imperialist, expansionist, murdering, evil, lying, psychologically extremely
dodgy... Scum!!


\iusr{Sergey Zuyev}

Ukraine was a very divided country. The election for president was close but
Yanukovich won the vote. Just before the coup polling showed that only 45\% of
Ukrainians supported Maidan protests. That happens to be exactly the percentage
that voted against Yanukovich. Majority of Ukrainians opposed Maidan. So the
people who lost the election just seized power by force. 

\href{https://www.kyivpost.com/article/content/ukraine-politics/poll-half-of-ukrainians-dont-support-kyiv-euromaidan-rb-334469.html}{%
Poll: Half of Ukrainians don’t support Kyiv Euromaidan, kyivpost.com, 30.12.2013%
}

\begin{itemize} % {
\iusr{Serhiy Uryn}
Mind the date of the publication: it is before first murders by Yanukovych

\iusr{Sergey Zuyev}

It is indeed before the sniper from the building occupied by Right Sector
started shooting both police and protesters. Majority of Ukrainians did not
support the Maidan message so the coup organizers had to resort to violence.
But first murder was committed by Maidan protesters when they stormed the Party
of Regions offices and murdered an employee there.


\iusr{Roksolana Vasilishina}
Zuyev - putinistic troll

\iusr{Sergey Zuyev}
So Roksolana: Does it make you a Nazi troll? Why can't you just admit that at least half of Ukraine did not want your violent coup.

\iusr{Serhiy Uryn}
\textbf{Sergey Zuev}: here is some homework on snipers for you

\href{https://www.pravda.com.ua/rus/news/2014/03/7/7018031/}{%
Москаль рассказал, чьи снайперы стреляли на Майдане, pravda.com.ua, 07.03.2014%
}

\begin{multicols}{2}
В участников протестов на Майдане и милиционеров стреляли снайперы МВД и СБУ, а
не какие-то иностранцы.

Об этом заявил нардеп Геннадий Москаль в интервью "Зеркалу недели".

Москаль, который обнародовал планы операций по зачистке Майдана, заявил, что
офис Партии регионов сожгли переодетые работники СБУ.

"Проведению обеих спецопераций предшествовала специальная подготовка.
Переодетые работники СБУ под видом митингующих, к которым присоединились и
настоящие участники акций протеста, подожгли офис Партии регионов, в результате
чего погибли два человека", - заявил Москаль.

"Вместе с этим снайперы получили указание расстреливать не только протестующих,
но и милиционеров. Все делалось для эскалации конфликта, чтобы оправдать
силовую зачистку Евромайдана", - заявил Москаль.

Он напомнил, что сразу после этого появились гневные призывы к президенту от
областных советов Востока, Юга и Крыма с требованиями принять решительные меры.

"То есть эти вещи были взаимосвязаны и четко спланированы", - считает Москаль.

Он заявляет, что использование снайперов предполагалось спецоперациями "Волна"
и "Бумеранг".

"Было несколько групп снайперов - из СБУ ("Альфа") и МВД (спецподразделения
внутренних войск плюс "Сокол")", - заявил Москаль.

Он убеждает, что приказать стрелять подразделениям МВД мог только экс-министр
Виталий Захарченко, а "Альфе" - экс-руководитель СБУ Александр Якименко.

Информацию о "третьей стороне", которая отдавала приказы снайперам, Москаль
называет попыткой нового руководства МВД и СБУ "заработать авторитет" и
отбелить силовиков.

"В обнародованных мной документах... названы снайперские группы конкретных
украинских спецподразделений. Там же указаны их точки дислокации, фамилии
ответственных, позывные снайперов", - напоминает Москаль.

Он не понимает, "как туда могли затесаться какие-то иностранцы? Какая "третья
сила" приснилась Авакову с Наливайченко?"

Как известно, новый глава МВД Арсен Аваков заявлял, что действий снайперов в
Киеве причастна некая "третья сила".
\end{multicols}

\iusr{Петр Сергеевич}

It's so simple to distinguish Right Sector sniper from Left or Middle Sector
one sitting in WA, isn't it? And by the way (I'll give you a little guide) what
is that "occupied" building you chatting about? When Maidan shootout unraveled,
Trade Union House (previously headquarter of uprising) was cleared from rebels
and burnt down. There was not a single rebel inside Zhovtnevy palace too. All
another buildings on Kostyolnaya and Khreschyatyk str., "Ukraina" hotel was
NEVER "occupied" by anyone. Давай, безродная ватная мразь, расскажи мне -
киевлянину - про Правый сектор.

\end{itemize} % }

\iusr{John Yates}
You are a fool Mr Stone

\iusr{Angel Miles}

Perhaps hollywood should stay out of international politics. Just because
you're famous doesn't mean your right.

\iusr{Dzvinka Hayda}
you are still hoodwinked

\iusr{Květoslav Slávek Hradecký}
Thank you for nice films, interesting documents and bold views. HAPPY NEW YEAR  @igg{fbicon.thumb.up.yellow} 

\iusr{Jan Koopman}
so true

\iusr{Chamba Fernandez}

\ifcmt
  ig https://scontent-frt3-1.xx.fbcdn.net/v/t1.18169-9/535962_10155014620285352_6456031025624581389_n.jpg?_nc_cat=106&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=cYfx8LzQNzIAX8a71Og&_nc_ht=scontent-frt3-1.xx&oh=3bcb7b804704e30634efc2852e833775&oe=61CDCCAC
  @width 0.4
\fi

\iusr{Carol Anne}
Agree with you 110\% on this one. Good job Mr. Oliver Stone!

\iusr{Van Huebner}

Seems to me there's a lot of logical fallacy at work with regard to who is to
blame \& who to trust on the topic of the Ukraine crisis.

For example, wanting democracy or independence from either America or Russia
isn't a bad desire - that is, unless what you plan to do as a democracy
includes the same abandonment of all consideration for the environment ( such
as frack and destroy arable land and ground water forever ), or the fate of
communities that that wish to preserve local control of the agrarian methods
(bioregionally appropriate yield) versus allowing The West (including both gov
\& NGOs of the EU - including Israel btw) as a tool of Agribusinesses such as
Monsanto to basically steal the small farm for an ailing global marketplace (
ie, increased profit for the more powerful producers of consumable goods and
technology which btw is dependent upon the very inscrutable manipulation of
public information through, yes, logical fallacies!)

So, the question becomes both who has what to gain and how do each of the
protagonists propose to go about establishing and maintaining their goal when
examining such issues as the fate of this territory. I propose that as long as
one purports to be talking about Nationhood, a listener should recognize a
deeper fundamental issue at stake: the very use and abuse of land and
communities more in touch with the soil. This indeed makes the Ukraine a
greater focal point for discussion regarding "who's to blame" for the
despoliation of arable land versus who is getting in the way of the expansion
of Global Industry and its appropriation of wealth by profiting from the
natural resources in the territories of yet to be manipulated others.


\iusr{Rick Stasel}
Thanks Oliver for exposing the truth to a larger audience. You're a great American and a national treasure

\iusr{Jeff Grotke}

the larger point is they don't want us there any more than we want Russia in
Cuba or Tijuana, and it is brinkmanship to think otherwise

\iusr{Robert Hayes}

Keep at it Oliver! Most of us want to know the truth... even though there are
plenty of Americans that want to deny it.

\iusr{Christof Conings}

No ordinary person knows who really shot down people on Maidan from the roofs
but the fact is that under Yanu the corruption was unlimited and they would
falsify all new elections ,court decisions as is done in Crimea and Donbass.
Yanukovitsj is not the person to ask who it was he sold people to Moscow . The
big protest on Maidan is not because of the not signing of the eu contract but
the fact that Berkut officers hit and shoot down students .(that was to see by
people) That was the sign for the people of Ukraine to stop the regime of
corruption and violence . For sure CIA was there as the KGB and others were in
Kiev at that moment .

\iusr{Yuri Panchul}

The war in Ukraine is actually a sort of religious war, and the religion in
question is called "Democracy Promotion". Here is a quote from Michael McFaul,
a formet Ambassador of the United States in Russia:

\href{http://panchul.livejournal.com/316473.html}{%
Макфол для чайников / McFaul for Dummies, panchul.livejournal.com, 12.12.2013%
}

Quote from Michael McFaul: These state-to-state relationships helped to
dissuade Kuchma and Shevardnadze from cracking down on their opposition
movements and also facilitated the work of American non-governmental
organizations, which worked with civil society and opposition groups inside
both countries.

Quote from Michael McFaul: In the fall of 2003, numerous American envoys tried
to convince President Shevardnadze to hold free and fair elections. When he did
not, the Bush administration did not immediately denounce the election results,
but gradually signaled support for the opposition until they seized power. In
the run up to the Orange Revolution in Ukraine, Bush administration officials
also encouraged President Kuchma to hold free and fair elections, and by
denying visas to prominent Ukrainian businessmen, signaled to the regime the
consequences of a fraudulent vote. These threats did not prevent Kuchma from
trying to steal the vote, but they may have helped to constrain the president
and his entourage from using force against the demonstrators. Indirectly,
American-supported media outlets’ reports on Kuchma’s involvement in the
killing of Ukrainian journalist Georgiy Gongadze and the vast corruption of
Shevardnadze’s Georgian government also helped to undermine the popularity and
power of these leaders.

Quote from Michael McFaul: NDI and IRI played active roles in encouraging
cooperation among the democratic groups in Serbia and Ukraine, though less so
in Georgia. They did so by collecting and then sharing survey data, which
underscored the electoral advantage of a single candidate. In both countries,
this data pointed to the need to back particular candidates — Voijislav Kostunica
in Serbia and Viktor Yushchenko in Ukraine rather than the more charismatic
opposition leaders in both countries at the time (Zoran Djinjic in Serbia and
Yulia Timoshenko in Ukraine).

\iusr{Thomas Dacey}

I had no idea about this. Thanks for letting the truth out.

\iusr{Marusia Stashynsky}

Oliver Stone I have no idea where your getting your info from but your research
is full of propoganda!

Do you have any intentions of visiting Ukraine?

Do you have any intentions of speaking to the people who live in Ukraine?

It wouldn't be a documentary of TRUTH if your answers are no!!!

Do yourself a favour go to Ukraine and do your research or you will be laughed
out of the film industry and your career will be as good as DONE!!!!

\iusr{валентина вишнякова}

agree with you !!!!!!!!!! The CIA has made a revolution in Ukraine

\begin{itemize} % {
\iusr{Menachem Boruch Askin}
Stop saying stupid crap.
\end{itemize} % }

\iusr{Aivo Blum}

\ifcmt
  ig https://scontent-frt3-1.xx.fbcdn.net/v/t1.18169-9/10881649_10152971867379461_658476262793598259_n.jpg?_nc_cat=104&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=saE0RzTf5RIAX-BIsLQ&_nc_ht=scontent-frt3-1.xx&oh=8555cc42577b2b9bbf071ef71511356b&oe=61CC9200
  @width 0.4
\fi

\iusr{Mark Kraft}

While there is little doubt that the US State Dept. did have some role in
supporting Ukranians in overthrowing their leader, they didn't do so in a
vacuum.

You have to keep in mind that their Parliament - including many who were
previous supporters of Yanukovich - voted overwhelmingly for his removal from
office. By your own admission, the people of Ukraine wanted this to happen, and
he has no mandate to rule.

I also find it rather disturbing that you cite an RT article - RT being
controlled by the Russian government, which in turn cites an article by the
Russian government owned Rossiya segodnya - known in the West as Sputnik
International - about how the US wants to contain Russia.

Gee, Ollie. I wonder why. Furthermore, I wonder why all the Baltic nations,
Germany, the former Soviet nations, etc. have overwhelmingly supported
sanctions and closer ties with NATO. They're scared of Putin and the Russians,
Mr. Stone. They are afraid of invasion, just as they are afraid of having their
gas cut off in the middle of winter, being extorted by the Russians for
concessions, etc.

The best thing for all of these nations is to strengthen ties with Europe and
find ways to be less reliant on Russia and more open to the free market, as
opposed to being extorted back in to the former Soviet sphere - with Russians
basically centralizing and monopolizing the distribution of such a cartel.
Russia's idea of an economic union is little different than the kind of
mercantilism, imperialism, and exploitation that the US rose up against in
gaining its independence. I personally have few qualms when our government
prefers not seeing that happen again, elsewhere.

You don't seem to acknowledge that Ukraine had the Crimea seized by Russia -
with actual Russian ground troops, though Putin initially lied about it -
because Ukraine might've wanted a better deal for providing Russia with a key
naval base on the Black Sea. Somehow, it's horrible that American diplomats
sided with the Ukrainian people in overthrowing their dictator - the so-called
"president" you suggest as being legitimate, despite arresting the opposition
leader. That's awful... but sending ground troops into a sovereign nation by
Russia is okay?!

I'm not saying that you should completely dismiss the information you have
received... and there is a story there about what American people don't know
about how some former neocons were giddy as hell with the Ukranian uprising -
not that they really played kingmaker in the whole affair - but you seem
absolutely determined not to have a balanced perspective on the matter, Mr.
Stone. Instead, you seem determined to interview and seek advice from those who
are least likely to offer an unbiased perspective.

Obviously, this is a complex situation... and by no means are US hands entirely
clean... but your lack of balance in the quest for a pre-ordained story just
makes you a well-informed, entertaining... but ultimately naive... dupe. And
this is unfortunate, because your work would be better - and potentially more
damning, tragic, and complex - if your work had more dimensions to it.

\iusr{Borys Kucherenko}

You are not brave and you are not a some kind of investigator or researcher.
You are simply fool . But as a celebrity who is decided to judge Ukrainians by
talking to complete moron who can not put two words together without help?! -
did you noticed that ? Or your interpretator "forgot" to tell you that? Now
excuses sudenly because you can be our "history teacher" about the time of cold
war? You have no idea what are you talking about.


\iusr{Oksana Styles}

Hopefully among those historic facts you mention, you'll include other well
known tragedies, such as famine 1933-34, massive collectivization and
deportations of Crimean Tatars, to enlighten your viewers why people of Ukraine
had had enough of the 'friendly' neighbour's interference.

\iusr{Natalia Ko}

I have a question for you Ms Stone. Did you were in Maidan when it was
happenning or in you cosy home? You talk when you see and when you touch.
Please, give me a break and get STONED. How well educated you are? Or Putins
money talk to you more, that your own morality? Shame on you! You even have no
courage to go yourself to Ukraine and talk to people who were in Maidan! Shame!
Shame! Shame on you! On behalf of all thoes people in Ukraine, I wish, you can
sleep at night, because they are not! And on behalf of all Ukrainians, I wish,
you can go to Maidan and look into theirs eyes with honesty and appologize for
what you just said!

\begin{itemize} % {
\iusr{Lisa Marie White}

fortruss.blogspot.com link

Sadly your efforts were highjacked by people who do not represent you and who
do not have your interests at heart. Yanukovych didn't sign the association
agreement because it was bad news for Ukraine. I support your movement and
trying to join the EU, but the EU are mostly puppets of America. It's not
independence. Do you want that? I wish nothing but the best for the people of
Ukraine but your movement has been taken over by lunatics.

\end{itemize} % }

\iusr{Иван Путинок}

Mr. Stone THANK YOU, the world must know the truth! That wasn't any revolution
as they say, it was terroristic removing of president Yanukovich in armed way
and now we have civilian war inside the ex-Ukraine. That's it! All this trouble
was conducted by US and EU. Please tell the world true story!!!


\iusr{Александр Ермолов}
Низкий Вам поклон , за правду !

\begin{itemize} % {
\iusr{Menachem Boruch Askin}
If you call it truth, you have no brain.

\iusr{Вадим Кудрявцев}
And you are not Boruch
\end{itemize} % }

\iusr{Akos Magyar}

Stoned responds with more KGB conspiracy theories...
He just cannot fathom that most Eastern Europeans genuinely want a Western lifestyle. Since he thinks the West is evil (from his 20 room Hollywood mansion and standing reserved table at Spagos) he will never accept any anti Soviet movement.
Shit even the anti Nazi partisans and activists had foreign support.
DUH !!!

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10888633_10152525587321691_6019887782255012466_n.jpg?_nc_cat=100&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=nHc21Y8Q4jYAX_-YSGo&_nc_ht=scontent-frx5-1.xx&oh=357d7e898c3e1759580c0173bf9d8298&oe=61CDE9EB
  @width 0.4
\fi

\iusr{Kath Stevenson}

Well MISTER Stone by the number of russians on here applauding you seems very
evident that they find you a true putin ally. Makes any normal person come to
the conclusion that your backers and you are russian supporters and putin's
dirty money is in your bank accounts. If you hate the USA so much do everyone a
favour and move to the kremlin...

\begin{itemize} % {
\iusr{Christian Serra}

A typical example of democratic people like you. "Don't you agree with the
government? Leave!". You are on the same wave with the nazi terrorists which
took the power in kiev thanks to the CIA


\iusr{Kath Stevenson}

Typical example of a mindless puppet! If you actually read my comment it said
USA not government. Possibly you are on the same wavelength as the ruSSkie
trolls???

\end{itemize} % }

\iusr{Ramunas Cesonis}

Mr Stone, I guess you're one of those who simply ignore the will and the
ability of Eastern European countries to choose their own destiny. I suggest
you read this:

\href{http://euromaidanpress.com/2014/10/27/western-commentators-should-rid-themselves-of-old-prejudices-dating-back-from-the-age-of-colonialism-before-commenting-on-eastern-european-affairs/}{%
Orientalism reanimated: colonial thinking in Western analysts’ comments on Ukraine, Fabio Belafatti, euromaidanpress.com, 27.10.2014%
}

\iusr{Narcis Semeniuc}

than please, after reading carefully the real history of Ukraine, go to Ukraine
and TALK TO THE REGULAR PEOPLE, TALK TO THE PEOPLE THAT HAVE PARTICIPATED AT
EUROMAIDAN, make research, find and TALK TO SURVIVALS FROM WW2, make research
and find out how many of the corrupt people in Ukraine are realy ukrainians,
ask for the documentary about the "HOLODOMOR" - the huge artificial hunger in
Ukraine, DO A REAL JOB. Unless, you are not at all interested in presenting the
truth and in such case, you could have at least enough decency and say open:
WHAT IS YOUR REAL REASON behind this FAKE DOCUMENTARY???

\iusr{Bill Kurlak}

OLIVER - you are INCORRECT - There were NO armed Ukrainians forcing Yanykowych
out of Ukraine in February 2014. VIDEO proves that he quickly took all of his
costly possessions (which he stole from the Ukrainian people) and took off on a
helicopter.) DID YOU VIEW THIS VIDEO??? DID YOU SPEAK TO THE UKRAINIAN PEOPLE
WHO WERE AT THE MAIDAN?? DID YOU SPEAK TO THE GRIEVING FAMILY MEMBERS OF THE
UNARMED UKRAINIANS AT MAIDAN?? DID YOU GET ANOTHER POINT OF VIEW, BESIDES
YANUKOWYCH'S BIASED OPINION?? YOU SHOULD KNOW BETTER!! DO YOUR RESEARCH AND
PRESENT THE TRUTH IN YOUR MOVIE!

\iusr{Allen Kapp}
You must really need the money to turn into such a dishonorable person.

\iusr{Серікжан Есенғосұлы}
Come to Kiyev and talk to local citizens. I think you will change you mind instsntly.

\iusr{Valeriy Oliynyk}

Mr. Stone, I can tell straight to you face that you don’t have any knowledge in
Ukrainian history at all. I don’t know in what college you were taking history
classes but I would like to know. I will personally send letter to this college
to change you grade to F

I just can imagine that you have some problems in your movie business and you
have to make up some crap like this about “Nightingale” in 1949 and CIA
paratroopers in Stalin’s Soviet Union.

You just don’t have any ideas about what are you talking here or you just a
person who like to spread this kind of rumor and enjoy all disagreement and
angriness from people here, I mean from people who live or lived and love
Ukraine

\iusr{Philip Oakman}

Can someone explain how Yanukovych became the democratically elected leader of
Ukraine if he was so corrupt and widely hated?

\begin{itemize} % {
\iusr{Константин Азаров}

He was seen as best among others, with more or less clear profile at time of
election. New president Poroshenko was involved in corruption scandals long
before his election.

\end{itemize} % }

\iusr{Наталия Вер}

That is ever so intriguing why people do things they do. In your case, Mr.
Stone, the most likely motivation would be either money – pure and simple; or
striving to be anti-mainstream, unique, avant-garde.

If you are after Cremlin’s paycheck – this is understandable indeed, but not
too likely your major motivation. Easy deal – Lord of the nuclear button’s
thirty pieces of silver would be generous enough to make you forget about
dilemmas like choosing the color of your next yacht – you can have them in each
color of the rainbow spectrum. But again – not too likely this is your sole
motivation. More probably – you share the same human weakness, that Mr.Putin
has – both of you, having reached some major accomplishments in your social
status and careers on a global level - are now trying to instill your heritage
into the times to come – for future generations. Mr. Putin has the ambition to
go down in history books as a great re-unitor of russian lands –whatever it
might mean in his sick brain. You wanna make sure you stand out from the
mainstream opinion, crowd mass thinking – you aim to be different at any cost –
having this clairvoyant whistleblowers status.

Mr. Putin will sure go down history books as a paranoid obsessive tyrant
imperialist and a lousy manager of a huge country with massive potential. How
you go down for centuries to come is yet to be defined. Or, more precisely – it
can be re-directed towards the more positive image still. Or remain as is now -
a Hollywood director with ambition to create history, not just direct very
roughly called historical movies – that he parlously failed.

Whichever motivation it is – please remember, Mr. Stone – Ukraine is still
paying a huge price for it. Have some respect. There’s blood on those crispy
notes. There's blood on your reputation now too.

\iusr{Alex Agersten}

The Cold War has never really ended, after the fall of Soviet Union back in
1991, USA continued to expand NATO to other European countries, like they never
really wanted peace between us. Anyway the spirit and tradition of Russia will
never been broken, Russia will prevail

\iusr{Taras Chaban}
Mr. Stoned out of your mind.

\iusr{Alexander Staroselsky}
Mr Stone, do you plan to limit your interview activity by Russians and Yanukovich or you plan to interview the other side as well?

\iusr{Oleg Savitskii}

I think you misunderstood what mr. Stone was trying to say. It's ok for the
people to go and demand their rights, but it's not ok for some foreign power to
high jack the revolution in order to achieve its own geopolitical goals. And if
you analyze the situation carefully, tell me how Poroshenko is different from
Yanukovitch? Is he not part of the same gang who has been plundering Ukraine
for the last 20 years? Everybody in Ukraine knows that all Ukrainian oligarchs
have become oligarchs illegally. While ordinary people were dreaming of
becoming prosperous and free and part of Europe, they were amassing their
fabulous fortunes stealing everything that had been done by the previous soviet
generations, and on top of that treating their own people as cattle. Why is
nobody talking about that? Or maybe everybody wants to become an oligarch just
like Poroshenko?

\iusr{Paul Reader}

Just some facts....Ukraine nationalists collaborated with
the Nazi’s during WWII, they even had their own SS Division (SS Galacia).
The Crimea was Russian territory won back from the Ottoman
Empire in the late 1800’s and given to the Ukraine as a protectorate by Khrushchev in the 1950’s.
The Crimea is Russia’s only warm sea port and NATO wants
them out.

America supposedly has the freedom of Ukraine as an agenda,
but America has CSG coming out of it’s ears and they would welcome the European market share that Russia currently has.
Vice President Joe Biden's son and a close friend of Secretary of State John Kerry's stepson have joined the board of the leading Ukrainian gas producer............ why?........... to save the people from Russian aggression or to grab more filthy money for the few that govern the wealth of the globe?............

\iusr{Rex Weyler}

Oliver is correct about events in the Ukraine. Yanukovych is no saint. He was
corrupt. But the US toppled him because he would not do their bidding, and the
US backed a bunch of Nazi thugs to do so. Pepe Escobar, as Oliver suggests, is
the best journalist covering these Ukrainian and Eurasian events. And here is
another informative report from Casey Research, a conservative financial
research firm:

\url{http://www.caseyresearch.com/cdd/welcome-to-the-machine}


\begin{itemize} % {
\iusr{Rex Weyler}

No proof Nazsi took over Ukraine? Are you blind Gennady? In fact, the US took
over the Ukraine, and they used these Nazi thugs to do it. Wake up.

\ifcmt
  ig https://scontent-frx5-2.xx.fbcdn.net/v/t1.18169-9/10917326_804962606238054_3546164243849664398_n.jpg?_nc_cat=109&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=bvCnt6_MK6kAX_DIVh2&_nc_ht=scontent-frx5-2.xx&oh=2153e71dd8e8e4362dbb5b6d57c3c323&oe=61CCD7B7
  @width 0.4
\fi

\iusr{Rex Weyler}
more info about the Ukrainian Nazis here:

\href{http://vineyardsaker.blogspot.com/2014/12/2014-end-of-year-report-and-look-into.html}{%
2014 "End of Year" report and a look into what 2015 might bring, %
vineyardsaker.blogspot.com, 30.12.2014%
}

\ifcmt
  ig https://scontent-frx5-1.xx.fbcdn.net/v/t1.18169-9/10888803_804968459570802_2977469489451859765_n.jpg?_nc_cat=110&ccb=1-5&_nc_sid=dbeb18&_nc_ohc=23MjRFTWtaEAX-pAmUo&_nc_ht=scontent-frx5-1.xx&oh=d9056437faf099e60c5fa0deda05eabd&oe=61CD8F42
  @width 0.4
\fi

\iusr{Taras Atrazine}

P.S: Rex, I don't mean to be rude, but you are an idiot and using THE in the
front of the name of an independent country is a grammatically incorrect and is
offensive towards our nation.


\iusr{Rex Weyler}

Taras .. "The" and "Ukrainian" both modify "Nazis," and with all due respect, I
am no idiot. You can find more photos of these Ukrainian Nazis yourself, or
even go see them at public rally's in Kiev, or on the battle front in Donbass.

\iusr{Marijka Stadnyk}

Are you concerned about these Russian Nazi's currently in Ukraine on behalf of
Putin, Rex?

\href{http://euromaidanpress.com/2014/08/27/russian-neo-nazi-kornilovtsy-battalion-operating-in-ukraine/}{%
Russian neo-Nazi \enquote{Kornilovtsy} battalion operating in Ukraine, euromaidanpress.com, 27.08.2014%
}

\iusr{Marijka Stadnyk}
Or these?

\href{https://jamestown.org/program/the-involvement-of-russian-ultra-nationalists-in-the-donbas-conflict/}{%
The Involvement of Russian Ultra-Nationalists in the Donbas Conflict, Richard Arnold, jamestown.org, 11.06.2014%
}

\ifcmt
  ig https://jamestown.org/wp-content/uploads/2014/06/Russian_far_right_-_EDM_June_11__2014.jpg
  @width 0.4
\fi

\begin{multicols}{2}

Several cities in Donbas, the eastern portion of Ukraine comprising the regions
of Donetsk and Luhansk, have been embroiled in Russian-sponsored secessionist
violence against Ukrainian authorities since early April 2014. And while Russia
has no officially identified uniformed troops in the region, there are claims
that it has been involved in the fighting through the deployment of irregulars,
like the Chechen Vostok battalion (see EDM, May 30). Other irregular forces
have also been involved, such as hardline Russian nationalists. 

Now it appears there are connections to the most extreme nationalists, Russia’s
neo-Nazi movement. Posting on Facebook, Alexander Belov, the leader of the
banned Movement Against Illegal Immigration (known by its Russian acronym
DPNI), announced the death in Donetsk of Sergei Vorotsev. Vorotsev was a former
organizer for the DPNI in the Moscow Region town of Korolev (Official Facebook
page of DPNI, June 4). According to the same posting, Vorotsev was killed in
the battle for the Donetsk airport.

The presence of a former member of the DPNI in eastern Ukraine is not entirely
surprising, but it does suggest a merging of the goals of such movements and of
the Russian regime. Similarly, other neo-Nazi groups have also tried to become
involved in the Ukrainian crisis, with the group \enquote{Sputnik and Pogrom}
organizing humanitarian aid for those ethnic Russians affected by the fighting
in the region. A banner bearing the slogan \enquote{Donbas says thank you} was posted
on their site to thank all those who had donated financial aid
(sputnikipogrom.com). On another neo-Nazi website (officially banned in Russia
but purportedly hosted on servers in the United States to prevent closure by
the Kremlin), that of the skinhead gang \enquote{Slavyansky Soyuz} (Slavic Union),
there is a call for Russia to start arming the separatists or even to provide
more substantial aid due to the disproportionate array of forces deployed
against them by the government in Kyiv

(\href{http://www.demushkin.com/content/news/222/8964.html}{demushkin.com link}). 

Finally, an individual
from the \enquote{Russkiye} ethno-political movement, which grew out of the 2011
protests against United Russia and the reelection of President Vladimir Putin
(and whose membership overlaps with many other neo-Nazi gangs), expressed
condolences on May 18 to the families of those killed in the fighting in
Donbas, saying that \enquote{we must prepare ourselves for new victims}

(http://www.dpni.org/articles/vazhnoe/39003/).

It also seems that the extreme nationalists have renounced their position in
the Russian political opposition movement. Illustratively, the calls by some
nationalists for a \enquote{new Manezh} (street protest) against Putin on May 18 were
dismissed by most Far Right leaders as a provocation
(\href{http://www.sova-center.ru/racism-xenophobia/publications/2014/06/d29635/}{%
Расизм и ксенофобия. Итоги мая 2014 года, www.sova-center.ru, 02.06.2014%
}).

This evidence strongly suggests, therefore, the Kremlin has now co-opted the
neo-Nazi movement.

Nevertheless, the Russian Far Right’s involvement in Donbas has consequences
for the unity of other irregular forces who are supporting the separatists in
eastern Ukraine. Specifically, not all the Russian neo-Nazis were happy with
the prospect of working with other elements—especially the Chechens—in the
fight for eastern Ukraine. On DPNI leader Belov’s Facebook page, for instance,
there were comments, presumably from other neo-Nazis, deriding the involvement
of the Chechens. Indeed, Belov himself posted commentary on the DPNI website
complaining that Chechens were in Donbas \enquote{with [Chechen leader Ramzan]
Kadyrov’s blessing and for money} and not out of reasons of patriotism or
ethnic belonging (\href{http://www.dpni.org/articles/novostnaya/39200/}{%
АЛЕКСАНДР БЕЛОВ: ЧЕЧЕНЦЫ В ДОНЕЦК ПРИЕХАЛИ С БЛАГОСЛОВЕНИЯ КАДЫРОВА И ЗА ДЕНЬГИ, %
www.dpni.org, 02.06.2014%
}). 

This was despite the denials from Chechen president and Kremlin appointee
Kadyrov that he had directed any Chechens to go to Donbas. Ethnic-Russian
nationalists question the commitment of the Chechens and other North Caucasians
to the cause of \enquote{Novorossiya} (\enquote{New Russia,} a vision declared
by Vladimir Putin on April 17 calling for bringing southeastern Ukraine under
some form of Russian control—see EDM, May 1). 

Rather, many ethnic Russians perceive people from the
Caucasus as foreign at best and all too often as hostile aliens. Indeed, there
has been a spate of race riots against people from the Caucasus in Russia in
recent times (see EDM, March 5), which presumably was something the organizers
of the May 18 rally were trying to provoke. It is tempting to conclude that the
irregular Russian juggernaut now fighting in eastern Ukraine is held together
by its common goals, but it will have to keep winning future victories or it
will dissolve in internal squabbling.

The evidence that the Kremlin is working with neo-Nazi or ultranationalist
forces in Donbas is highly ironic but not surprising. The regime’s allies in
the Russian Far Right make the Kremlin’s warnings of a \enquote{neo-Nazi} takeover in
Kyiv seem even more incredulous. Ostensibly, it was concerns over the role of
the Ukrainian neo-Nazi group \enquote{Right Sector} and its leader Dmitri Yarosh in the
new government that served as justification for the Russian government to annex
Crimea. Kremlin propaganda from the time told of mass shootings carried out by
Right Sector and even broadcast what it alleged to be photographs of corpses
lying in freshly-dug mass graves

(\href{http://antimaydan.info/2014/03/lider_neonacistskoj_gruppirovki_pravyj_sektor_dmitrij_yarosh_zayavil__37446.html}{%
Лидер неонацистской группировки «Правый сектор» Дмитрий Ярош заявил о создании карательного батальона «Правый сектор — Восток» для подавления русского восстания на Юго-Востоке Украины, antimaydan.info, 13.03.2014%
}).

While, Right Sector has indeed been involved in a number of violent actions in
Ukraine such as an April 2014 attack on a court and judge in the country

(\href{http://novorossy.ru/news/news_post/pravyy-sektor-zahvatil-verhovnyy-sud-ukrainy-a-nakazhut-yugo}{%
Правый сектор захватил верховный суд Украины, а "накажут" юго-восток, novorossy.ru, 07.04.2014%
}),

the fact that the Kremlin is working with its own domestic neo-Nazi movement
makes its claims seem all the more disingenuous.

The Russian Far Right’s involvement in the Ukraine crisis and its growing ties
to the Kremlin also provide a warning of how volatile the current situation is
inside Russia itself. If such trends continue, the next Kremlin occupant could
very well be openly sympathetic to the Russian neo-Nazi movement, and such an
outcome would truly be a dire situation for the country, Eurasia and the world
(see EDM, February 13, 2012).
\end{multicols}

\iusr{Marijka Stadnyk}

Why the concern about Ukraine, when clearly, the bigger Nazi fascist threat
comes from Russia?

\href{http://anton-shekhovtsov.blogspot.com/2014/08/neo-nazi-russian-national-unity-in.html}{%
Neo-Nazi Russian National Unity in Eastern Ukraine, anton-shekhovtsov.blogspot.com, 14.08.2014%
}

\iusr{Rex Weyler}

Yeah, Marijka, there are neo-nazis all over the world, even where I live in
Canada. But in Ukraine, they have ascended to power in the government installed
with the help of the US. So I suggest, if you are concerned about fascism, that
you focus on Ukrainian fascists, who actually now have power and are killing
people.

\end{itemize} % }

\iusr{Vesa Raiskila}

telegraph.co.uk - Ukraine crisis - who fired the shots that shook the Maidan?

\begin{itemize} % {
\iusr{Vesa Raiskila}

Thus, even the official commission set up by the post-coup regime concluded
that Yanukovych's police forces (the Berkut) were *not* to be blamed for the
massacre.

\end{itemize} % }

\iusr{Sergey Povzner}

Your trip to Moscow, the aggressor in this war, has been clearly very
illuminating.

I would humbly suggest you also visit Kyiv and speak to families and friends of
those who were killed on Maidan. It is well established that the vast majority
of murdered people on Maidan were protesters. It is surprising to see
statements to the contrary about such basic facts from someone who is working
on a historical movie.

Reading some history books about Ukraine in the 20th century would also be a
great idea: both Timothy Snyder and Anne Applebaum have written excellent books
on this subject.

And finally, since you are working on a movie about Ukraine and Ukrainians, I
suggest that you premiere it in Kyiv. In person, of course.

\iusr{David Karlin}

Mr. Stone, your movies are good. you as a person not so much. I don't know why
and how you found friends among russian government crooks, but knowing that
fact I assume that you're a sell out. Yanukovitch and his circle were corrupted
scumbags (such as the current russian authorities). when Yanukovich lost his
power due to Maidan movement, russians became angry and sent troops to Ukraine.
as a proof - russian soldiers in Kiev shooting policemen and Maidan activists.
later they were found in Crimea and some of them went to Donetsk-Donbas (many
of them died there but officially they never been there). the Malay plane? most
evidences point out it was pro-russian separatists led by russian KGB officer
Girkin-Strelkov who bragged about it few minutes later online not yet knowing
it was a civil plane.

so I now wonder what do you plan with your new friends, what kind of propaganda
might come out from this cooperation

\iusr{Peter Iwanec}

What is wrong with Ukraine wanting to be free? When the Soviets helped
revolutionary factions in central America Oliver Stone was all for it. So why
is it wrong for good Christian people in their own land who have been abused by
circumstances of history to yearn for freedom?

\iusr{Dzvinka Siatetska}

By the way, this is how ridiculous your words are "Russia is not involved".
Would you make a trip to Moscow to work on a documentary, if Russia was not
involved?

\iusr{Dzvinka Siatetska}

Ok, you decided to make a documentary on the Ukrainian revolution. You've made
your trip to Moscow to interview the corrupt ex-president. In any documentary,
all sides views are presented. Why don't you make a trip to Kyiv now and
interview the people that were standing on Maidan, the families of those that
were killed?

\iusr{Сергій Атаманчук}

Mr. Stone you are focused on USA "intrusion", but fail to see how Russia
intrudes into Ukraine. If USA was so into Ukraine wouldnt they send weapons to
support the war against Russia?

\iusr{Roman Krutokhvostov}

Mr. Stone, the way it was done much more looks like The Battle of Athens
(1946), just on a larger scale.

It is very strange of you to call special service and special enforcement
troopers "policemen" and even strange not to give a number , just..."many".
What is "many"? More than 100 civilians are known to be killed AFTER being
kidnapped and tortured by these "policemen".

From your next statement one can conclude that German Nazis were supporting
creation of a separate Ukrainian State - BRAVO.

Beginning in 1947-48 USSR:

a) blocked Marshall Plan, which I believed was offered to Ukraine as a state
with a presence in United Nations, thus leading Ukrainians to cannibalism
because of famine.

b) was constantly violating Potsdam Agreement and Paris Peace Treaties for decades.

I assume a) is an enough reason to start organize guerrillas due to Truman
Doctrine, but b) is also important.

The big picture is now-reduced-Russia doesn't want to release Ukraine for its
industry placed in the chain of the armament production in Russia starting with
the mining of uranium. The last move is possible creation of buffer state of
"Novorossia" or whatever it will be called in order to avoid direct contact
with Ukrainian diplomacy and third-country or UN arbitrage.

Maybe you and some leader abroad enjoy thinking that that leader can start a
new military-diplomatic competition vs US, but in reality it is his own
hallucination, which you, Mr Stone, are discussing as something real.

\iusr{Vadym Ivanynyuk}

Sure, Me. Stone, pro-western, indeed... You would probably prefer Tian an men
square way, when Russian tanks do the job without any "pro-western" support.
Like Putin's "democracy" as we see it now in Russia where any non-pro
government meeting is being suppressed by police? Want all world be like that?
"Stockholm syndrome"? Then go ahead, listen to the Yanukovich, make movies how
good is Putin and feed Americans with this crap. But if you think your millions
will save you from the catastrophe you were helping to create - think again....
Snowdens's way leads to nowhere...

\iusr{Евгений Ласман}

Don't you think, Mr. @Olive Stone, that it is better come to Ukraine and ask
people about Nightingale here? Or maybe about Maidan? Sure only in case if you
are trying to make a documentary, not a fiction movie.

\iusr{Patrick Murray}

Hey Mr Stone, you could better spend you time looking into the militarisation
of police forces in your own country, see what you make of that before you
embark on ill conceived foreign crusades.

\iusr{Yura Kovalchuk}

HOW MUCH DID putin PAYS YOU FOR THIS SHIT ??? A lot of money ?

\begin{itemize} % {
\iusr{Иван Путинок}
You idiot. The world must know the truth.

\iusr{Iryna Brand}
I guess, a lot!!!
\end{itemize} % }

\iusr{Vladimír Manda}
I agree with you Mr. Stone.

\iusr{Christopher Dale}

What bullshit! I was there, on the ground through the entire protests in Kiev.
The most pro western involvement was my friends and I wandering around trying
not to get shot. It is disgraceful that you can give this DURAK a voice to
continue spouting his lies and dilute the movement that so many died for.
Maidan showed humanity at its finest- the bravest people i've ever seen, and at
it's worst- riot police beating and killing their own people.

Think back to how the protests started- riot police beating peaceful, gentle,
students. Is it not plausible that just maybe as the protests escalated, so did
the levels of violence.


\iusr{Olga Kovtun}
Better stay silent if you know nothing about the history of Ukraine. SHAME on you, Mr. Stone.

\iusr{Miro Marta Shchurevich}
Shame on you for your idiotic comments.

\iusr{Chris Harrison}

Threads of video evidence rated to the Kiev Nazis. Verifiable proof that the US
media have lied about the Ukrainian Crisis on numerous occasions

http://www.discussionist.com/101451370

The incredulous lies of the US media on Ukraine

http://www.discussionist.com/101463288

Ukraine - The rise of a US supported fascist state.

http://www.discussionist.com/101461889

US media coverup of Ukraines Nazis continues and the story of MH-17 disappears
from US media radar


\end{itemize} % }
