% vim: keymap=russian-jcukenwin
%%beginhead 
 
%%file 28_05_2022.fb.suhorukova_nadia.mariupol.1.vremja_gorod.eng
%%parent 28_05_2022.fb.suhorukova_nadia.mariupol.1.vremja_gorod
 
%%url 
 
%%author_id 
%%date 
 
%%tags 
%%title 
 
%%endhead 

\#mariupol \#hope The way from the fifth to the first during the bombing is much
longer than the flight to the moon and back. Since February 24, there was a
special time in our city. Mariupol. It almost didn't move. Sad and scary time.
An Infinite Hell.

Sometimes we asked each other, "What time is it? "As if there was any
difference. After two weeks of war, I confused the days of the week and
numbers. The cold March was raging like February. It seemed to me that the
eternal winter had begun.

There were three times in a day - morning, day and night. The night was the
scariest. She performed in Mariupol as soon as it got dark. That's when the
endless shelling began.

It seems to me that the Russians bombed the city and took it with exhaustion. I
guess they thought if they didn't let us sleep for a minute, we would disappear
somewhere. We will not run like scared mice in the streets in search of water
and food during the day.

Or maybe they were just having fun. Just like in a computer game. It's like the
city they were destroying, the multi-storey buildings they were constantly
fired at with missiles, people who were bombed from planes are unreal.

For them, we were just human beings in a computer game. They were killing us
and laughing at us They didn't care that we're alive, we're scared, we're in
pain, we're trying to save ourselves.

Only monsters can shoot at living people like this, as the Russians did. Every
day they introduce us to a new kind of weapon. Shattered a thousand lives.

Just watched a video the other day. Two men were filming from a car in the
center of Mariupol. From art school to Torgovaya. One asked, "Did anyone
survive here? How was it possible to survive here? "

I also don't understand how we survived? How was this even possible?

Do you know how the Russians tightened the noose around the throat of the city?
They walked from different directions. We sat in our neighborhood, listening to
the sounds of hell and waited horribly for them to get very close.

We knew they were bombing and shelling the streets nearby. We saw how tanks
with the letter son-in-law on the side drove along Mira Avenue. The house two
intersections fell into an eternal sleep. People said he collapsed from the air
strike. Not everyone died under his rubble.

Their moans and screams leaked to the surface. There was no one to get them.
Before that, they shelled the rescue base. The dead were lying on the asphalt
near the State Emergency Service building. In a nearby bomb shelter - the
living were hiding.

Vitya told the most terrible horrors. The neighbor of the people who sheltered
me and my mom. Vitya walked around the city and saw everything with his own
eyes. Dead bodies on Cheremushki, a funnel that became a grave for a two-story
house, limbs severed.

We didn’t wanna hear it. If you cover your head with a blanket, trouble will
not notice you and will pass by. We covered ourselves with a blanket of war.

We understood that everything was very bad, but we told ourselves: not a single
rocket or bomb will fall on us. Everything that happens outside is a bad dream.
The war will be over sooner. Orcs will not have time to get close to our house.

The loop got tightened up very quickly. The rocket hit the roof of the house,
the shells were pounding all the floors around. Planes cut the sky above our
house and launched air strikes. It was impossible to hide from them.

Even if a bomb falls across the street, the house responds by shaking and
floating the walls. It's like a giant guitar string vibrates and breaks and
everything freezes inside you.

These photos are from different districts of Mariupol. This is my town right
now.

Today, the occupants continue to bomb Ukraine and kill people in their homes.
